---
title: "Noise_Plasticity_Coupling_in_E.coli"
author: "Tsuru"
date: "2024/5/7"
output: html_document
---
# 0. Set the codes public or private 
```{r Set,warning=FALSE, message=FALSE}
# TODO
my_public<-FALSE # TRUE: public, FALSE: private 
```
# 1. General settings
## 1.1. Load workspace
```{r General,warning=FALSE, message=FALSE}
# load("./Main.RData")
```
## 1.2. Save workspace
```{r General,warning=FALSE, message=FALSE}
# save.image("./Main.RData")
```
## 1.3. Library loading
```{r library,warning=FALSE, message=FALSE}
library(dplyr)# dataframe
library(tidyverse)# dataframe
library(magrittr)# pipe
library(readxl) # read xlsx
library(flowCore) # flow cytometry
# library(flowViz) # flow cytometry
# 
# library(stringr)# regular expression
# 
# library(KernSmooth)
# library(ggplot2)# visualization
# library(gridExtra)# visualization
# library(grid)# visualization
# library(scales)# visualization
# library(ggfortify)
# library(reshape2) # dataframe
# library(cowplot)
# library(ggpubr)# visualization
# library(rstatix)# statistical test
# library(boot)
# library(qvalue)# statistical test
# library(ppcor)# calc. partial correlation coeff. 
# library(GGally)# visualization
# library(gtable)# visualization
# 
# library(matrixStats) # rowMeans etc.
# library(preprocessCore)
# library(RColorBrewer)# visualization
# 
# library(fitdistrplus)
# 
# library(clusterProfiler) # statistical test

Sys.time()
```
## 1.4. versatile user functions
The [qw](https://ja.coder.work/so/r/240447) function in Perl.  
The [createEmptyDf](https://htsuda.net/archives/2560) function.
The [g_legend](https://github.com/hadley/ggplot2/wiki/Share-a-legend-between-two-ggplot2-graphs) function to extract legend.
```{r General}
qw <- function(...) {
  sapply(match.call()[-1], deparse)
}

createEmptyDf = function( nrow, ncol, colnames = c() ){
  data.frame( matrix( vector(), nrow, ncol, dimnames = list( c(), colnames ) ) )
}
Sys.time()
```
## 1.5 Font size
```{r General}
# my_fontsize<-16
# Sys.time()
```
## 1.6. External ssd/hdd
```{r General}
my_volume<-"/Volumes/DailyUse"
my_playgrnd<-paste(my_volume,"Noise_Plasticity",sep="/")

if (my_public){
  my_playgrnd<-getwd()
}

Sys.time()
```
## 1.7. Versatile color palletes
```{r color}
# mycolpal<-get_palette("lancet",9)
# print(c("#00468BFF","#ED0000FF","#42B540FF","#0099B4FF","#925E9FFF","#FDAF91FF","#AD002AFF","#ADB6B6FF","#1B1919FF"))
# mycolpal.BuRd<-c(get_palette(palette = "Blues", 4)[2:4],get_palette(palette = "Reds", 4)[2:4])
# print(c("#FEE5D9","#FCAE91","#FB6A4A","#CB181D"))
# print(c("#EFF3FF","#BDD7E7","#6BAED6","#2171B5"))
Sys.time()
```

#### Directory
define the directory of the file which describes information of each fcs file.
```{r directory,warning=FALSE, message=FALSE}
d<-getwd()
dfileinfo<-paste(d,"Noise_Plasticity_FileInfo_h.csv",sep="/")
bkgfile <-paste(my_playgrnd,"FACS_data/Tsuru/T20191209/Plate_00_BW25113.fcs",sep = "/")
if(my_public){
  bkgfile <-paste(my_playgrnd,"Zenodo/T20191209/Plate_00_BW25113.fcs",sep = "/")
}
```

# 2. Initial Curation
## 2.1. 
This section defines 
- maximal # of events per fcs file
- well postions showing aggregation of YFP fused protein
```{r initialize,warning=FALSE, message=FALSE}
Nbtot<-50000
Forci<-qw(B3,B12,D3,F3,G2,G5,H3)
mycol<-qw(FSC, SSC, FITC, logFSC, logSSC, logFITC, TubeID, Medium, Pos, FSCgate, FITCgate, TotalEvent)
mycol2<-qw(TotalEvent, Event, Med_FITC, rSD_FITC, rCV_FITC, rCV2_FITC, Av_FITC, SD_FITC, CV_FITC, CV2_FITC, log10Av_FITC, log10SD_FITC, Med_FSC,log10Av_FSC)
chsize<-24 # font size
# myescol<-get_palette(palette = "lancet", 2)
Sys.time()
```

## 2.2. Calculate BKG fluorescence for N1 strains
```{r bacground,warning=FALSE, message=FALSE}
bkgfile <-paste(my_playgrnd,"FACS_data/Tsuru/T20191209/Plate_00_BW25113.fcs",sep = "/")
if(my_public){
  bkgfile <-paste(my_playgrnd,"Zenodo/T20191209/Plate_00_BW25113.fcs",sep = "/")
}
dbkg=createEmptyDf(Nbtot, length(mycol), colnames = mycol )
fcs<-read.FCS(bkgfile)
dbkg[,c(1:3)]<-fcs@exprs[, c("FSC-A","SSC-A","FITC-A")]
FITCbkg<-median(dbkg$FITC,na.rm = T)
rm(fcs)
Sys.time()
```

## 2.3. Load file list and extract information about N1 strains
```{r Filelist,warning=FALSE, message=FALSE}
dat<-paste(getwd(),"Meta","fcs_fileinfo.xlsx",sep = "/") %>% read_xlsx()
my_meta<-dat[(dat$Strain=="N1")&(dat$Use=="Y"),]
tmp=createEmptyDf(nrow(dat), length(mycol2), colnames = mycol2 )
dat<-cbind(dat,tmp)
dat<-subset(dat, dat$Strain=="N1"&dat$Use=="Y")
Sys.time()
```

## 2.4. Define focal medium
Run only first time
```{r Medium,warning=FALSE, message=FALSE}
# df_med<-dat %>% select(Medium_Series,Medium,YYMMDD) %>% distinct(Medium,YYMMDD,.keep_all = TRUE)
# df_med<-df_med[order(df_med$Medium),]
# rownames(df_med)<-seq(1,nrow(df_med))
# df_med$FSClogmed<-NA
# df_med$FSCupr<-NA
# df_med$FSClwr<-NA
# Sys.time()
```
## 2.3. Define FSC gate
Run only first time
```{r MainLoop,warning=FALSE, message=FALSE}
# for(jj in 1:nrow(df_med)){
#   my_tmp<-dat[(dat$Medium_Series==df_med$Medium_Series[jj])&
#                 (dat$Medium==df_med$Medium[jj])&
#                 (dat$YYMMDD==df_med$YYMMDD[jj]),] %>%
#     select(Folder,FCS)
#   df=createEmptyDf(nrow = Nbtot*nrow(my_tmp),ncol = 1,colnames = qw(logFSC))
#   Cell=1
#   for(j in 1:nrow(my_tmp)){
#     dfcs=createEmptyDf(nrow = Nbtot,ncol = 2, colnames = qw(FSC,logFSC))
#     fcs<-paste(my_playgrnd,my_tmp$Folder[j],my_tmp$FCS[j],sep="/") %>%
#       read.FCS()
#     fcs<-fcs@exprs[, c("FSC-A")]
#     my_count<-length(fcs)
#     if(my_count<=Nbtot){
#       dfcs$FSC[1:my_count]<-fcs
#     }else{
#       dfcs$FSC<-fcs[1:Nbtot]
#     }
#     dfcs[(!is.na(dfcs$FSC))&(dfcs$FSC>0),]$logFSC<-log10(dfcs[(!is.na(dfcs$FSC))&(dfcs$FSC>0),]$FSC)
#     df$logFSC[Cell:c(Cell+Nbtot-1)]<-dfcs$logFSC
#     Cell=Cell+Nbtot
#   }
#   FSClogmed<-median(df$logFSC,na.rm=T)
#   df_med$FSClogmed[jj]<-FSClogmed
#   df_med$FSCupr[jj]<-FSClogmed+0.1
#   df_med$FSClwr[jj]<-FSClogmed-0.1
#   print(Sys.time())
#   print(paste(jj,nrow(df_med),sep="/"))
# }
# rm(df)
# # write_csv(x = df_med,file = paste(getwd(),"FlowData_Output","df_med.csv",sep="/"))
# Sys.time()
```
## 2.5. load FSC gates
```{r MainLoop,warning=FALSE, message=FALSE}
df_med<-paste(getwd(),"FlowData_Output","df_med.csv",sep="/") %>% 
  read_csv()
Sys.time()
```
## 2.6. Main loop
Run only first time
```{r MainLoop,warning=FALSE, message=FALSE}
for(jj in 1:nrow(df_med)){
  my_tmp<-dat[(dat$Medium_Series==df_med$Medium_Series[jj])&
                (dat$Medium==df_med$Medium[jj])&
                (dat$YYMMDD==df_med$YYMMDD[jj]),] %>%
    select(TubeID,Folder,FCS)
  my_tmp$Event<-NA
  my_tmp$Med_FITC<-NA
  my_tmp$rSD_FITC<-NA
  my_tmp$rCV_FITC<-NA
  my_tmp$rCV2_FITC<-NA
  my_tmp$Av_FITC<-NA
  my_tmp$SD_FITC<-NA
  my_tmp$CV_FITC<-NA
  my_tmp$CV2_FITC<-NA
  my_tmp$log10Av_FITC<-NA
  my_tmp$log10SD_FITC<-NA
  my_tmp$log10Av_FSC<-NA
  my_tmp$log10Med_FSC<-NA

  FSClogmed<-df_med$FSClogmed[jj]
  FSCupr<-df_med$FSCupr[jj]
  FSClwr<-df_med$FSClwr[jj]
  j<-1
  for(j in 1:nrow(my_tmp)){
    dfcs=createEmptyDf(nrow = Nbtot,ncol = length(mycol), colnames = mycol )
    dfcs<-dfcs %>% select(FSC,FITC,logFSC,logFITC)
    my_path<-paste(my_playgrnd,my_tmp$Folder[j],my_tmp$FCS[j],sep="/")
    if(my_public){
      my_path<-my_path %>% str_replace(string = .,pattern = "FACS_data/Tsuru",replacement = "Zenodo")
    }
    fcs<-my_path %>%
      read.FCS()
    fcs<-fcs@exprs[, c("FSC-A","FITC-A")] %>%
      data.frame() %>%
      select(FSC.A,FITC.A)
    colnames(fcs)<-qw(FSC,FITC)
    my_count<-nrow(fcs)
    if(my_count<=Nbtot){
      dfcs[1:my_count,c(qw(FSC,FITC))]<-fcs
    }else{
      dfcs[1:Nbtot,c(qw(FSC,FITC))]<-fcs[1:Nbtot,]
    }
    dfcs$FITC<-dfcs$FITC-FITCbkg# subtract autofluorescence
    dfcs[(!is.na(dfcs$FSC))&(dfcs$FSC>0),]$logFSC<-log10(dfcs[(!is.na(dfcs$FSC))&(dfcs$FSC>0),]$FSC)
    dfcs<-dfcs[!is.na(dfcs$logFSC)&(dfcs$logFSC>=FSClwr)&(dfcs$logFSC<=FSCupr)&(dfcs$FITC>0),]
    dfcs$logFITC<-log10(dfcs$FITC)

    my_tmp$Event[j]<-nrow(dfcs)
    my_tmp$Med_FITC[j]<-median(dfcs$FITC,na.rm = T)
    my_tmp$rSD_FITC[j]<-median(abs(dfcs$FITC-my_tmp$Med_FITC[j]),na.rm = T)*1.4826 # robust SD
    my_tmp$rCV_FITC[j]<-my_tmp$rSD_FITC[j]/my_tmp$Med_FITC[j]
    my_tmp$rCV2_FITC[j]<-my_tmp$rCV_FITC[j]^2
    my_tmp$Av_FITC[j]<-mean(dfcs$FITC,na.rm = T)
    my_tmp$SD_FITC[j]<-sd(dfcs$FITC,na.rm = T)
    my_tmp$CV_FITC[j]<-my_tmp$SD_FITC[j]/my_tmp$Av_FITC[j]
    my_tmp$CV2_FITC[j]<-my_tmp$CV_FITC[j]^2
    my_tmp$log10Av_FITC[j]<-mean(dfcs$logFITC,na.rm = T)
    my_tmp$log10SD_FITC[j]<-sd(dfcs$logFITC,na.rm = T)
    my_tmp$log10Av_FSC[j]<-mean(dfcs$logFSC,na.rm = T)
    my_tmp$log10Med_FSC[j]<-FSClogmed
  }
  my_tmp<-my_tmp %>% select(-Folder,-FCS)
  if(jj==1){
    my_df<-my_tmp
  }else{
    my_df<-bind_rows(my_df,my_tmp)
  }
  print(Sys.time())
  print(paste(jj,nrow(df_med),sep="/"))
}
my_tmp<-my_meta[my_meta$Use=="Y",]
my_tmp<-left_join(my_tmp,my_df)
write_csv(x = my_tmp,file = paste(getwd(),"FlowData_Output","stats_flowdata.csv",sep="/"))
Sys.time()
```
