---
title: "Noise_Plasticity_Coupling_in_E.coli"
author: "Tsuru"
date: "2025/3/9"
output: html_document
---
# 0. Set the codes public or private 
```{r Set,warning=FALSE, message=FALSE}
# TODO
my_public<-FALSE # TRUE: public, FALSE: private 
```
# 1. General settings
## 1.1. Load workspace
```{r General,warning=FALSE, message=FALSE}
# load("./Main.RData")
```
## 1.2. Save workspace
```{r General,warning=FALSE, message=FALSE}
# save.image("./Main.RData")
```
## 1.3. Library loading
```{r General,warning=FALSE, message=FALSE}
library(dplyr)# dataframe
library(tidyverse)# dataframe
library(magrittr)# pipe
library(Hmisc) # use %nin%
library(readxl) # read xlsx
library(flowCore) # flow cytometry
# library(flowViz) # flow cytometry

library(stringr)# regular expression

library(KernSmooth)
library(ggplot2)# visualization
library(gridExtra)# visualization
library(grid)# visualization
library(scales)# visualization
library(ggrepel)# visualization
library(ggfortify)
library(reshape2) # dataframe
library(cowplot)
library(ggpubr)# visualization
library(rstatix)# statistical test
library(boot)
library(qvalue)# statistical test
library(ppcor)# calc. partial correlation coeff. 
library(GGally)# visualization
library(gtable)# visualization

library(matrixStats) # rowMeans etc.
library(preprocessCore)
library(RColorBrewer)# visualization

library(boot) # bootstrap

library(fitdistrplus)

library(clusterProfiler) # statistical test
library(KEGGREST) # enrichment analysis

library(FactoMineR) # PCA
library(factoextra) # PCA
library(viridis) # visualization

library(Biostrings)
library(msa)
library(seqinr)
library(ape)
library(ggtree)

library(ggpmisc) # stat_poly_eq

library(ggmsa) # multiple sequence analysis

library(svglite) # used for ggsave (save figs as svg files)
library(ggplotify) # plot to ggplot


Sys.time()
```
## 1.4. versatile user functions
The [qw](https://ja.coder.work/so/r/240447) function in Perl.  
The [createEmptyDf](https://htsuda.net/archives/2560) function.
The [g_legend](https://github.com/hadley/ggplot2/wiki/Share-a-legend-between-two-ggplot2-graphs) function to extract legend.
```{r General}
qw <- function(...) {
  sapply(match.call()[-1], deparse)
}

createEmptyDf = function( nrow, ncol, colnames = c() ){
  data.frame( matrix( vector(), nrow, ncol, dimnames = list( c(), colnames ) ) )
}

g_legend<-function(a.gplot){
  tmp <- ggplot_gtable(ggplot_build(a.gplot))
  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
  legend <- tmp$grobs[[leg]]
  return(legend)}

pValue_sp_text=function(dtf){
  pcor_sp<-cor.test(x=dtf[,1],y=dtf[,2],method="spearman")
  rho_sp<-round(pcor_sp$estimate,digits = 2)
  pv_sp<-ifelse(pcor_sp$p.value<0.05," P<0.05",paste(" P==",round(pcor_sp$p.value,digits = 1),sep = ""))
  rhopvtxt_sp<-paste("list(italic(rho)==", rho_sp,", ",pv_sp,")")
  return(rhopvtxt_sp)
}

pValue_pr_text=function(dtf){
  pcor_pr<-cor.test(x=dtf[,1],y=dtf[,2],method="pearson")
  r_pr<-round(pcor_pr$estimate,digits = 2)
  pv_pr<-ifelse(pcor_pr$p.value<0.05," P<0.05",paste(" P==",round(pcor_pr$p.value,digits = 1),sep = ""))
  rpvtxt_pr<-paste("list(italic(r)==", r_pr,", ",pv_pr,")")
  return(rpvtxt_pr)
}
Sys.time()
```
## 1.5 Font size
```{r General}
my_fontsize<-16
Sys.time()
```
## 1.6. External ssd/hdd
```{r General}
my_volume<-"/Volumes/DailyUse"
my_playgrnd<-paste(my_volume,"Noise_Plasticity",sep="/")

if (my_public){
  my_playgrnd<-getwd()
}

my_figout<-paste(getwd(),"Output/Figures",sep="/")
my_supplfigout<-paste(getwd(),"Output/Suppl_Figures",sep="/")

Sys.time()
```
## 1.7. Versatile color palletes
```{r General}
mycolpal<-get_palette("lancet",9)
print(c("#00468BFF","#ED0000FF","#42B540FF","#0099B4FF","#925E9FFF","#FDAF91FF","#AD002AFF","#ADB6B6FF","#1B1919FF"))
mycolpal.BuRd<-c(get_palette(palette = "Blues", 4)[2:4],get_palette(palette = "Reds", 4)[2:4])
print(c("#FEE5D9","#FCAE91","#FB6A4A","#CB181D"))
print(c("#EFF3FF","#BDD7E7","#6BAED6","#2171B5"))
Sys.time()
```
## 1.8. Legends
```{r General,fig.height=2.5,fig.width=1,dpi=300}
my_richness<-c("#440154FF","#46337EFF","#365C8DFF","#277F8EFF","#277F8EFF","#1FA187FF","#4AC16DFF","#9FDA3AFF","#FDE725FF") # based on viridis(n=8)
my_tmp<-data.frame(x=seq(1,9),y=seq(1,9),z=seq(1,9),zz=c("01","02","08","09","10","03","04","05","06"))
my_tmp$z<-factor(my_tmp$z,levels = seq(1,9))
my_tmp$zz<-factor(my_tmp$zz,levels = my_tmp$zz)
p<-ggscatter(my_tmp,x="x",y="y",color="zz",palette = my_richness,legend="right",legend.title="")
q<-get_legend(p)
as_ggplot(q)

p<-ggbarplot(my_tmp,x="x",y="y",color="zz",fill="zz",palette = my_richness,legend="right",legend.title="")
q<-get_legend(p)
as_ggplot(q)


my_richness2<-c("#440154FF","#46337EFF","#365C8DFF","#277F8EFF","#1FA187FF","#4AC16DFF","#9FDA3AFF","#FDE725FF") # based on viridis(n=8)
my_tmp<-data.frame(x=seq(1,8),y=seq(1,8),z=seq(1,8))
my_tmp$z<-factor(my_tmp$z,levels = rev(seq(1,8)))
p<-ggscatter(my_tmp,x="x",y="y",color="z",palette = my_richness2,legend="right",legend.title="")
p<-ggpar(p,font.legend = my_fontsize)
q<-get_legend(p)
as_ggplot(q)

p<-ggbarplot(my_tmp,x="x",y="y",color="z",fill="z",palette = my_richness2,legend="right",legend.title="")
p<-ggpar(p,font.legend = my_fontsize)
q<-get_legend(p)
as_ggplot(q)
#TODO ggsave(file="Fig2a_colorbar.svg", path=my_figout,dpi = 300, width = 1, height = 2.5)


my_tmp<-data.frame(x=seq(1,3),y=seq(1,3),z=qw(E,F,G))
my_tmp$z<-factor(my_tmp$z,levels = qw(E,F,G))
p<-ggscatter(my_tmp,x="x",y="y",shape="z",legend="right",legend.title="")
q<-get_legend(p)
as_ggplot(q)
#TODO ggsave(file="Fig2a_symbol.svg", path=my_figout,dpi = 300, width = 1, height = 2.5)


Sys.time()
```

# 2. Name Space
## 2.1. Define namse space of genes
```{r Global_Bnb,warning=FALSE, message=FALSE,fig.height=3,fig.width=3,dpi=300}
# gene name of W3110
genename.w3110<-paste(getwd(),"W3110_genes","w3110_gnftr.csv",sep="/") %>%
  read_csv() %>%
  data.frame()
# gene name of MG1655 including CDS, ncRNA, tRNA, rRNA
genename.mg1655<-paste(getwd(),"MG1655_genes","MG1655_gnftr.csv",sep="/") %>%
  read_csv() %>%
  data.frame()
genename.mg1655<-genename.mg1655[,c(2:ncol(genename.mg1655))]
colnames(genename.mg1655)[colnames(genename.mg1655)=="locus_tag"]<-"Bnb"
colnames(genename.mg1655)[colnames(genename.mg1655)=="GeneID"]<-"EntrezID"
# Essentiality (Goodal 2018 mBio)
dess<-paste(getwd(),"W3110_genes","ESSCDSList_Goodall.txt",sep="/") %>%
  read_delim(col_names =qw(Name,ECKnb) ) %>%
  data.frame()
dess$Essentiality<-"essential"
dess<-dess %>% select(ECKnb,Essentiality)


my_cond_ess<-c("b2507","b3281","b3956","b0109","b0243") # identified by a growth test using ko strians as detailed below
my_no_ko<-c("b1131","b0886","b0733")
my_removal_gn<-c(my_cond_ess,my_no_ko)

# # Essentiality (Tong 2020 mBio)
# dess_mltcbn<-paste(getwd(),"Essentiality","mbio.02259-20-st001.xlsx",sep="/") %>%
#   read_xlsx(sheet = "S1A - Endpoint Biomass") %>%
#   data.frame()
# colnames(dess_mltcbn)[1]<-"Bnb"
# dess_mltcbn<-dess_mltcbn %>% select(-Gene)
# my_df<-dess_mltcbn %>% pivot_longer(cols = -Bnb,names_to = "Carbon",values_to = "Growth")
# my_q1<-my_df$Growth %>% quantile()
# my_q3<-my_q1[4]
# my_q1<-my_q1[2]
# Growth_thr<-mean(my_df[(my_df$Growth>=my_q1)&(my_df$Growth<my_q3),]$Growth)-3*sd(my_df$Growth)
# ggscatter(dess_mltcbn,x="Glucose",y="Glycerol",size=0.3,alpha=0.3)+
#   geom_hline(yintercept = Growth_thr,color="Green")+
#   geom_vline(xintercept = Growth_thr,color="Green")
# 
# 
# # Essentiality (Baba 2006 MolSystBiol)
# dess_ko<-paste(getwd(),"Essentiality","Baba_2006_MSB_TableS3.xlsx",sep="/") %>%
#   read_xlsx() %>%
#   data.frame()
# dess_ko<-dess_ko[grepl(dess_ko$Bnb,pattern = "^b"),]
# KO_Growth_thr<-0.000000001 # 0.084 for slow growth Baba et al., Fig.6
# dess_ko$CondEssentiality<-"nonessential"
# dess_ko[is.na(dess_ko$LB_22hr),]$CondEssentiality<-"essential"
# dess_ko[(!is.na(dess_ko$MOPS_48hr))&(dess_ko$MOPS_48hr<KO_Growth_thr),]$CondEssentiality<-"conditional"

dBnb<-genename.mg1655
dBnb<-dBnb[!is.na(dBnb$Bnb),]
Sys.time()
```
# 3. Flow data
## 3.1. FCS headder
```{r FlowData,warning=FALSE, message=FALSE}
bkgfile <-paste(my_playgrnd,"FACS_data/Tsuru/T20191209/Plate_00_BW25113.fcs",sep = "/")
if(my_public){
  bkgfile <-paste(my_playgrnd,"Zenodo/T20191209/Plate_00_BW25113.fcs",sep = "/")
}
my_tmp<-read.FCSheader(bkgfile)
my_tmp<-my_tmp[[1]] %>% data.frame()
my_tmp$Feature<-rownames(my_tmp)
colnames(my_tmp)<-qw(Values,Feature)
my_tmp$Feature<-str_remove_all(my_tmp$Feature,pattern = "\\$")
rownames(my_tmp)<-seq(1,nrow(my_tmp))
my_tmp <- my_tmp %>% select(Feature,Values)
print(paste("Threshold:",my_tmp[my_tmp$Feature=="THRESHOLD",]$Values,sep=" "))
print(paste("PMT of FSC:",my_tmp[my_tmp$Feature=="P1V",]$Values,sep=" "))
print(paste("PMT of SSC:",my_tmp[my_tmp$Feature=="P4V",]$Values,sep=" "))
print(paste("PMT of YFP:",my_tmp[my_tmp$Feature=="P7V",]$Values,sep=" "))
Sys.time()
```
## 3.2. Define BKG fluorescence for N1 strains
```{r FlowData,warning=FALSE, message=FALSE}
Nbtot<-50000
bkgfile <-paste(my_playgrnd,"FACS_data/Tsuru/T20191209/Plate_00_BW25113.fcs",sep = "/")
if(my_public){
  bkgfile <-paste(my_playgrnd,"Zenodo/T20191209/Plate_00_BW25113.fcs",sep = "/")
}
fcs<-read.FCS(bkgfile)
dbkg<-fcs@exprs[, c("FSC-A","SSC-A","FITC-A")] %>% data.frame()
colnames(dbkg)<-qw(FSC,SSC,FITC)
FITCbkg<-median(dbkg$FITC,na.rm = T)
rm(fcs)
Sys.time()
```
## 3.3. load stats of FlowData
```{r FlowData,warning=FALSE, message=FALSE}
# FSC_gate
df_med<-paste(getwd(),"FlowData_Output","df_med.csv",sep="/") %>% 
  read_csv()
# Stats
df_stat_flow<-paste(getwd(),"FlowData_Output","stats_flowdata.csv",sep="/") %>%
  read_csv()
df_stat_flow<-df_stat_flow[(df_stat_flow$Strain=="N1")&(df_stat_flow$Foci=="N"),]
Sys.time()
```
## 3.4. Representative genes
pgk (essential gene) and carA (nonessential gene)
```{r FlowData,warning=FALSE, message=FALSE, fig.width=3,fig.height=3}
Nbtot<-50000
# tube ID=292(pgk, essential), 300(carA, nonessential) in E10
my_med<-"E10"
my_date<-df_med[df_med$Medium==my_med,]$YYMMDD[1]
my_upr<-df_med[(df_med$Medium==my_med)&(df_med$YYMMDD==my_date),]$FSCupr
my_lwr<-df_med[(df_med$Medium==my_med)&(df_med$YYMMDD==my_date),]$FSClwr

# load flow data of pgk in E10
my_path<-df_stat_flow[(df_stat_flow$Medium==my_med)&
                        (df_stat_flow$YYMMDD==my_date)&
                        (df_stat_flow$Name=="pgk"),]
my_path<-paste(my_playgrnd,my_path$Folder,my_path$FCS,sep="/")
if(my_public){
  my_path<-my_path %>% str_replace(string = .,pattern = "FACS_data/Tsuru",replacement = "Zenodo")
}

my_fcs1<-my_path %>% read.FCS()
my_fcs1<-my_fcs1@exprs[, c("FSC-A","FITC-A")] %>%
      data.frame() %>%
      select(FSC.A,FITC.A)
colnames(my_fcs1)<-qw(FSC,FITC)
if(nrow(my_fcs1)<=Nbtot){
  my_fcs1<-my_fcs1[1:Nbtot,]
}
my_fcs1$Name="pgk"

# load flow data of carA in E10
my_path<-df_stat_flow[(df_stat_flow$Medium==my_med)&
                        (df_stat_flow$YYMMDD==my_date)&
                        (df_stat_flow$Name=="carA"),]
my_path<-paste(my_playgrnd,my_path$Folder,my_path$FCS,sep="/")
if(my_public){
  my_path<-my_path %>% str_replace(string = .,pattern = "FACS_data/Tsuru",replacement = "Zenodo")
}
my_fcs2<-my_path %>% read.FCS()
my_fcs2<-my_fcs2@exprs[, c("FSC-A","FITC-A")] %>%
      data.frame() %>%
      select(FSC.A,FITC.A)
colnames(my_fcs2)<-qw(FSC,FITC)
if(nrow(my_fcs2)<=Nbtot){
  my_fcs2<-my_fcs2[1:Nbtot,]
}
my_fcs2$Name="carA"

my_fcs<-bind_rows(my_fcs1,my_fcs2)
my_fcs$FITC<-my_fcs$FITC-FITCbkg # subtract background
my_fcs<-my_fcs[(my_fcs$FITC>0)&(my_fcs$FSC>0),]
my_fcs$logFSC<-log10(my_fcs$FSC)
my_fcs$logFITC<-log10(my_fcs$FITC)
my_fcs$Gate<-"Out"
my_fcs[(my_fcs$logFSC>=my_lwr)&(my_fcs$logFSC<=my_upr),]$Gate<-"In"
my_fcs$Gate<-factor(my_fcs$Gate,levels=qw(In,Out))

p1<-ggscatter(my_fcs[my_fcs$Name=="pgk",],x="logFITC",y="logFSC",
          size=0.3,alpha=0.3,color="Gate",palette = c("#ED0000FF","black"),
          legend="")+
  annotate("text",x=-Inf,y=Inf,label="pgk",hjust = -0.5,vjust = 1,size=5,fontface="italic")+
  scale_x_continuous(breaks=seq(0,4,1),limits=c(-0.1,4))+
  scale_y_continuous(breaks=seq(0,4,1),limits=c(-0.1,4.5))+
  xlab(expression(log[10]~"YFP FI [a.u.]"))+
  ylab(expression(log[10]~"FSC [a.u.]"))
p1<-ggpar(p1,font.x=my_fontsize,font.y=my_fontsize,font.tickslab = my_fontsize)
p1
#TODO ggsave(file="Fig1d_pgk.svg", path=my_figout,dpi = 300, width = 3, height = 3)

p2<-ggscatter(my_fcs[my_fcs$Name=="carA",],x="logFITC",y="logFSC",
          size=0.3,alpha=0.3,color="Gate",palette = c("#00468BFF","black"),
          legend="")+
  annotate("text",x=-Inf,y=Inf,label="carA",hjust = -0.5,vjust = 1,size=5,fontface="italic")+
    scale_x_continuous(breaks=seq(0,4,1),limits=c(-0.1,4))+
  scale_y_continuous(breaks=seq(0,4,1),limits=c(-0.1,4.5))+
  xlab(expression(log[10]~"YFP FI [a.u.]"))+
  ylab(expression(log[10]~"FSC [a.u.]"))
p2<-ggpar(p2,font.x=my_fontsize,font.y=my_fontsize,font.tickslab = my_fontsize)
p2
#TODO ggsave(file="Fig1d_carA.svg", path=my_figout,dpi = 300, width = 3, height = 3)


p3<-gghistogram(my_fcs[(my_fcs$Name=="pgk")&(my_fcs$Gate=="In"),],
                x="logFITC",y="density",bins=100,
                fill="#ED0000FF",color ="#ED0000FF",size=0.02,alpha=0.4,
                add="mean", add.params = list(size=0.5,linetype=5),
                ylab="Relative frequency")+
  annotate("text",x=-Inf,y=Inf,label="pgk",hjust = -0.5,vjust = 1,size=5,fontface="italic")+
  xlab(expression(log[10]~"YFP FI [a.u.]"))+
  scale_y_continuous(breaks=seq(0,2,1),limits=c(-0.1,2.5))+
  scale_x_continuous(breaks=seq(0,4,1),limits=c(-0.1,4))
p3<-ggpar(p3,font.x=my_fontsize,font.y=my_fontsize,font.tickslab = my_fontsize)
p3
#TODO ggsave(file="Fig1e_pgk.svg", path=my_figout,dpi = 300, width = 3, height = 3)


p4<-gghistogram(my_fcs[(my_fcs$Name=="carA")&(my_fcs$Gate=="In"),],
                x="logFITC",y="density",bins=100,
                fill="#00468BFF",color ="#00468BFF",size=0.02,alpha=0.4,
                add="mean", add.params = list(size=0.5,linetype=5),
                ylab="Relative frequency")+
  annotate("text",x=-Inf,y=Inf,label="carA",hjust = -0.5,vjust = 1,size=5,fontface="italic")+
  xlab(expression(log[10]~"YFP FI [a.u.]"))+
  scale_y_continuous(breaks=seq(0,2,1),limits=c(-0.1,2.5))+
  scale_x_continuous(breaks=seq(0,4,1),limits=c(-0.1,4))
p4<-ggpar(p4,font.x=my_fontsize,font.y=my_fontsize,font.tickslab = my_fontsize)
p4
#TODO ggsave(file="Fig1e_carA.svg", path=my_figout,dpi = 300, width = 3, height = 3)

Sys.time()
```
# 4. Calc. Plasticity and Noise
## 4.1. averaging data of replicates
```{r Noise_Plasticity,warning=FALSE, message=FALSE, fig.width=3,fig.height=3}
my_df<-df_stat_flow %>%
  select(Bnb,Name,Essentiality,Foci,Medium) %>%
  distinct(Bnb,Medium,.keep_all = TRUE) 
my_df$log10Av_FITC<-NA
my_df$log10Var_FITC<-NA
my_df$log10SD_FITC<-NA
my_df$Essentiality<-factor(my_df$Essentiality,levels=qw(nonessential,essential))
i<-1
for(i in 1:nrow(my_df)){
  my_tmp<-df_stat_flow[(df_stat_flow$Bnb==my_df$Bnb[i])&
                         (df_stat_flow$Medium==my_df$Medium[i]),]
  my_tmp<-my_tmp[my_tmp$Event>=4000,]
  if(nrow(my_tmp)==2){
      my_tmp$log10Var_FITC<-my_tmp$log10SD_FITC^2
      my_df$log10Av_FITC[i]<-mean(my_tmp$log10Av_FITC)
      my_df$log10Var_FITC[i]<-mean(my_tmp$log10Var_FITC)
      my_df$log10SD_FITC[i]<-my_df$log10Var_FITC[i]^0.5
  }
}
df_stat_flow_rep<-my_df

# Calc. plasticity (SD_logAvFITC)
my_df<-df_stat_flow %>%
  select(Bnb,Name,Essentiality,Foci) %>%
  distinct(Bnb,.keep_all = TRUE)
my_df$Essentiality<-factor(my_df$Essentiality,levels=qw(nonessential,essential))
my_df$Mean_logAvFITC<-NA
my_df$SD_logAvFITC<-NA
i<-1
for(i in 1:nrow(my_df)){
  my_tmp<-df_stat_flow_rep[df_stat_flow_rep$Bnb==my_df$Bnb[i],]
  my_df$Mean_logAvFITC[i]<-mean(my_tmp$log10Av_FITC,na.rm=T)
  my_df$SD_logAvFITC[i]<-sd(my_tmp$log10Av_FITC,na.rm=T)
}
df_plst<-my_df

# dess_mltcbn_sbst<-dess_mltcbn[dess_mltcbn$Bnb %in% df_plst$Bnb,]
# dess_mltcbn_sbst<-dess_mltcbn_sbst %>% select(Bnb,Glucose,Glycerol,Mannose)
# dess_mltcbn_sbst$CondEssentiality<-"nonessential"
# my_condess<-c(dess_mltcbn_sbst[dess_mltcbn_sbst$Glucose<Growth_thr,]$Bnb,
#   dess_mltcbn_sbst[dess_mltcbn_sbst$Glycerol<Growth_thr,]$Bnb,
#   dess_mltcbn_sbst[dess_mltcbn_sbst$Mannose<Growth_thr,]$Bnb
# ) %>% unique()
# dess_mltcbn_sbst[dess_mltcbn_sbst$Bnb %in% my_condess,]$CondEssentiality<-"conditional"
# 
# dess_ko_sbst<-dess_ko[dess_ko$Bnb %in% df_plst$Bnb,]
# 
# # my_tmp<-dess_mltcbn_sbst %>% select(Bnb,CondEssentiality)
# my_tmp<-dess_ko_sbst %>% select(Bnb,CondEssentiality)
# df_plst<-left_join(df_plst,my_tmp)
# df_plst[df_plst$Essentiality=="essential",]$CondEssentiality<-"essential"

df_plst$StringentSet<-TRUE
df_plst[df_plst$Bnb %in% my_removal_gn,]$StringentSet<-FALSE

Sys.time()
```
## 4.2. Mean Epop vs. SD of Epop (Plasticity)
```{r Noise_Plasticity,warning=FALSE, message=FALSE, fig.width=3,fig.height=3}
p<-ggscatter(df_plst,x="Mean_logAvFITC",y="SD_logAvFITC",
             size=1,alpha=0.5,
             legend="",
             xlab="Mean",ylab="SD of mean",
             cor.coef = TRUE,
             cor.coeff.args = list(method = "spearman", label.x = 3, label.y=0.3, label.sep = "\n",size=5),
             color = "Essentiality",palette =mycolpal[c(1,2)])+
  xlab(expression(Mean~of~E[pop]))+
  ylab(expression(SD~of~E[pop]))
p<-ggpar(p,font.x=my_fontsize,font.y=my_fontsize,font.tickslab = my_fontsize)
p

p<-ggscatter(df_plst,x="Mean_logAvFITC",y="SD_logAvFITC",
             size=2,alpha=0.5,
             label = "Name",repel = T,label.select =qw(pgk,carA),font.label = c(16,"italic"),
             legend="",
             xlab="Mean",ylab="SD of mean",
             cor.coef = TRUE,
             cor.coeff.args = list(method = "spearman", label.x = 3, label.y=0.3, label.sep = "\n",size=5),
             color = "Essentiality",palette =mycolpal[c(1,2)])+
  scale_y_continuous(breaks = get_breaks(by=0.1,from = 0.1,to=0.4),limits = c(0.07,0.42))+
  # geom_text_repel(aes(label=ifelse(Name %in% qw(pgk,carA),Name,""),color=Essentiality))+
  xlab(expression(Mean~of~E[pop]))+
  ylab(expression(SD~of~E[pop]))
p<-ggpar(p,font.x=my_fontsize,font.y=my_fontsize,font.tickslab = my_fontsize)
p
#TODO ggsave(file="Fig2c.svg", path=my_figout,dpi = 300, width = 3, height = 3)

df_plst %>% 
  group_by(Essentiality) %>%
cor_test(vars = Mean_logAvFITC,vars2 = SD_logAvFITC,method="spearman")

Sys.time()
```
## 4.3. Calc. Noise (DMv)
```{r Noise_Plasticity,warning=FALSE, message=FALSE, fig.width=3,fig.height=3}
my_df<-df_stat_flow_rep
my_df<-my_df[!is.na(my_df$log10Av_FITC),]
my_df<-my_df[order(my_df$log10Av_FITC),]
my_df$RMv<-runmed(my_df$log10SD_FITC,41)
SmthSp_v<-createEmptyDf(nrow=1000,ncol=2, colnames = qw(logx,SS))
SmthSp_v$logx=seq(min(my_df$log10Av_FITC),max(my_df$log10Av_FITC),length=nrow(SmthSp_v))
my_splist<-list()
my_splist[[1]]<-smooth.spline(data.frame(x=my_df$log10Av_FITC,y=my_df$RMv),df=12)
SmthSp_v$SS<-predict(my_splist[[1]],SmthSp_v$logx)[[2]]
my_df$SSv<-predict(my_splist[[1]],my_df$log10Av_FITC)[[2]]
my_df$DMv<-my_df$log10SD_FITC-my_df$SSv  # <------------------------------ DMv
df_noise<-my_df
Sys.time()
```
## 4.4. Relationship between mean and noise
```{r Noise_Plasticity,warning=FALSE, message=FALSE, fig.width=3,fig.height=3}
p1<-ggscatter(df_noise,x="log10Av_FITC",y="log10SD_FITC",
          color="Essentiality",palette = mycolpal[c(1,2)],
          # cor.coef = TRUE, # Add correlation coefficient. see ?stat_cor
          # cor.coeff.args = list(method = "spearman", label.x = 11, label.y=2.7, label.sep = "\n",size=5),
          alpha = 0.5, size=0.3,legend="")+
    xlab(expression(E[pop]))+
    ylab(expression(V[pop]))+
  # geom_vline(xintercept = c(7,10),linetype=2,size=0.5)+
  geom_line(data=df_noise,aes(x=log10Av_FITC,y=RMv), colour="magenta", size=1.75)+ # 0.5
  geom_line(data=SmthSp_v,aes(x=logx,y=SS), colour="deepskyblue", size=0.75) # 1
p1<-ggpar(p1,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p1
#TODO ggsave(file="Fig3a_all.svg", path=my_figout,dpi = 300, width = 3, height = 3)

p2<-ggscatter(df_noise,x="log10Av_FITC",y="DMv",
          color="Essentiality",palette = mycolpal[c(1,2)],
          cor.coef = TRUE, # Add correlation coefficient. see ?stat_cor
          cor.coeff.args = list(method = "spearman", label.x = 3, label.y=0.3, label.sep = "\n",size=5),
          alpha = 0.5, size=0.3,legend="")+
  scale_y_continuous(breaks = get_breaks(by=0.2,from = 0,to=0.4),limits = c(-0.06,0.4))+
    xlab(expression(E[pop]))+
    ylab(expression(DM[V]))
p2<-ggpar(p2,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p2

my_df<-df_noise
my_df$class<-"others"
my_df[my_df$Name=="pgk",]$class<-"pgk"
my_df[my_df$Name=="carA",]$class<-"carA"
my_df$class<-factor(my_df$class,levels=qw(carA,pgk,others))
my_df$size<-0.2
my_df[my_df$Name %in% qw(pgk,carA),]$size<-1
my_df<-my_df[order(my_df$class,decreasing = T),]

p3<-ggscatter(my_df, x="log10Av_FITC",y="log10SD_FITC",
          legend="",
   color = "class", palette = mycolpal[c(1,2,8)],
   size = "size", alpha = 0.5)+
  scale_size(range = c(0.2, 3))+
    xlab(expression(E[pop]))+
    ylab(expression(V[pop]))+
  geom_line(data=df_noise,aes(x=log10Av_FITC,y=RMv), colour="magenta", size=1.75)+ # 0.5
  geom_line(data=SmthSp_v,aes(x=logx,y=SS), colour="deepskyblue", size=0.75) # 0.75
p3<-ggpar(p3,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p3
#TODO ggsave(file="Fig3a_rep.svg", path=my_figout,dpi = 300, width = 3, height = 3)

p4<-ggplot()+
  xlab(expression(E[pop]))+
    ylab(expression(V[pop]))+
  geom_line(data=df_noise,aes(x=log10Av_FITC,y=RMv), colour="magenta", size=1.75)+ # 0.5
  geom_line(data=SmthSp_v,aes(x=logx,y=SS), colour="deepskyblue", size=0.75)+ # 0.75
  scale_y_continuous(breaks = get_breaks(by=0.1,from = 0.1,to=0.5),limits = c(0.095,0.573))+
  theme_pubr()
p4<-ggpar(p4,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p4
  
Sys.time()
```
## 4.5. Noise-plasticity coupling
### 4.5.1. 89 genes
```{r Noise_Plasticity,warning=FALSE, message=FALSE, fig.width=3.5,fig.height=3}
df_plst_noise<-df_plst
df_plst_noise$Mean_DMv<-NA
for(i in 1:nrow(df_plst_noise)){
  my_tmp<-df_noise[df_noise$Bnb==df_plst_noise$Bnb[i],]
  df_plst_noise$Mean_DMv[i]<-mean(my_tmp$DMv,na.rm=T)
}
my_tmp<-genename.mg1655[genename.mg1655$Bnb %in% df_plst_noise$Bnb,] %>% select(Bnb,EntrezID)
df_plst_noise<-left_join(df_plst_noise,my_tmp)

p1<-ggscatter(df_plst_noise,x="SD_logAvFITC",y="Mean_DMv",
          color="Essentiality",palette = mycolpal[c(1,2)],
          cor.coef = TRUE, # Add correlation coefficient. see ?stat_cor
          cor.coeff.args = list(method = "spearman", label.x = 0.25, label.y=0.08, label.sep = "\n",size=5),
          alpha = 0.5, size=2,legend="")+
   scale_y_continuous(breaks = get_breaks(by=0.04,from = 0,to=0.08),limits = c(-0.02,0.1))+
  scale_x_continuous(breaks = get_breaks(by=0.1,from = 0.1,to=0.4),limits = c(0.07,0.43))+
    xlab(expression("SD of"~E[pop]))+
    ylab(expression("Mean DM"[V]))
p1<-ggpar(p1,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p1
#TODO ggsave(file="Fig4a_pool.svg", path=my_figout,dpi = 300, width = 3.5, height = 3)

p2<-ggscatter(df_plst_noise,x="SD_logAvFITC",y="Mean_DMv",
          color="Essentiality",palette = mycolpal[c(1,2)],
          cor.coef = TRUE, # Add correlation coefficient. see ?stat_cor
          cor.coeff.args = list(method = "spearman", label.x = 0.2, label.y=0.07, label.sep = "\n",size=5),
          alpha = 0.5, size=0.5,legend="")+
  scale_y_continuous(breaks = get_breaks(by=0.04,from = 0,to=0.08),limits = c(-0.02,0.12))+
  stat_cor(aes(color = Essentiality), label.x = 0.1, size=4,method = "spearman")+
    xlab(expression("SD of"~E[pop]))+
    ylab(expression("Mean DM"[V]))
p2<-ggpar(p2,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p2

p3<-ggscatter(df_plst_noise[df_plst_noise$Essentiality=="nonessential",],x="SD_logAvFITC",y="Mean_DMv",
          color=mycolpal[1],
          label="Name",repel=T,label.select = list(criteria = "`x` > 0.25 | `y` > 0.02"),font.label = c("italic"),
          cor.coef = TRUE, # Add correlation coefficient. see ?stat_cor
          cor.coeff.args = list(method = "spearman", label.x = 0.25, label.y=0.08, label.sep = "\n",size=5),
          alpha = 0.5, size=2,legend="")+
  scale_y_continuous(breaks = get_breaks(by=0.04,from = 0,to=0.08),limits = c(-0.02,0.1))+
  scale_x_continuous(breaks = get_breaks(by=0.1,from = 0.1,to=0.4),limits = c(0.07,0.43))+
    xlab(expression("SD of"~E[pop]))+
    ylab(expression("Mean DM"[V]))
p3<-ggpar(p3,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p3
#TODO ggsave(file="Fig4a_nes.svg", path=my_figout,dpi = 300, width = 3.5, height = 3)

p4<-ggscatter(df_plst_noise[df_plst_noise$Essentiality=="essential",],x="SD_logAvFITC",y="Mean_DMv",
          color=mycolpal[2],
          label="Name",repel=T,label.select = list(criteria = "`x` > 0.21 | `y` > 0.02"),font.label = c("italic"),
          cor.coef = TRUE, # Add correlation coefficient. see ?stat_cor
          cor.coeff.args = list(method = "spearman", label.x = 0.25, label.y=0.08, label.sep = "\n",size=5),
          alpha = 0.5, size=2,legend="")+
  scale_y_continuous(breaks = get_breaks(by=0.04,from = 0,to=0.08),limits = c(-0.02,0.1))+
  scale_x_continuous(breaks = get_breaks(by=0.1,from = 0.1,to=0.4),limits = c(0.07,0.43))+
    xlab(expression("SD of"~E[pop]))+
    ylab(expression("Mean DM"[V]))
p4<-ggpar(p4,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p4
#TODO ggsave(file="Fig4a_ess.svg", path=my_figout,dpi = 300, width = 3.5, height = 3)

# check robustness of the correlation coeff. by removing the three outliers (genes showing very high DMv).
p5<-ggscatter(df_plst_noise[(df_plst_noise$Essentiality=="essential")&(df_plst_noise$Mean_DMv<0.01),],x="SD_logAvFITC",y="Mean_DMv",
          color=mycolpal[2],
          cor.coef = TRUE, # Add correlation coefficient. see ?stat_cor
          cor.coeff.args = list(method = "spearman", label.x = 0.2, label.y=0.07, label.sep = "\n",size=5),
          alpha = 0.5, size=2,legend="")+
  scale_y_continuous(breaks = get_breaks(by=0.04,from = 0,to=0.08),limits = c(-0.02,0.1))+
  scale_x_continuous(breaks = get_breaks(by=0.1,from = 0.1,to=0.4),limits = c(0.07,0.43))+
    xlab(expression("SD of"~E[pop]))+
    ylab(expression("Mean DM"[V]))
p5<-ggpar(p5,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p5

Sys.time()
```
### 4.5.2. Genes without conditional essential genes
```{r Noise_Plasticity,warning=FALSE, message=FALSE, fig.width=3.5,fig.height=3}
df_plst_noise_sbst<-df_plst_noise[df_plst_noise$StringentSet,]

p1<-ggscatter(df_plst_noise_sbst,x="SD_logAvFITC",y="Mean_DMv",
          color="Essentiality",palette = mycolpal[c(1,2)],
          cor.coef = TRUE, # Add correlation coefficient. see ?stat_cor
          cor.coeff.args = list(method = "spearman", label.x = 0.25, label.y=0.08, label.sep = "\n",size=5),
          alpha = 0.5, size=2,legend="")+
   scale_y_continuous(breaks = get_breaks(by=0.04,from = 0,to=0.08),limits = c(-0.02,0.1))+
  scale_x_continuous(breaks = get_breaks(by=0.1,from = 0.1,to=0.4),limits = c(0.07,0.43))+
    xlab(expression("SD of"~E[pop]))+
    ylab(expression("Mean DM"[V]))
p1<-ggpar(p1,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p1

p2<-ggscatter(df_plst_noise_sbst,x="SD_logAvFITC",y="Mean_DMv",
          color="Essentiality",palette = mycolpal[c(1,2)],
          cor.coef = TRUE, # Add correlation coefficient. see ?stat_cor
          cor.coeff.args = list(method = "spearman", label.x = 0.2, label.y=0.07, label.sep = "\n",size=5),
          alpha = 0.5, size=0.5,legend="")+
  scale_y_continuous(breaks = get_breaks(by=0.04,from = 0,to=0.08),limits = c(-0.02,0.12))+
  stat_cor(aes(color = Essentiality), label.x = 0.1, size=4,method = "spearman")+
    xlab(expression("SD of"~E[pop]))+
    ylab(expression("Mean DM"[V]))
p2<-ggpar(p2,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p2

p3<-ggscatter(df_plst_noise_sbst[df_plst_noise_sbst$Essentiality=="nonessential",],x="SD_logAvFITC",y="Mean_DMv",
          color=mycolpal[1],
          label="Name",repel=T,label.select = list(criteria = "`x` > 0.25 | `y` > 0.02"),font.label = c("italic"),
          cor.coef = TRUE, # Add correlation coefficient. see ?stat_cor
          cor.coeff.args = list(method = "spearman", label.x = 0.25, label.y=0.08, label.sep = "\n",size=5),
          alpha = 0.5, size=2,legend="")+
  scale_y_continuous(breaks = get_breaks(by=0.04,from = 0,to=0.08),limits = c(-0.02,0.1))+
  scale_x_continuous(breaks = get_breaks(by=0.1,from = 0.1,to=0.4),limits = c(0.07,0.43))+
    xlab(expression("SD of"~E[pop]))+
    ylab(expression("Mean DM"[V]))
p3<-ggpar(p3,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p3

p4<-ggscatter(df_plst_noise_sbst[df_plst_noise_sbst$Essentiality=="essential",],x="SD_logAvFITC",y="Mean_DMv",
          color=mycolpal[2],
          label="Name",repel=T,label.select = list(criteria = "`x` > 0.21 | `y` > 0.02"),font.label = c("italic"),
          cor.coef = TRUE, # Add correlation coefficient. see ?stat_cor
          cor.coeff.args = list(method = "spearman", label.x = 0.25, label.y=0.08, label.sep = "\n",size=5),
          alpha = 0.5, size=2,legend="")+
  scale_y_continuous(breaks = get_breaks(by=0.04,from = 0,to=0.08),limits = c(-0.02,0.1))+
  scale_x_continuous(breaks = get_breaks(by=0.1,from = 0.1,to=0.4),limits = c(0.07,0.43))+
    xlab(expression("SD of"~E[pop]))+
    ylab(expression("Mean DM"[V]))
p4<-ggpar(p4,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p4


Sys.time()
```
## 4.6. Comparison on Noise/Plasticity between essential and nonessential genes
### 4.6.1. 89 genes
```{r Noise_Plasticity,warning=FALSE, message=FALSE, fig.width=3.5,fig.height=3}
p1<-ggboxplot(df_plst_noise,x="Essentiality",y="SD_logAvFITC",
          color="Essentiality",palette = mycolpal[c(1,2)],
          add="jitter",add.params = list(size = 0.5, jitter = 0.2,alpha=0.5),
          xlab="",
          legend="")+
  stat_compare_means(size=5,label.y = 0.45)+
  scale_y_continuous(breaks = get_breaks(by=0.1,from = 0.1,to=0.4),limits = c(0.08,0.5))+
    ylab(expression("SD of"~E[pop]))
p1<-ggpar(p1,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p1
#TODO ggsave(file="Fig2d.svg", path=my_figout,dpi = 300, width = 3.5, height = 3)

p2<-ggboxplot(df_plst_noise,x="Essentiality",y="Mean_DMv",
          color="Essentiality",palette = mycolpal[c(1,2)],
          add="jitter",add.params = list(size = 0.5, jitter = 0.2,alpha=0.5),
          xlab="",
          legend="")+
  stat_compare_means(size=5,label.y = 0.1)+
scale_y_continuous(breaks = get_breaks(by=0.04,from = 0,to=0.08),limits = c(-0.02,0.12))+
    ylab(expression(Mean~DM[V]))
p2<-ggpar(p2,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p2
#TODO ggsave(file="Fig3b.svg", path=my_figout,dpi = 300, width = 3.5, height = 3)

print(paste("Nb. of essential genes:",nrow(df_plst_noise[df_plst_noise$Essentiality=="essential",]),sep=" "))
print(paste("Nb. of nonessential genes:",nrow(df_plst_noise[df_plst_noise$Essentiality=="nonessential",]),sep=" "))
Sys.time()
```
### 4.6.2. Genes without conditional essential genes
```{r Noise_Plasticity,warning=FALSE, message=FALSE, fig.width=3.5,fig.height=3}
p1<-ggboxplot(df_plst_noise_sbst,x="Essentiality",y="SD_logAvFITC",
          color="Essentiality",palette = mycolpal[c(1,2)],
          add="jitter",add.params = list(size = 0.5, jitter = 0.2,alpha=0.5),
          xlab="",
          legend="")+
  stat_compare_means(size=5,label.y = 0.45)+
  scale_y_continuous(breaks = get_breaks(by=0.1,from = 0.1,to=0.4),limits = c(0.08,0.5))+
    ylab(expression("SD of"~E[pop]))
p1<-ggpar(p1,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p1

p2<-ggboxplot(df_plst_noise_sbst,x="Essentiality",y="Mean_DMv",
          color="Essentiality",palette = mycolpal[c(1,2)],
          add="jitter",add.params = list(size = 0.5, jitter = 0.2,alpha=0.5),
          xlab="",
          legend="")+
  stat_compare_means(size=5,label.y = 0.1)+
scale_y_continuous(breaks = get_breaks(by=0.04,from = 0,to=0.08),limits = c(-0.02,0.12))+
    ylab(expression(Mean~DM[V]))
p2<-ggpar(p2,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p2

print(paste("Nb. of essential genes:",nrow(df_plst_noise_sbst[df_plst_noise_sbst$Essentiality=="essential",]),sep=" "))
print(paste("Nb. of nonessential genes:",nrow(df_plst_noise_sbst[df_plst_noise_sbst$Essentiality=="nonessential",]),sep=" "))
Sys.time()
```

# 5. Transcriptional Regulators
## 5.1. Retrieve Transcriptional Regulators (TRs)
TRN based on RegulonDB & Ecocyc
```{r TR,warning=FALSE, message=FALSE,fig.height=2,fig.width=2,dpi=300}
# Load TRN dataset from RegulonDB
TRN<-paste(getwd(),"RegulonDB","2022_ver_11","Output","trn.regulator_gene.csv",sep="/") %>%
  read_csv() %>%
  data.frame()
# rename regulator
# CRP to Crp, Dan to TtdR, FNR to Fnr, HigB-A to HigBA, MatA to EcpR
TRN[TRN$regulator=="CRP",]$regulator<-"Crp"
TRN[TRN$regulator=="Dan",]$regulator<-"TtdR"
TRN[TRN$regulator=="FNR",]$regulator<-"Fnr"
TRN[TRN$regulator=="HigB-HigA",]$regulator<-"HigBA"
TRN[TRN$regulator=="MatA",]$regulator<-"EcpR"

# Load dataset of ECOCYC
ecocyc.all.genes<-paste(getwd(),"ECOCYC","2022_10_09_Ecocyc","All_Genes.csv",sep="/") %>%
  read_csv() %>%
  data.frame()
ecocyc.sub.genes<-ecocyc.all.genes[!is.na(ecocyc.all.genes$Bnb),]
# length(unique(ecocyc.sub.genes$Bnb))
# load data set for TF
ecocyc.all.tfs<-paste(getwd(),"ECOCYC","2022_10_09_Ecocyc","All_transcription_factors.csv",sep="/") %>%
  read_csv() %>%
  data.frame()
temp<-paste(getwd(),"ECOCYC","2022_10_09_Ecocyc","Cure01_transcription_factors.csv",sep="/") %>%
  read_csv() %>%
  data.frame()
ecocyc.all.tfs<-bind_rows(ecocyc.all.tfs,temp)
# check name space of regulator
ecocyc.all.tfs[ecocyc.all.tfs$regulator %nin% unique(TRN$regulator),]$regulator
unique(TRN[TRN$regulator %nin% ecocyc.all.tfs$regulator,]$regulator)

mycolname<-qw(regulator,gene_name,gene_id,effect,evidence,source,category,regulator_label,Use,regulator_id)
for(i in 1:nrow(ecocyc.all.tfs)){
  temp0<-unique(str_split(ecocyc.all.tfs$Regulated_Bnb[i],",")[[1]])
  temp0<-temp0[grepl("^b",temp0)]
  temp1<-createEmptyDf(nrow=length(temp0),ncol=length(mycolname),colnames = mycolname)
  temp1$regulator<-ecocyc.all.tfs$regulator[i]
  temp1$regulator_id<-ecocyc.all.tfs$Bnb[i]
  temp1$category<-ecocyc.all.tfs$Category[i]
  temp1$gene_id<-temp0
  temp1.1<-c()
  if(!is.na(ecocyc.all.tfs$Inhibited_Bnb[i])){
    temp1.1<-unique(str_split(ecocyc.all.tfs$Inhibited_Bnb[i],",")[[1]])
    temp1.1<-temp1.1[grepl("^b",temp1.1)]
  }
  temp1.2<-c()
  if(!is.na(ecocyc.all.tfs$Activated_Bnb[i])){
    temp1.2<-unique(str_split(ecocyc.all.tfs$Activated_Bnb[i],",")[[1]])
    temp1.2<-temp1.2[grepl("^b",temp1.2)]
  }
  for(j in 1:nrow(temp1)){
    temp1$gene_name[j]<-ecocyc.sub.genes[ecocyc.sub.genes$Bnb==temp1$gene_id[j],]$Gene
    if(length(temp1.1[temp1.1==temp1$gene_id[j]])>0&length(temp1.2[temp1.2==temp1$gene_id[j]])>0){
      temp1$effect[j]<-"+,-"
    }else if(length(temp1.1[temp1.1==temp1$gene_id[j]])>0&length(temp1.2[temp1.2==temp1$gene_id[j]])==0){
      temp1$effect[j]<-"-"
    }else if(length(temp1.1[temp1.1==temp1$gene_id[j]])==0&length(temp1.2[temp1.2==temp1$gene_id[j]])>0){
      temp1$effect[j]<-"+"
    }
  }
  if(i==1){
    temp4.1<-temp1
  }else{
    temp4.1<-bind_rows(temp4.1,temp1)
  }
}
temp4.1$source<-"Ecocyc"

# load data set for Sigma
ecocyc.sigmulon<-paste(getwd(),"ECOCYC","2022_10_09_Ecocyc","Sigmulon.csv",sep="/") %>%
  read_csv() %>%
  data.frame()
for(i in 1:nrow(ecocyc.sigmulon)){
  temp2.1<-unique(str_split(ecocyc.sigmulon$Activation[i],",")[[1]])
  temp2.1<-unique(ecocyc.sub.genes[ecocyc.sub.genes$Gene %in% temp2.1,]$Bnb)
  temp2.1<-temp2.1[grepl("^b",temp2.1)]
  temp2.2<-createEmptyDf(nrow=length(temp2.1),ncol=length(mycolname),colnames = mycolname)
  temp2.2$regulator<-ecocyc.sigmulon$Sigma[i]
  temp2.2$regulator_id<-ecocyc.sigmulon$Bnb[i]
  temp2.2$effect<-"+"
  temp2.2$category<-"sigma"
  temp2.2$gene_id<-temp2.1
  for(j in 1:nrow(temp2.2)){
    temp2.2$gene_name[j]<-ecocyc.sub.genes[ecocyc.sub.genes$Bnb==temp2.2$gene_id[j],]$Gene
  }
  if(i==1){
    temp4.2<-temp2.2
  }else{
    temp4.2<-bind_rows(temp4.2,temp2.2)
  }
}
temp4.2$source<-"Ecocyc"
temp4<-bind_rows(temp4.1,temp4.2)

# fix Bnb
temp5<-temp4 %>% distinct(regulator,.keep_all = T)
for(i in 1:nrow(temp5)){
  temp6<-TRN[TRN$regulator==temp5$regulator[i],]
  if(nrow(temp6)>0){
    temp5$regulator_id[i]<-unique(temp6$regulator_id)
  }
}
for(i in 1:nrow(temp5)){
  temp4[temp4$regulator==temp5$regulator[i],]$regulator_id<-temp5$regulator_id[i]
}



# add regulator_id (Bnb)
# TRN<-left_join(TRN,temp5[,which(colnames(temp5) %in% qw(regulator,regulator_id)),],by="regulator")

# update effect
for (i in 1:nrow(TRN)){
  if(TRN$effect[i] %nin% c("+","-","+,-")&!is.na(TRN$regulator_id[i])){
    temp6<-temp4[(temp4$regulator_id==TRN$regulator_id[i])&temp4$gene_id==TRN$gene_id[i],]
    if(nrow(temp6)==1){
      if(!is.na(temp6$effect)){
        TRN$effect[i]<-temp6$effect
      }
    }
  }
}


# Unique interactions in Ecocyc smart table
temp7<-temp4
temp7$prsn_in_TRN<-NA
for(i in 1:nrow(temp7)){
  if(nrow(TRN[(TRN$regulator==temp7$regulator[i])&(TRN$gene_id==temp7$gene_id[i]),])>0){
    temp7$prsn_in_TRN[i]<-"Yes"
  }
}
temp7<-temp7[is.na(temp7$prsn_in_TRN),]
temp7[is.na(temp7$effect),]$effect<-""
temp7<-temp7[temp7$gene_id %in% genename.mg1655$Bnb,]
temp8<-TRN %>% distinct(regulator,.keep_all = T)
for(i in 1:nrow(temp7)){
  temp9<-genename.mg1655[genename.mg1655$Bnb==temp7$gene_id[i],]$gene
  if(length(temp9)==1){
    temp7$gene_name[i]<-temp9
  }
  # temp10<-temp8[temp8$regulator==temp7$regulator[i],]$regulator_label
  # if(length(temp10)==1){
  #   temp7$regulator_label[i]<-temp10
  #   temp7$Use[i]<-temp8[temp8$regulator==temp7$regulator[i],]$Use
  # }else{
  #   temp7$regulator_label[i]<-temp7$regulator[i]
  #   temp7$Use[i]<-"Yes"
  # }
}
temp7$evidence<-NA
TRN<-bind_rows(TRN,temp7[,which(colnames(temp7) %nin% qw(prsn_in_TRN))])

# Use gene name space in MG1655
TRN<-TRN[TRN$gene_id %in% genename.mg1655$Bnb,]
i<-1
for(i in 1:nrow(TRN)){
  if(grepl("^b",TRN$gene_id[i])){
    TRN$gene_name[i]<-genename.mg1655[genename.mg1655$Bnb==TRN$gene_id[i],]$gene
  }
}

# Check duplication of interactions
temp<-TRN %>% distinct(regulator,gene_id,.keep_all = T)
j<-1
k<-1
temp2<-createEmptyDf(nrow=0,ncol=1,colnames="x")
nrow(temp2)
for(i in 1:nrow(temp)){
  temp1<-TRN[(TRN$regulator==temp$regulator[i])&(TRN$gene_id==temp$gene_id[i]),]
  if(nrow(temp1)>1){
    if(j==1){
      temp2<-temp1
      j<-j+1
    }else{
      temp2<-rbind(temp2,temp1)
    }
  }else{
    if(k==1){
      temp3<-temp1
      k<-k+1
    }else{
      temp3<-rbind(temp3,temp1)
    }
  }
}
if(nrow(temp2)>0){
  temp2<-temp2[!is.na(temp2$evidence),]
  temp2<-temp2 %>% distinct(regulator,gene_id,.keep_all = T)
  TRN<-bind_rows(temp3,temp2)
}
Sys.time()
```
## 5.2.  Retrieve Sensory Regulators (SRs)
http://regulondb.ccg.unam.mx/menu/about_regulondb/cellsensing/index.jsp
https://citeseerx.ist.psu.edu/document?repid=rep1&type=pdf&doi=62adcb9d37fa4257d6d5e74cdade4870ff9faf45
```{r TR,warning=FALSE, message=FALSE,fig.height=2,fig.width=2,dpi=300}
# Rename
my_cure<-paste(getwd(),"RegulonDB","Cell_Sensing","Cell_Sensing.xlsx",sep="/") %>%
  read_xlsx(sheet = "Cure")
my_cure<-my_cure[!is.na(my_cure$Ecocyc),]

# E-TC
#  Include TFs forming part of two-component systems, the signals are sensed by the sensor component (most of them located in the bacterial periplasm)
df_cs_e_tc<-paste(getwd(),"RegulonDB","Cell_Sensing","Cell_Sensing.xlsx",sep="/") %>%
  read_xlsx(sheet = "E-TC")
colnames(df_cs_e_tc)[1]<-"regulator"
df_cs_e_tc$regulator<-str_replace(df_cs_e_tc$regulator, pattern="/", replacement="")
df_cs_e_tc$regulator<-str_replace(df_cs_e_tc$regulator, pattern="\\?", replacement="")
for(i in 1:nrow(df_cs_e_tc)){
  temp<-my_cure[my_cure$RegulonDB==df_cs_e_tc$regulator[i],]
  if(nrow(temp)==1){
    df_cs_e_tc$regulator[i]<-temp$Ecocyc
  }
}
df_cs_e_tc<-df_cs_e_tc[df_cs_e_tc$regulator %in% unique(TRN$regulator),]

# E-TM
#  Include TFs sensing transportable metabolites; these TFs work in close connection with transport systems that sense/introduce specific metabolites from the milieu. The metabolites bound/sensed by this kind of TF are not anymore modified by the cell metabolism except those modifications inherent to the transport events (e.g. phosphorylation).
df_cs_e_tm<-paste(getwd(),"RegulonDB","Cell_Sensing","Cell_Sensing.xlsx",sep="/") %>%
  read_xlsx(sheet = "E-TM")
colnames(df_cs_e_tm)[1]<-"regulator"
i<-17
for(i in 1:nrow(df_cs_e_tm)){
  df_cs_e_tm$regulator[i]<-str_split(df_cs_e_tm$regulator[i],pattern = " ")[[1]][1]
}
for(i in 1:nrow(df_cs_e_tm)){
  temp<-my_cure[my_cure$RegulonDB==df_cs_e_tm$regulator[i],]
  if(nrow(temp)==1){
    df_cs_e_tm$regulator[i]<-temp$Ecocyc
  }
}
df_cs_e_tm<-df_cs_e_tm[df_cs_e_tm$regulator %in% unique(TRN$regulator),]

# H
# Includes hybrid TFs, thus named because both bind/sense metabolites produced by the cell and transported from the milieu (mostly for sensing amino acids that in addition to be synthesized by the cell can be transported into the cell from the milieu).
df_cs_h<-paste(getwd(),"RegulonDB","Cell_Sensing","Cell_Sensing.xlsx",sep="/") %>%
  read_xlsx(sheet = "H")
colnames(df_cs_h)[1]<-"regulator"
df_cs_h$regulator<-str_replace(df_cs_h$regulator, pattern="\\*", replacement="")
for(i in 1:nrow(df_cs_h)){
  df_cs_h$regulator[i]<-str_split(df_cs_h$regulator[i],pattern = " ")[[1]][1]
}
for(i in 1:nrow(df_cs_h)){
  temp<-my_cure[my_cure$RegulonDB==df_cs_h$regulator[i],]
  if(nrow(temp)==1){
    df_cs_h$regulator[i]<-temp$Ecocyc
  }
}
df_cs_h<-df_cs_h[df_cs_h$regulator %in% unique(TRN$regulator),]

# I-SM
# Include TFs binding/sensing metabolites generated by the cellular metabolism; by enzymatic reactions (sugar, nucleotides, cofactors, etc) or generated as byproducts of biochemical reactions (e.g. redox potential).
df_cs_i_sm<-paste(getwd(),"RegulonDB","Cell_Sensing","Cell_Sensing.xlsx",sep="/") %>%
  read_xlsx(sheet = "I-SM")
colnames(df_cs_i_sm)[1]<-"regulator"
for(i in 1:nrow(df_cs_i_sm)){
  df_cs_i_sm$regulator[i]<-str_split(df_cs_i_sm$regulator[i],pattern = " ")[[1]][1]
}
for(i in 1:nrow(df_cs_i_sm)){
  temp<-my_cure[my_cure$RegulonDB==df_cs_i_sm$regulator[i],]
  if(nrow(temp)==1){
    df_cs_i_sm$regulator[i]<-temp$Ecocyc
  }
}
df_cs_i_sm<-df_cs_i_sm[df_cs_i_sm$regulator %in% unique(TRN$regulator),]


# I-DB
#  Include DNA-bending TFs for nucleoid or chromosome remodeling and compaction, the activity of this kind of TF is not directly affected by signal effectors but possibly by DNA supercoiling or macromolecular crowding.
df_cs_i_db<-paste(getwd(),"RegulonDB","Cell_Sensing","Cell_Sensing.xlsx",sep="/") %>%
  read_xlsx(sheet = "I-DB")
colnames(df_cs_i_db)[1]<-"regulator"
df_cs_i_db<-df_cs_i_db[df_cs_i_db$regulator %in% unique(TRN$regulator),]

# From sensory 
df_ec_eff<-paste(getwd(),"ECOCYC","2022_10_09_Ecocyc","transcription_factors_effectors.csv",sep="/") %>%
  read_csv() %>%
  data.frame()
df_ec_eff<-df_ec_eff[!is.na(df_ec_eff$Effectors),]
df_ec_eff<-df_ec_eff[df_ec_eff$regulator %in% unique(TRN$regulator),]

sensory_tfs<-unique(c(df_cs_e_tc$regulator,
                    df_cs_e_tm$regulator,
                    df_cs_h$regulator,
                    df_cs_i_sm$regulator,
                    df_cs_i_db$regulator,
                    df_ec_eff$regulator))
print(paste("Sensory Regulators:",paste(sensory_tfs,collapse = ",")))

Sys.time()
```
## 5.3.  Retrieve Metabolic-sensory regulators (MSRs)
https://www.nature.com/articles/s41467-019-12474-1
```{r TR,warning=FALSE, message=FALSE,fig.width=10}
df_tfmet<-paste(getwd(),"Metabolite_TF_Interactions","Suppl_7.csv",sep = "/") %>%
  read_csv(show_col_types = F) %>%
  data.frame()
df_tfmet1<-createEmptyDf(nrow = length(unique(df_tfmet$Transcription_Factor)),ncol = 3,colnames = qw(regulator,Nb_of_Metabolite,List_of_Metabolites))
df_tfmet1$regulator<-unique(df_tfmet$Transcription_Factor)
for (i in 1:nrow(df_tfmet1)) {
  tfmet_temp<-subset(df_tfmet,df_tfmet$Transcription_Factor==df_tfmet1$regulator[i])
  df_tfmet1$Nb_of_Metabolite[i]<-nrow(tfmet_temp)
  df_tfmet1$List_of_Metabolites[i]<-paste(tfmet_temp$Metabolite,collapse = ";")
}

df_tftrgt<-paste(getwd(),"Metabolite_TF_Interactions","Suppl_8mod.csv",sep = "/") %>%
  read_csv(show_col_types = F) %>%
  data.frame()
tflist<-colnames(df_tftrgt)[2:length(colnames(df_tftrgt))]
df_msr<-createEmptyDf(nrow = length(tflist),ncol = 1,colnames = qw(regulator))
df_msr$regulator<-tflist
df_msr<-left_join(df_msr,df_tfmet1,by=c("regulator"))
df_msr<-transform(df_msr,regulator_Met=NA,Median_HillCoeff_h=NA,Median_HillCoeff_k=NA,Median_HillCoeff_v=NA)

df_tfmethill<-paste(getwd(),"Metabolite_TF_Interactions","Met_TF_Hillfit.csv",sep = "/") %>%
  read_csv(show_col_types = F) %>%
  data.frame()
for(i in 1:nrow(df_msr)){
  if(is.na(df_msr$Nb_of_Metabolite[i])==F){
    df_msr$regulator_Met[i]<-paste("<<",paste(df_msr[i,1:3],collapse = "**"),">>",sep = "")
    tf_met_hill<-subset(df_tfmethill,df_tfmethill$TFA_Name==df_msr$regulator[i])
    if(is.na(nrow(tf_met_hill))==F){
      df_msr$Median_HillCoeff_h[i]<-median(tf_met_hill$Coeff_h)
      df_msr$Median_HillCoeff_k[i]<-median(tf_met_hill$Coeff_k)
      df_msr$Median_HillCoeff_v[i]<-median(tf_met_hill$Coeff_v)
    }
  }else{
    df_msr$regulator_Met[i]<-df_msr$regulator[i]
  }
}

my_tmp<-paste(getwd(),"Metabolite_TF_Interactions","TR_name_cure.xlsx",sep = "/") %>%
  read_xlsx() %>%
  data.frame()
for(i in 1:nrow(my_tmp)){
  df_msr[df_msr$regulator==my_tmp$Before[i],]$regulator<-my_tmp$After[i]
}

df_msr[!is.na(df_msr$Nb_of_Metabolite),] %>% nrow()
df_msr[!is.na(df_msr$Nb_of_Metabolite),]$List_of_Metabolites %>% paste(collapse = ";") %>% str_split(pattern = ";") %>% unlist() %>% unique() %>% length()
Sys.time()
```
## 5.4. Integrate all regulatory infomation and Noise/Plasticity data into one
```{r TR,warning=FALSE, message=FALSE,fig.height=3,fig.width=4.5,dpi=300}
df_trn<-TRN
df_trn<-df_trn[!is.na(df_trn$gene_id),]

df_reg<-df_plst_noise %>% select(Bnb,Name)
df_reg<-df_reg[!is.na(df_reg$Bnb),]
df_reg$act<-0
df_reg$inh<-0
df_reg$Nb_reg<-0 # all TRs (TFs and sigmas)
df_reg$Regulator<-NA
df_reg$Nb_TRcom<-0 # TRcoms
df_reg$Nb_SR<-0 # all seonsory regulators
df_reg$Nb_MSR<-0 # metabolic sensory regulators
df_reg$Nb_Mtblt<-0
df_reg$MSR<-NA

df_trn<-df_trn[df_trn$gene_id %in% df_reg$Bnb,]
df_trn<-df_trn[df_trn$effect %nin% "?",]

TRcoms<-c("Nac","RpoS","Lrp","ArcA","Crp","Fis","IHF","Fur","Fnr","H-NS","IscR","FlhDC","FliA")
my_msr<-df_msr[!is.na(df_msr$Nb_of_Metabolite),]$regulator

i<-1
for(i in 1:nrow(df_reg)){
  my_tmp<-df_trn[df_trn$gene_id==df_reg$Bnb[i],]
  if(nrow(my_tmp)>0){
    df_reg$act[i]<-nrow(my_tmp[my_tmp$effect %in% c("+","+,-","-,+"),])
    df_reg$inh[i]<-nrow(my_tmp[my_tmp$effect %in% c("-","+,-","-,+"),])
    df_reg$Nb_reg[i]<-length(unique(my_tmp$regulator))
    df_reg$Regulator[i]<-paste(my_tmp$regulator,collapse = ";")
    df_reg$Nb_TRcom[i]<-length(unique(my_tmp[my_tmp$regulator %in% TRcoms,]$regulator))
    df_reg$Nb_SR[i]<-length(unique(my_tmp[my_tmp$regulator %in% sensory_tfs,]$regulator))
    my_tmp2<-df_msr[(!is.na(df_msr$Nb_of_Metabolite))&(df_msr$regulator %in% my_tmp$regulator),]
    my_sum<-0
    if(nrow(my_tmp2)>0){
      my_sum<-paste(my_tmp2$List_of_Metabolites,collapse = ";") %>% 
        str_split(.,pattern = ";")
      my_sum<-my_sum[[1]] %>% 
        unique() %>% 
        length()
    }
    df_reg$Nb_MSR[i]<-length(unique(my_tmp[my_tmp$regulator %in% my_msr,]$regulator))
    df_reg$Nb_Mtblt[i]<-my_sum
    if(df_reg$Nb_MSR[i]>0){
      df_reg$MSR[i]<-unique(my_tmp[my_tmp$regulator %in% my_msr,]$regulator) %>% paste(.,collapse=";")
    }
  }
}

df_reg$TR_flag<-"Presence"
df_reg[df_reg$Nb_reg==0,]$TR_flag<-"Absence"
df_reg$TR_flag<-factor(df_reg$TR_flag,levels=c("Absence","Presence"))

df_reg$TRcom_flag<-"Presence"
df_reg[df_reg$Nb_TRcom==0,]$TRcom_flag<-"Absence"
df_reg$TRcom_flag<-factor(df_reg$TRcom_flag,levels=c("Absence","Presence"))

df_reg$SR_flag<-"Presence"
df_reg[df_reg$Nb_SR==0,]$SR_flag<-"Absence"
df_reg$SR_flag<-factor(df_reg$SR_flag,levels=c("Absence","Presence"))

df_reg$MSR_flag<-"Presence"
df_reg[df_reg$Nb_MSR==0,]$MSR_flag<-"Absence"
df_reg$MSR_flag<-factor(df_reg$MSR_flag,levels=c("Absence","Presence"))

dtf<-left_join(df_reg,df_plst_noise)

my_sigmas<-qw(RpoD,RpoE,RpoN,RpoH,RpoS,FliA,FecI)
my_sig_comb<-qw(RpoD,RpoD_RpoX,RpoX,NA)
dtf$Sigma<-NA
dtf$Sigma_label<-NA
i<-1
for(i in 1:nrow(dtf)){
  if(dtf$Nb_reg[i]>0){
    my_tmp<-dtf$Regulator[i] %>% str_split(.,pattern=";") %>% unlist()
    my_tmp<-my_tmp[my_tmp %in% my_sigmas]
    if(length(my_tmp)>0){
      my_tmp <-my_tmp[order(my_tmp)]
      dtf$Sigma[i]<-my_tmp %>% paste(.,collapse = ";")
      if(length(my_tmp)==1){
        if(my_tmp=="RpoD"){
          dtf$Sigma_label[i]<-"RpoD"
        }
        if(my_tmp=="RpoS"){
          dtf$Sigma_label[i]<-"RpoS"
        }
      }
      if(length(my_tmp)>1){
        my_tmp2<-my_tmp[my_tmp %in% "RpoD"]
        if(length(my_tmp2)>0){
          my_tmp3<-my_tmp[my_tmp %in% "RpoS"]
          if(length(my_tmp3)>0){
            dtf$Sigma_label[i]<-"RpoD_RpoS"
          }else{
            dtf$Sigma_label[i]<-"RpoD"
          }
        }
      }
    }
  }
}
dtf[is.na(dtf$Sigma_label),]$Sigma_label<-"No_RpoDS"


Sys.time()
```
## 5.5. Comparison in the number of regulators between essential and nonessential genes
```{r TR,warning=FALSE, message=FALSE,fig.height=3,fig.width=4,dpi=300}
#TRs
p1<-ggdotplot(dtf,x="Essentiality",y="Nb_reg",
                add="mean_sd",
          color="Essentiality",palette = mycolpal[c(1,2)],alpha=0.3,
          # palette = mycolpal[1],
          # add.params = list(size = 0.5, jitter = 0.2,alpha=0.5),
          legend="",xlab="",ylab="Number of TRs")+
  stat_compare_means(size=5,label.y = 15)+
  scale_y_continuous(breaks = get_breaks(by=5,from = 0),limits = c(-1,17))
p1<-ggpar(p1,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p1

#MSRs
p2<-ggdotplot(dtf,x="Essentiality",y="Nb_MSR",
                add="mean_sd",
          color="Essentiality",palette = mycolpal[c(1,2)],alpha=0.3,
          # palette = mycolpal[1],
          # ,add.params = list(size = 0.5, jitter = 0.2,alpha=0.5),
          legend="",xlab="",ylab="Number of MSRs")+
  stat_compare_means(size=5,label.y = 10)+
  scale_y_continuous(breaks = get_breaks(by=5,from = 0),limits = c(-1,11))
p2<-ggpar(p2,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p2

dtf %>% levene_test(Nb_reg~Essentiality)
dtf %>% levene_test(Nb_MSR~Essentiality)

Sys.time()
```
## 5.6. Plasticity vs. Number of Regulators (TRs, SRs, MSRs and TRcoms)
```{r TR,warning=FALSE, message=FALSE,fig.height=3,fig.width=3,dpi=300}
#TRs
p1<-ggboxplot(dtf[dtf$Essentiality=="nonessential",],x="TR_flag",y="SD_logAvFITC",
          color=mycolpal[1],
          # palette = mycolpal[1],
          add="jitter",add.params = list(size = 0.5, jitter = 0.2,alpha=0.5),
          legend="")+
  stat_compare_means(size=5,label.y = 0.45)+
  scale_y_continuous(breaks = get_breaks(by=0.1,from = 0.1,to=0.4),limits = c(0.1,0.5))+
    xlab(expression("Regulation by TRs"))+
    ylab(expression("SD of"~E[pop]))
p1<-ggpar(p1,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p1

#TRcoms
p2<-ggboxplot(dtf[dtf$Essentiality=="nonessential",],x="TRcom_flag",y="SD_logAvFITC",
          color=mycolpal[1],
          # palette = mycolpal[1],
          add="jitter",add.params = list(size = 0.5, jitter = 0.2,alpha=0.5),
          legend="")+
  stat_compare_means(size=5,label.y = 0.45)+
  scale_y_continuous(breaks = get_breaks(by=0.1,from = 0.1,to=0.4),limits = c(0.1,0.5))+
    xlab(expression("Regulation by"~TR[com]))+
    ylab(expression("SD of"~E[pop]))
p2<-ggpar(p2,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p2

#SR
p3<-ggboxplot(dtf[dtf$Essentiality=="nonessential",],x="SR_flag",y="SD_logAvFITC",
          color=mycolpal[1],
          # palette = mycolpal[1],
          add="jitter",add.params = list(size = 0.5, jitter = 0.2,alpha=0.5),
          legend="")+
  stat_compare_means(size=5,label.y = 0.45)+
  scale_y_continuous(breaks = get_breaks(by=0.1,from = 0.1,to=0.4),limits = c(0.1,0.5))+
    xlab(expression("Regulation by"~SRs))+
    ylab(expression("SD of"~E[pop]))
p3<-ggpar(p3,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p3

#MSR
p4<-ggboxplot(dtf[dtf$Essentiality=="nonessential",],x="MSR_flag",y="SD_logAvFITC",
          color=mycolpal[1],
          # palette = mycolpal[1],
          add="jitter",add.params = list(size = 0.5, jitter = 0.2,alpha=0.5),
          legend="")+
  stat_compare_means(size=5,label.y = 0.45)+
  scale_y_continuous(breaks = get_breaks(by=0.1,from = 0.1,to=0.4),limits = c(0.1,0.5))+
    xlab(expression("Regulation by"~MSRs))+
    ylab(expression("SD of"~E[pop]))
p4<-ggpar(p4,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p4


p4.1<-ggerrorplot(dtf[dtf$Essentiality=="nonessential",],x="MSR_flag",y="SD_logAvFITC",
                desc_stat="mean_sd",
          color=mycolpal[1],alpha=0.3,
          # palette = mycolpal[1],
          add="jitter",add.params = list(size = 0.5, jitter = 0.2,alpha=0.5),
          legend="")+
  stat_compare_means(size=5,label.y = 0.45)+
  scale_y_continuous(breaks = get_breaks(by=0.1,from = 0.1,to=0.4),limits = c(0.1,0.5))+
    xlab(expression("Regulation by"~MSRs))+
    ylab(expression("SD of"~E[pop]))
p4.1<-ggpar(p4.1,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p4.1


Sys.time()
```
## 5.7. Noise vs. Number of Regulators (TRs, SRs and TRcoms)
```{r TR,warning=FALSE, message=FALSE,fig.height=3,fig.width=3,dpi=300}
#TRs
p1<-ggboxplot(dtf[dtf$Essentiality=="nonessential",],x="TR_flag",y="Mean_DMv",
          color=mycolpal[1],
          # palette = mycolpal[1],
          add="jitter",add.params = list(size = 0.5, jitter = 0.2,alpha=0.5),
          legend="")+
  stat_compare_means(size=5,label.y = 0.1)+
  scale_y_continuous(breaks = get_breaks(by=0.04,from = 0,to=0.08),limits = c(-0.02,0.12))+
    xlab(expression("Regulation by TRs"))+
    ylab(expression(Mean~DM[V]))
p1<-ggpar(p1,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p1

#TRcoms
p2<-ggboxplot(dtf[dtf$Essentiality=="nonessential",],x="TRcom_flag",y="Mean_DMv",
          color=mycolpal[1],
          # palette = mycolpal[1],
          add="jitter",add.params = list(size = 0.5, jitter = 0.2,alpha=0.5),
          legend="")+
  stat_compare_means(size=5,label.y = 0.1)+
  scale_y_continuous(breaks = get_breaks(by=0.04,from = 0,to=0.08),limits = c(-0.02,0.12))+
    xlab(expression("Regulation by"~TR[com]))+
    ylab(expression(Mean~DM[V]))
p2<-ggpar(p2,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p2

#SR
p3<-ggboxplot(dtf[dtf$Essentiality=="nonessential",],x="SR_flag",y="Mean_DMv",
          color=mycolpal[1],
          # palette = mycolpal[1],
          add="jitter",add.params = list(size = 0.5, jitter = 0.2,alpha=0.5),
          legend="")+
  stat_compare_means(size=5,label.y = 0.1)+
  scale_y_continuous(breaks = get_breaks(by=0.04,from = 0,to=0.08),limits = c(-0.02,0.12))+
    xlab(expression("Regulation by"~SRs))+
    ylab(expression(Mean~DM[V]))
p3<-ggpar(p3,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p3

#MSR
p4<-ggboxplot(dtf[dtf$Essentiality=="nonessential",],x="MSR_flag",y="Mean_DMv",
          color=mycolpal[1],
          # palette = mycolpal[1],
          add="jitter",add.params = list(size = 0.5, jitter = 0.2,alpha=0.5),
          legend="")+
  stat_compare_means(size=5,label.y = 0.1)+
  scale_y_continuous(breaks = get_breaks(by=0.04,from = 0,to=0.08),limits = c(-0.02,0.12))+
    xlab(expression("Regulation by"~MSRs))+
    ylab(expression(Mean~DM[V]))
p4<-ggpar(p4,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p4

p4.1<-ggerrorplot(dtf[dtf$Essentiality=="nonessential",],x="MSR_flag",y="Mean_DMv",
                desc_stat="mean_sd",
          color=mycolpal[1],alpha=0.3,
          # palette = mycolpal[1],
          add="jitter",add.params = list(size = 0.5, jitter = 0.2,alpha=0.5),
          legend="")+
  stat_compare_means(size=5,label.y = 0.1)+
  scale_y_continuous(breaks = get_breaks(by=0.04,from = 0,to=0.08),limits = c(-0.02,0.12))+
    xlab(expression("Regulation by"~MSRs))+
    ylab(expression(Mean~DM[V]))
p4.1<-ggpar(p4.1,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p4.1
Sys.time()
```
## 5.8. Correlation between Noise/Plasticity and Nb of Metabolic sensory regulators (MSRs)
### 5.8.1. 89 genes
```{r TR,warning=FALSE, message=FALSE,fig.height=3,fig.width=3,dpi=300}
my_tmp<-data_frame(Nb_MSR=seq(0,max(dtf[dtf$Essentiality=="nonessential",]$Nb_MSR)),Nb_genes=0)
for(i in 1:nrow(my_tmp)){
  my_tmp$Nb_genes[i]<-dtf[(dtf$Essentiality=="nonessential")&(dtf$Nb_MSR==my_tmp$Nb_MSR[i]),] %>% nrow()
}
my_range<-my_tmp[my_tmp$Nb_genes>0,]$Nb_MSR
my_df<-dtf[(dtf$Essentiality=="nonessential")&(dtf$Nb_MSR %in% my_range),]

# Partial Correlation test using Spearman's R
pcor.test(x = my_df$Nb_MSR,y = my_df$SD_logAvFITC,z = my_df$Nb_reg,method = "spearman")

# Wilcoxon
my_df %>% wilcox_test(Mean_DMv ~ MSR_flag)


# Plasticity
p1<-ggerrorplot(my_df,x="Nb_MSR",y="SD_logAvFITC",
          desc_stat = "mean_sd",
          add = "jitter",add.params = list(size = 0.5, jitter = 0.2,alpha=0.5),
          color=mycolpal[1],alpha=0.3,
          legend="")+
          stat_cor(data =my_df,aes(x=Nb_MSR,y=SD_logAvFITC), label.x = 1, size=5,method = "spearman", label.sep = "\n")+
  scale_y_continuous(breaks = get_breaks(by=0.1,from=0.1,to=0.4),limits = c(0.07,0.5))+
          xlab(expression("Number of MSRs"))+
          ylab(expression("SD of"~E[pop]))
p1<-ggpar(p1,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p1
#TODO ggsave(file="Fig2g_nes.svg", path=my_figout,dpi = 300, width = 3.5, height = 3)

# Noise
p2<-ggerrorplot(my_df,x="Nb_MSR",y="Mean_DMv",
          desc_stat = "mean_sd",
          add = "jitter",add.params = list(size = 0.5, jitter = 0.2,alpha=0.5),
          color=mycolpal[1],alpha=0.3,
          legend="")+
          scale_y_continuous(breaks = get_breaks(by=0.04,from = 0,to=0.08),limits = c(-0.02,0.1))+
          stat_cor(data =my_df,aes(x=Nb_MSR,y=Mean_DMv), label.x = 3.5,label.y = 0.08, size=5,method = "spearman", label.sep = "\n")+
          xlab(expression("Number of MSRs"))+
          ylab(expression("Mean"~DM[V]))
p2<-ggpar(p2,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p2
#TODO ggsave(file="Fig3c_nes.svg", path=my_figout,dpi = 300, width = 3, height = 3)

my_df2<-dtf[(dtf$Essentiality=="essential")&(dtf$Nb_MSR %in% my_range),]
# Plasticity
p3<-ggerrorplot(my_df2,x="Nb_MSR",y="SD_logAvFITC",
          desc_stat = "mean_sd",
          add = "jitter",add.params = list(size = 0.5, jitter = 0.2,alpha=0.5),
          color=mycolpal[2],alpha=0.3,
          legend="")+
          stat_cor(data =my_df2,aes(x=Nb_MSR,y=SD_logAvFITC), label.x = 1, size=5,method = "spearman", label.sep = "\n")+
  scale_y_continuous(breaks = get_breaks(by=0.1,from=0.1,to=0.4),limits = c(0.07,0.5))+
          xlab(expression("Number of MSRs"))+
          ylab(expression("SD of"~E[pop]))
p3<-ggpar(p3,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p3
#TODO ggsave(file="Fig2g_ess.svg", path=my_figout,dpi = 300, width = 3.5, height = 3)

# Noise
p4<-ggerrorplot(my_df2,x="Nb_MSR",y="Mean_DMv",
          desc_stat = "mean_sd",
          add = "jitter",add.params = list(size = 0.5, jitter = 0.2,alpha=0.5),
          color=mycolpal[2],alpha=0.3,
          legend="")+
          scale_y_continuous(breaks = get_breaks(by=0.04,from = 0,to=0.08),limits = c(-0.02,0.1))+
          stat_cor(data =my_df2,aes(x=Nb_MSR,y=Mean_DMv), label.x = 1.5,label.y = 0.08, size=5,method = "spearman", label.sep = "\n")+
          xlab(expression("Number of MSRs"))+
          ylab(expression("Mean"~DM[V]))
p4<-ggpar(p4,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p4
#TODO ggsave(file="Fig3c_ess.svg", path=my_figout,dpi = 300, width = 3, height = 3)

Sys.time()
```
### 5.8.2. Genes without conditional essential genes
```{r TR,warning=FALSE, message=FALSE,fig.height=3,fig.width=3,dpi=300}
my_tmp<-data_frame(Nb_MSR=seq(0,max(dtf[dtf$Essentiality=="nonessential",]$Nb_MSR)),Nb_genes=0)
for(i in 1:nrow(my_tmp)){
  my_tmp$Nb_genes[i]<-dtf[(dtf$Essentiality=="nonessential")&(dtf$Nb_MSR==my_tmp$Nb_MSR[i]),] %>% nrow()
}
my_range<-my_tmp[my_tmp$Nb_genes>0,]$Nb_MSR
my_df<-dtf[(dtf$Essentiality=="nonessential")&(dtf$Nb_MSR %in% my_range),]
my_df<-my_df[my_df$StringentSet,]

# Partial Correlation test using Spearman's R
pcor.test(x = my_df$Nb_MSR,y = my_df$SD_logAvFITC,z = my_df$Nb_reg,method = "spearman")

# Wilcoxon
my_df %>% wilcox_test(Mean_DMv ~ MSR_flag)


# Plasticity
p1<-ggerrorplot(my_df,x="Nb_MSR",y="SD_logAvFITC",
          desc_stat = "mean_sd",
          add = "jitter",add.params = list(size = 0.5, jitter = 0.2,alpha=0.5),
          color=mycolpal[1],alpha=0.3,
          legend="")+
          stat_cor(data =my_df,aes(x=Nb_MSR,y=SD_logAvFITC), label.x = 1, size=5,method = "spearman", label.sep = "\n")+
  scale_y_continuous(breaks = get_breaks(by=0.1,from=0.1,to=0.4),limits = c(0.07,0.5))+
          xlab(expression("Number of MSRs"))+
          ylab(expression("SD of"~E[pop]))
p1<-ggpar(p1,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p1

# Noise
p2<-ggerrorplot(my_df,x="Nb_MSR",y="Mean_DMv",
          desc_stat = "mean_sd",
          add = "jitter",add.params = list(size = 0.5, jitter = 0.2,alpha=0.5),
          color=mycolpal[1],alpha=0.3,
          legend="")+
          scale_y_continuous(breaks = get_breaks(by=0.04,from = 0,to=0.08),limits = c(-0.02,0.1))+
          stat_cor(data =my_df,aes(x=Nb_MSR,y=Mean_DMv), label.x = 3.5,label.y = 0.08, size=5,method = "spearman", label.sep = "\n")+
          xlab(expression("Number of MSRs"))+
          ylab(expression("Mean"~DM[V]))
p2<-ggpar(p2,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p2


my_df2<-dtf[(dtf$Essentiality=="essential")&(dtf$Nb_MSR %in% my_range),]
# Plasticity
p3<-ggerrorplot(my_df2,x="Nb_MSR",y="SD_logAvFITC",
          desc_stat = "mean_sd",
          add = "jitter",add.params = list(size = 0.5, jitter = 0.2,alpha=0.5),
          color=mycolpal[2],alpha=0.3,
          legend="")+
          stat_cor(data =my_df2,aes(x=Nb_MSR,y=SD_logAvFITC), label.x = 1, size=5,method = "spearman", label.sep = "\n")+
  scale_y_continuous(breaks = get_breaks(by=0.1,from=0.1,to=0.4),limits = c(0.07,0.5))+
          xlab(expression("Number of MSRs"))+
          ylab(expression("SD of"~E[pop]))
p3<-ggpar(p3,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p3

# Noise
p4<-ggerrorplot(my_df2,x="Nb_MSR",y="Mean_DMv",
          desc_stat = "mean_sd",
          add = "jitter",add.params = list(size = 0.5, jitter = 0.2,alpha=0.5),
          color=mycolpal[2],alpha=0.3,
          legend="")+
          scale_y_continuous(breaks = get_breaks(by=0.04,from = 0,to=0.08),limits = c(-0.02,0.1))+
          stat_cor(data =my_df2,aes(x=Nb_MSR,y=Mean_DMv), label.x = 1.5,label.y = 0.08, size=5,method = "spearman", label.sep = "\n")+
          xlab(expression("Number of MSRs"))+
          ylab(expression("Mean"~DM[V]))
p4<-ggpar(p4,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p4


Sys.time()
```
## 5.9. Cumulative analysis by sliding Noise
Following a previous study (Fig. 2)
https://www.ncbi.nlm.nih.gov/pmc/articles/PMC4468965/
### 5.9.1. Nonessential genes
```{r TR,warning=FALSE, message=FALSE,fig.height=3,fig.width=4,dpi=300}
my_tmp<-data_frame(Nb_MSR=seq(0,max(dtf[dtf$Essentiality=="nonessential",]$Nb_MSR)),Nb_genes=0)
for(i in 1:nrow(my_tmp)){
  my_tmp$Nb_genes[i]<-dtf[(dtf$Essentiality=="nonessential")&(dtf$Nb_MSR==my_tmp$Nb_MSR[i]),] %>% nrow()
}
my_range<-my_tmp[my_tmp$Nb_genes>0,]$Nb_MSR
my_df<-dtf[(dtf$Essentiality=="nonessential")&(dtf$Nb_MSR %in% my_range),]

my_df<-my_df[order(my_df$Mean_DMv,decreasing = T),]
my_df$Cum_Nb_MSR<-0
my_df$Cum_Nb_MSR_SE<-0
my_df$Cum_Nb_TR<-0
my_df$Cum_Nb_TR_SE<-0
my_df$Cum_Plasticity<-0
my_df$Cum_Plasticity_SE<-0
for(i in 6:nrow(my_df)){
  ## MSR
  my_df$Cum_Nb_MSR[i]<-my_df[my_df$Mean_DMv>my_df$Mean_DMv[i],]$Nb_MSR %>% mean()
  my_df$Cum_Nb_MSR_SE[i]<-my_df[my_df$Mean_DMv>my_df$Mean_DMv[i],]$Nb_MSR %>% sd()
  my_df$Cum_Nb_MSR_SE[i]<-my_df$Cum_Nb_MSR_SE[i]/sqrt(nrow(my_df[my_df$Mean_DMv>my_df$Mean_DMv[i],]))
  ## TR
  my_df$Cum_Nb_TR[i]<-my_df[my_df$Mean_DMv>my_df$Mean_DMv[i],]$Nb_reg %>% mean()
  my_df$Cum_Nb_TR_SE[i]<-my_df[my_df$Mean_DMv>my_df$Mean_DMv[i],]$Nb_reg %>% sd()
  my_df$Cum_Nb_TR_SE[i]<-my_df$Cum_Nb_TR_SE[i]/sqrt(nrow(my_df[my_df$Mean_DMv>my_df$Mean_DMv[i],]))
  ## Plasticity
  my_df$Cum_Plasticity[i]<-my_df[my_df$Mean_DMv>my_df$Mean_DMv[i],]$SD_logAvFITC %>% mean()
  my_df$Cum_Plasticity_SE[i]<-my_df[my_df$Mean_DMv>my_df$Mean_DMv[i],]$SD_logAvFITC %>% sd()
  my_df$Cum_Plasticity_SE[i]<-my_df$Cum_Plasticity_SE[i]/sqrt(nrow(my_df[my_df$Mean_DMv>my_df$Mean_DMv[i],]))
}

p1<-ggplot(my_df[my_df$Cum_Nb_MSR_SE>0,],aes(x=Mean_DMv,y=Cum_Nb_MSR))+
  geom_line(color=mycolpal[1],alpha=0.5)+
  geom_pointrange(aes(ymin=Cum_Nb_MSR-Cum_Nb_MSR_SE, ymax=Cum_Nb_MSR+Cum_Nb_MSR_SE),color=mycolpal[1],alpha=0.5)+
  scale_y_continuous(breaks = get_breaks(by=1,from=1),limits = c(1,4))+
  theme_pubr()+
  ylab(expression("Number of"~MSRs))+
  xlab(expression(Mean~DM[V]))
p1<-ggpar(p1,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p1
#TODO ggsave(file="Fig3d_nes.svg", path=my_figout,dpi = 300, width = 4, height = 3)

p2<-ggplot(my_df[my_df$Cum_Plasticity_SE>0,],aes(x=Mean_DMv,y=Cum_Plasticity))+
  geom_line(color=mycolpal[1],alpha=0.5)+
  geom_pointrange(aes(ymin=Cum_Plasticity-Cum_Plasticity_SE, ymax=Cum_Plasticity+Cum_Plasticity_SE),color=mycolpal[1],alpha=0.5)+
  scale_y_continuous(breaks = get_breaks(by=0.05,from = 0.1),limits = c(0.15,0.3))+
  theme_pubr()+
  ylab(expression("SD of"~E[pop]))+
  xlab(expression(Mean~DM[V]))
p2<-ggpar(p2,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p2

p3<-ggplot(my_df[my_df$Cum_Nb_TR_SE>0,],aes(x=Mean_DMv,y=Cum_Nb_TR))+
  geom_line(color=mycolpal[1],alpha=0.5)+
  geom_pointrange(aes(ymin=Cum_Nb_TR-Cum_Nb_TR_SE, ymax=Cum_Nb_TR+Cum_Nb_TR_SE),color=mycolpal[1],alpha=0.5)+
  scale_y_continuous(breaks = get_breaks(by=2,from=2),limits = c(2,8))+
  theme_pubr()+
  ylab(expression("Number of"~TRs))+
  xlab(expression(Mean~DM[V]))
p3<-ggpar(p3,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p3
    

Sys.time()
```
### 5.9.2. Pooled genes
```{r TR,warning=FALSE, message=FALSE,fig.height=3,fig.width=4,dpi=300}
my_tmp<-data_frame(Nb_MSR=seq(0,max(dtf$Nb_MSR)),Nb_genes=0)
for(i in 1:nrow(my_tmp)){
  my_tmp$Nb_genes[i]<-dtf[(dtf$Nb_MSR==my_tmp$Nb_MSR[i]),] %>% nrow()
}
my_range<-my_tmp[my_tmp$Nb_genes>0,]$Nb_MSR
my_df<-dtf[(dtf$Nb_MSR %in% my_range),]

my_df<-my_df[order(my_df$Mean_DMv,decreasing = T),]
my_df$Cum_Nb_MSR<-0
my_df$Cum_Nb_MSR_SE<-0
my_df$Cum_Nb_TR<-0
my_df$Cum_Nb_TR_SE<-0
my_df$Cum_Plasticity<-0
my_df$Cum_Plasticity_SE<-0
for(i in 6:nrow(my_df)){
  ## MSR
  my_df$Cum_Nb_MSR[i]<-my_df[my_df$Mean_DMv>my_df$Mean_DMv[i],]$Nb_MSR %>% mean()
  my_df$Cum_Nb_MSR_SE[i]<-my_df[my_df$Mean_DMv>my_df$Mean_DMv[i],]$Nb_MSR %>% sd()
  my_df$Cum_Nb_MSR_SE[i]<-my_df$Cum_Nb_MSR_SE[i]/sqrt(nrow(my_df[my_df$Mean_DMv>my_df$Mean_DMv[i],]))
  ## TR
  my_df$Cum_Nb_TR[i]<-my_df[my_df$Mean_DMv>my_df$Mean_DMv[i],]$Nb_reg %>% mean()
  my_df$Cum_Nb_TR_SE[i]<-my_df[my_df$Mean_DMv>my_df$Mean_DMv[i],]$Nb_reg %>% sd()
  my_df$Cum_Nb_TR_SE[i]<-my_df$Cum_Nb_TR_SE[i]/sqrt(nrow(my_df[my_df$Mean_DMv>my_df$Mean_DMv[i],]))
  ## Plasticity
  my_df$Cum_Plasticity[i]<-my_df[my_df$Mean_DMv>my_df$Mean_DMv[i],]$SD_logAvFITC %>% mean()
  my_df$Cum_Plasticity_SE[i]<-my_df[my_df$Mean_DMv>my_df$Mean_DMv[i],]$SD_logAvFITC %>% sd()
  my_df$Cum_Plasticity_SE[i]<-my_df$Cum_Plasticity_SE[i]/sqrt(nrow(my_df[my_df$Mean_DMv>my_df$Mean_DMv[i],]))
}

p1<-ggplot(my_df[my_df$Cum_Nb_MSR_SE>0,],aes(x=Mean_DMv,y=Cum_Nb_MSR))+
  geom_line(color="gray10",alpha=0.5)+
  geom_pointrange(aes(ymin=Cum_Nb_MSR-Cum_Nb_MSR_SE, ymax=Cum_Nb_MSR+Cum_Nb_MSR_SE),color="gray10",alpha=0.5)+
  scale_y_continuous(breaks = get_breaks(by=1,from=1),limits = c(1,4))+
  theme_pubr()+
  ylab(expression("Number of"~MSRs))+
  xlab(expression(Mean~DM[V]))
p1<-ggpar(p1,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p1

p1i<-ggplot(my_df[my_df$Cum_Nb_MSR_SE>0,],aes(x=Mean_DMv,y=Cum_Nb_MSR))+
  geom_line(color="gray10",alpha=0.8,size=1)+
  geom_pointrange(aes(ymin=Cum_Nb_MSR-Cum_Nb_MSR_SE, ymax=Cum_Nb_MSR+Cum_Nb_MSR_SE),color="gray10",alpha=0.8,size=1)+
  scale_x_continuous(breaks = get_breaks(by=0.04,from=0),limits = c(-0.02,0.05))+
  scale_y_continuous(breaks = get_breaks(by=2,from=2),limits = c(1,4.5))+
  theme_pubr()+
  theme(axis.title = element_blank(),
        axis.ticks = element_line(linewidth = 1),
        axis.ticks.length = unit(0.5,"cm"),
        axis.line = element_line(linewidth = 1,),
        )
p1i<-ggpar(p1i,font.xtickslab = my_fontsize*3,font.ytickslab = my_fontsize*3)
p1i
#TODO ggsave(file="Fig3d_pool.svg", path=my_figout,dpi = 300, width = 4, height = 3)

p2<-ggplot(my_df[my_df$Cum_Plasticity_SE>0,],aes(x=Mean_DMv,y=Cum_Plasticity))+
  geom_line(color="gray10",alpha=0.5)+
  geom_pointrange(aes(ymin=Cum_Plasticity-Cum_Plasticity_SE, ymax=Cum_Plasticity+Cum_Plasticity_SE),color="gray10",alpha=0.5)+
  scale_y_continuous(breaks = get_breaks(by=0.05,from = 0.1),limits = c(0.15,0.3))+
  theme_pubr()+
  ylab(expression("SD of"~E[pop]))+
  xlab(expression(Mean~DM[V]))
p2<-ggpar(p2,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p2

p3<-ggplot(my_df[my_df$Cum_Nb_TR_SE>0,],aes(x=Mean_DMv,y=Cum_Nb_TR))+
  geom_line(color="gray10",alpha=0.5)+
  geom_pointrange(aes(ymin=Cum_Nb_TR-Cum_Nb_TR_SE, ymax=Cum_Nb_TR+Cum_Nb_TR_SE),color="gray10",alpha=0.5)+
  scale_y_continuous(breaks = get_breaks(by=2,from=2),limits = c(2,8))+
  theme_pubr()+
  ylab(expression("Number of"~TRs))+
  xlab(expression(Mean~DM[V]))
p3<-ggpar(p3,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p3
    

Sys.time()
```
## 5.10. Cumulative analysis by sliding Plasticity
### 5.10.1. Nonessential genes 
```{r TR,warning=FALSE, message=FALSE,fig.height=3,fig.width=4,dpi=300}
my_tmp<-data_frame(Nb_MSR=seq(0,max(dtf[dtf$Essentiality=="nonessential",]$Nb_MSR)),Nb_genes=0)
for(i in 1:nrow(my_tmp)){
  my_tmp$Nb_genes[i]<-dtf[(dtf$Essentiality=="nonessential")&(dtf$Nb_MSR==my_tmp$Nb_MSR[i]),] %>% nrow()
}
my_range<-my_tmp[my_tmp$Nb_genes>0,]$Nb_MSR
my_df<-dtf[(dtf$Essentiality=="nonessential")&(dtf$Nb_MSR %in% my_range),]

my_df<-my_df[order(my_df$SD_logAvFITC,decreasing = T),]
my_df$Cum_Nb_MSR<-0
my_df$Cum_Nb_MSR_SE<-0
my_df$Cum_Nb_TR<-0
my_df$Cum_Nb_TR_SE<-0
my_df$Cum_Noise<-0
my_df$Cum_Noise_SE<-0
for(i in 6:nrow(my_df)){
  ## MSR
  my_df$Cum_Nb_MSR[i]<-my_df[my_df$SD_logAvFITC>my_df$SD_logAvFITC[i],]$Nb_MSR %>% mean()
  my_df$Cum_Nb_MSR_SE[i]<-my_df[my_df$SD_logAvFITC>my_df$SD_logAvFITC[i],]$Nb_MSR %>% sd()
  my_df$Cum_Nb_MSR_SE[i]<-my_df$Cum_Nb_MSR_SE[i]/sqrt(nrow(my_df[my_df$SD_logAvFITC>my_df$SD_logAvFITC[i],]))
  ## TR
  my_df$Cum_Nb_TR[i]<-my_df[my_df$SD_logAvFITC>my_df$SD_logAvFITC[i],]$Nb_reg %>% mean()
  my_df$Cum_Nb_TR_SE[i]<-my_df[my_df$SD_logAvFITC>my_df$SD_logAvFITC[i],]$Nb_reg %>% sd()
  my_df$Cum_Nb_TR_SE[i]<-my_df$Cum_Nb_TR_SE[i]/sqrt(nrow(my_df[my_df$SD_logAvFITC>my_df$SD_logAvFITC[i],]))
  ## Noise
  my_df$Cum_Noise[i]<-my_df[my_df$SD_logAvFITC>my_df$SD_logAvFITC[i],]$Mean_DMv %>% mean()
  my_df$Cum_Noise_SE[i]<-my_df[my_df$SD_logAvFITC>my_df$SD_logAvFITC[i],]$Mean_DMv %>% sd()
  my_df$Cum_Noise_SE[i]<-my_df$Cum_Noise_SE[i]/sqrt(nrow(my_df[my_df$SD_logAvFITC>my_df$SD_logAvFITC[i],]))
}

p1<-ggplot(my_df[my_df$Cum_Nb_MSR_SE>0,],aes(x=SD_logAvFITC,y=Cum_Nb_MSR))+
  geom_line(color=mycolpal[1],alpha=0.5)+
  geom_pointrange(aes(ymin=Cum_Nb_MSR-Cum_Nb_MSR_SE, ymax=Cum_Nb_MSR+Cum_Nb_MSR_SE),color=mycolpal[1],alpha=0.5)+
  scale_x_continuous(breaks=get_breaks(by=0.05,from=0.05),limits=c(0.05,0.25))+
  scale_y_continuous(breaks = get_breaks(by=1,from=1),limits = c(1,4))+
  theme_pubr()+
  ylab(expression("Number of"~MSRs))+
  xlab(expression("SD of"~E[pop]))
p1<-ggpar(p1,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p1

p2<-ggplot(my_df[my_df$Cum_Noise_SE>0,],aes(x=SD_logAvFITC,y=Cum_Noise))+
  geom_line(color=mycolpal[1],alpha=0.5)+
  geom_pointrange(aes(ymin=Cum_Noise-Cum_Noise_SE, ymax=Cum_Noise+Cum_Noise_SE),color=mycolpal[1],alpha=0.5)+
  scale_x_continuous(breaks=get_breaks(by=0.05,from=0.05),limits=c(0.05,0.25))+
  scale_y_continuous(breaks = get_breaks(by=0.02,from = 0),limits = c(0,0.04))+
  theme_pubr()+
  ylab(expression(Mean~DM[V]))+
  xlab(expression("SD of"~E[pop]))
p2<-ggpar(p2,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p2

p3<-ggplot(my_df[my_df$Cum_Nb_TR_SE>0,],aes(x=SD_logAvFITC,y=Cum_Nb_TR))+
  geom_line(color=mycolpal[1],alpha=0.5)+
  geom_pointrange(aes(ymin=Cum_Nb_TR-Cum_Nb_TR_SE, ymax=Cum_Nb_TR+Cum_Nb_TR_SE),color=mycolpal[1],alpha=0.5)+
  scale_x_continuous(breaks=get_breaks(by=0.05,from=0.05),limits=c(0.05,0.25))+
  scale_y_continuous(breaks = get_breaks(by=2,from=2),limits = c(2,8))+
  theme_pubr()+
  ylab(expression("Number of"~TRs))+
  xlab(expression("SD of"~E[pop]))
p3<-ggpar(p3,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p3
    

Sys.time()
```
### 5.10.2. Essential genes 
```{r TR,warning=FALSE, message=FALSE,fig.height=3,fig.width=4,dpi=300}
my_tmp<-data_frame(Nb_MSR=seq(0,max(dtf[dtf$Essentiality=="essential",]$Nb_MSR)),Nb_genes=0)
for(i in 1:nrow(my_tmp)){
  my_tmp$Nb_genes[i]<-dtf[(dtf$Essentiality=="essential")&(dtf$Nb_MSR==my_tmp$Nb_MSR[i]),] %>% nrow()
}
my_range<-my_tmp[my_tmp$Nb_genes>0,]$Nb_MSR
my_df<-dtf[(dtf$Essentiality=="essential")&(dtf$Nb_MSR %in% my_range),]

my_df<-my_df[order(my_df$SD_logAvFITC,decreasing = T),]
my_df$Cum_Nb_MSR<-0
my_df$Cum_Nb_MSR_SE<-0
my_df$Cum_Nb_TR<-0
my_df$Cum_Nb_TR_SE<-0
my_df$Cum_Noise<-0
my_df$Cum_Noise_SE<-0
for(i in 6:nrow(my_df)){
  ## MSR
  my_df$Cum_Nb_MSR[i]<-my_df[my_df$SD_logAvFITC>my_df$SD_logAvFITC[i],]$Nb_MSR %>% mean()
  my_df$Cum_Nb_MSR_SE[i]<-my_df[my_df$SD_logAvFITC>my_df$SD_logAvFITC[i],]$Nb_MSR %>% sd()
  my_df$Cum_Nb_MSR_SE[i]<-my_df$Cum_Nb_MSR_SE[i]/sqrt(nrow(my_df[my_df$SD_logAvFITC>my_df$SD_logAvFITC[i],]))
  ## TR
  my_df$Cum_Nb_TR[i]<-my_df[my_df$SD_logAvFITC>my_df$SD_logAvFITC[i],]$Nb_reg %>% mean()
  my_df$Cum_Nb_TR_SE[i]<-my_df[my_df$SD_logAvFITC>my_df$SD_logAvFITC[i],]$Nb_reg %>% sd()
  my_df$Cum_Nb_TR_SE[i]<-my_df$Cum_Nb_TR_SE[i]/sqrt(nrow(my_df[my_df$SD_logAvFITC>my_df$SD_logAvFITC[i],]))
  ## Noise
  my_df$Cum_Noise[i]<-my_df[my_df$SD_logAvFITC>my_df$SD_logAvFITC[i],]$Mean_DMv %>% mean()
  my_df$Cum_Noise_SE[i]<-my_df[my_df$SD_logAvFITC>my_df$SD_logAvFITC[i],]$Mean_DMv %>% sd()
  my_df$Cum_Noise_SE[i]<-my_df$Cum_Noise_SE[i]/sqrt(nrow(my_df[my_df$SD_logAvFITC>my_df$SD_logAvFITC[i],]))
}

p1<-ggplot(my_df[my_df$Cum_Nb_MSR_SE>0,],aes(x=SD_logAvFITC,y=Cum_Nb_MSR))+
  geom_line(color=mycolpal[2],alpha=0.5)+
  geom_pointrange(aes(ymin=Cum_Nb_MSR-Cum_Nb_MSR_SE, ymax=Cum_Nb_MSR+Cum_Nb_MSR_SE),color=mycolpal[2],alpha=0.5)+
  scale_x_continuous(breaks=get_breaks(by=0.05,from=0.05),limits=c(0.05,0.25))+
  scale_y_continuous(breaks = get_breaks(by=0.4,from=0),limits = c(-0.01,1.5))+
  theme_pubr()+
  ylab(expression("Number of"~MSRs))+
  xlab(expression("SD of"~E[pop]))
p1<-ggpar(p1,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p1

p2<-ggplot(my_df[my_df$Cum_Noise_SE>0,],aes(x=SD_logAvFITC,y=Cum_Noise))+
  geom_line(color=mycolpal[2],alpha=0.5)+
  geom_pointrange(aes(ymin=Cum_Noise-Cum_Noise_SE, ymax=Cum_Noise+Cum_Noise_SE),color=mycolpal[2],alpha=0.5)+
  scale_x_continuous(breaks=get_breaks(by=0.05,from=0.05),limits=c(0.05,0.25))+
  scale_y_continuous(breaks = get_breaks(by=0.01,from = -0.01),limits = c(-0.01,0.02))+
  theme_pubr()+
  ylab(expression(Mean~DM[V]))+
  xlab(expression("SD of"~E[pop]))
p2<-ggpar(p2,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p2

p3<-ggplot(my_df[my_df$Cum_Nb_TR_SE>0,],aes(x=SD_logAvFITC,y=Cum_Nb_TR))+
  geom_line(color=mycolpal[2],alpha=0.5)+
  geom_pointrange(aes(ymin=Cum_Nb_TR-Cum_Nb_TR_SE, ymax=Cum_Nb_TR+Cum_Nb_TR_SE),color=mycolpal[2],alpha=0.5)+
  scale_x_continuous(breaks=get_breaks(by=0.05,from=0.05),limits=c(0.05,0.25))+
  scale_y_continuous(breaks = get_breaks(by=1,from=0),limits = c(0,3))+
  theme_pubr()+
  ylab(expression("Number of"~TRs))+
  xlab(expression("SD of"~E[pop]))
p3<-ggpar(p3,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p3
    

Sys.time()
```
### 5.10.3. Pooled genes 
```{r TR,warning=FALSE, message=FALSE,fig.height=3,fig.width=4,dpi=300}
my_tmp<-data_frame(Nb_MSR=seq(0,max(dtf$Nb_MSR)),Nb_genes=0)
for(i in 1:nrow(my_tmp)){
  my_tmp$Nb_genes[i]<-dtf[(dtf$Nb_MSR==my_tmp$Nb_MSR[i]),] %>% nrow()
}
my_range<-my_tmp[my_tmp$Nb_genes>0,]$Nb_MSR
my_df<-dtf[(dtf$Nb_MSR %in% my_range),]

my_df<-my_df[order(my_df$SD_logAvFITC,decreasing = T),]
my_df$Cum_Nb_MSR<-0
my_df$Cum_Nb_MSR_SE<-0
my_df$Cum_Nb_TR<-0
my_df$Cum_Nb_TR_SE<-0
my_df$Cum_Noise<-0
my_df$Cum_Noise_SE<-0
for(i in 6:nrow(my_df)){
  ## MSR
  my_df$Cum_Nb_MSR[i]<-my_df[my_df$SD_logAvFITC>my_df$SD_logAvFITC[i],]$Nb_MSR %>% mean()
  my_df$Cum_Nb_MSR_SE[i]<-my_df[my_df$SD_logAvFITC>my_df$SD_logAvFITC[i],]$Nb_MSR %>% sd()
  my_df$Cum_Nb_MSR_SE[i]<-my_df$Cum_Nb_MSR_SE[i]/sqrt(nrow(my_df[my_df$SD_logAvFITC>my_df$SD_logAvFITC[i],]))
  ## TR
  my_df$Cum_Nb_TR[i]<-my_df[my_df$SD_logAvFITC>my_df$SD_logAvFITC[i],]$Nb_reg %>% mean()
  my_df$Cum_Nb_TR_SE[i]<-my_df[my_df$SD_logAvFITC>my_df$SD_logAvFITC[i],]$Nb_reg %>% sd()
  my_df$Cum_Nb_TR_SE[i]<-my_df$Cum_Nb_TR_SE[i]/sqrt(nrow(my_df[my_df$SD_logAvFITC>my_df$SD_logAvFITC[i],]))
  ## Noise
  my_df$Cum_Noise[i]<-my_df[my_df$SD_logAvFITC>my_df$SD_logAvFITC[i],]$Mean_DMv %>% mean()
  my_df$Cum_Noise_SE[i]<-my_df[my_df$SD_logAvFITC>my_df$SD_logAvFITC[i],]$Mean_DMv %>% sd()
  my_df$Cum_Noise_SE[i]<-my_df$Cum_Noise_SE[i]/sqrt(nrow(my_df[my_df$SD_logAvFITC>my_df$SD_logAvFITC[i],]))
}

p1<-ggplot(my_df[my_df$Cum_Nb_MSR_SE>0,],aes(x=SD_logAvFITC,y=Cum_Nb_MSR))+
  geom_line(color="gray10",alpha=0.5)+
  geom_pointrange(aes(ymin=Cum_Nb_MSR-Cum_Nb_MSR_SE, ymax=Cum_Nb_MSR+Cum_Nb_MSR_SE),color="gray10",alpha=0.5)+
  scale_x_continuous(breaks=get_breaks(by=0.05,from=0.05),limits=c(0.05,0.25))+
  scale_y_continuous(breaks = get_breaks(by=1,from=1),limits = c(1,4))+
  theme_pubr()+
  ylab(expression("Number of"~MSRs))+
  xlab(expression("SD of"~E[pop]))
p1<-ggpar(p1,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p1

p2<-ggplot(my_df[my_df$Cum_Noise_SE>0,],aes(x=SD_logAvFITC,y=Cum_Noise))+
  geom_line(color="gray10",alpha=0.5)+
  geom_pointrange(aes(ymin=Cum_Noise-Cum_Noise_SE, ymax=Cum_Noise+Cum_Noise_SE),color="gray10",alpha=0.5)+
  scale_x_continuous(breaks=get_breaks(by=0.05,from=0.05),limits=c(0.05,0.25))+
  scale_y_continuous(breaks = get_breaks(by=0.02,from = 0),limits = c(0,0.04))+
  theme_pubr()+
  ylab(expression(Mean~DM[V]))+
  xlab(expression("SD of"~E[pop]))
p2<-ggpar(p2,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p2

p3<-ggplot(my_df[my_df$Cum_Nb_TR_SE>0,],aes(x=SD_logAvFITC,y=Cum_Nb_TR))+
  geom_line(color="gray10",alpha=0.5)+
  geom_pointrange(aes(ymin=Cum_Nb_TR-Cum_Nb_TR_SE, ymax=Cum_Nb_TR+Cum_Nb_TR_SE),color="gray10",alpha=0.5)+
  scale_x_continuous(breaks=get_breaks(by=0.05,from=0.05),limits=c(0.05,0.25))+
  scale_y_continuous(breaks = get_breaks(by=2,from=2),limits = c(2,8))+
  theme_pubr()+
  ylab(expression("Number of"~TRs))+
  xlab(expression("SD of"~E[pop]))
p3<-ggpar(p3,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p3
    

Sys.time()
```
## 5.11. Correlation between Noise/Plasticity and Nb of TRcoms (Pooled)
```{r TR,warning=FALSE, message=FALSE,fig.height=3,fig.width=3,dpi=300}
my_tmp<-data_frame(Nb_TRcom=seq(0,max(dtf[dtf$Essentiality=="nonessential",]$Nb_TRcom)),Nb_genes=0)
for(i in 1:nrow(my_tmp)){
  my_tmp$Nb_genes[i]<-dtf[(dtf$Essentiality=="nonessential")&(dtf$Nb_TRcom==my_tmp$Nb_TRcom[i]),] %>% nrow()
}
my_range<-my_tmp[my_tmp$Nb_genes>0,]$Nb_TRcom
my_df<-dtf[(dtf$Essentiality=="nonessential")&(dtf$Nb_TRcom %in% my_range),]

# Plasticity
p1<-ggerrorplot(my_df,x="Nb_TRcom",y="SD_logAvFITC",
          desc_stat = "mean_sd",
          add = "jitter",add.params = list(size = 0.5, jitter = 0.2,alpha=0.5),
          color=mycolpal[1],alpha=0.3,
          legend="")+
          stat_cor(data =my_df,aes(x=Nb_TRcom,y=SD_logAvFITC), label.x = 1, size=5,method = "spearman", label.sep = "\n")+
          xlab(expression("Number of TR"[com]*s))+
          ylab(expression("SD of"~E[pop]))
p1<-ggpar(p1,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p1

# Noise
p2<-ggerrorplot(my_df,x="Nb_TRcom",y="Mean_DMv",
          desc_stat = "mean_sd",
          add = "jitter",add.params = list(size = 0.5, jitter = 0.2,alpha=0.5),
          color=mycolpal[1],alpha=0.3,
          legend="")+
          scale_y_continuous(breaks = get_breaks(by=0.04,from = 0,to=0.08),limits = c(-0.02,0.1))+
          stat_cor(data =my_df,aes(x=Nb_TRcom,y=Mean_DMv), label.x = 1,label.y = 0.08, size=5,method = "spearman", label.sep = "\n")+
          xlab(expression("Number of TR"[com]*s))+
          ylab(expression("Mean"~DM[V]))
p2<-ggpar(p2,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p2
Sys.time()
```
## 5.12. Correlation between Noise/Plasticity and Nb of TR (Nonessential)
```{r TR,warning=FALSE, message=FALSE,fig.height=3,fig.width=3.5,dpi=300}
my_tmp<-data_frame(Nb_TR=seq(0,max(dtf[dtf$Essentiality=="nonessential",]$Nb_reg)),Nb_genes=0)
for(i in 1:nrow(my_tmp)){
  my_tmp$Nb_genes[i]<-dtf[(dtf$Essentiality=="nonessential")&(dtf$Nb_reg==my_tmp$Nb_TR[i]),] %>% nrow()
}
my_range<-my_tmp[my_tmp$Nb_genes>0,]$Nb_TR
my_df<-dtf[(dtf$Essentiality=="nonessential")&(dtf$Nb_reg %in% my_range),]

# Plasticity
p1<-ggerrorplot(my_df,x="Nb_reg",y="SD_logAvFITC",
          desc_stat = "mean_sd",
          add = "jitter",add.params = list(size = 0.5, jitter = 0.2,alpha=0.5),
          color=mycolpal[1],alpha=0.3,
          legend="")+
          stat_cor(data =my_df,aes(x=Nb_reg,y=SD_logAvFITC), label.x = 1, size=5,method = "spearman", label.sep = "\n")+
          xlab(expression("Number of TR"))+
          ylab(expression("SD of"~E[pop]))
p1<-ggpar(p1,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p1


# Noise
p2<-ggerrorplot(my_df,x="Nb_reg",y="Mean_DMv",
          desc_stat = "mean_sd",
          add = "jitter",add.params = list(size = 0.5, jitter = 0.2,alpha=0.5),
          color=mycolpal[1],alpha=0.3,
          legend="")+
          scale_y_continuous(breaks = get_breaks(by=0.04,from = 0,to=0.08),limits = c(-0.02,0.1))+
          stat_cor(data =my_df,aes(x=Nb_reg,y=Mean_DMv), label.x = 4,label.y = 0.08, size=5,method = "spearman", label.sep = "\n")+
          xlab(expression("Number of TR"))+
          ylab(expression("Mean"~DM[V]))
p2<-ggpar(p2,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p2
Sys.time()
```
## 5.13. Correlation between Noise/Plasticity and Nb of TR (Essential)
```{r TR,warning=FALSE, message=FALSE,fig.height=3,fig.width=3.5,dpi=300}
my_tmp<-data_frame(Nb_TR=seq(0,max(dtf[dtf$Essentiality=="essential",]$Nb_reg)),Nb_genes=0)
for(i in 1:nrow(my_tmp)){
  my_tmp$Nb_genes[i]<-dtf[(dtf$Essentiality=="essential")&(dtf$Nb_reg==my_tmp$Nb_TR[i]),] %>% nrow()
}
my_range<-my_tmp[my_tmp$Nb_genes>0,]$Nb_TR
my_df<-dtf[(dtf$Essentiality=="essential")&(dtf$Nb_reg %in% my_range),]

# Plasticity
p1<-ggerrorplot(my_df,x="Nb_reg",y="SD_logAvFITC",
          desc_stat = "mean_sd",
          add = "jitter",add.params = list(size = 0.5, jitter = 0.2,alpha=0.5),
          color=mycolpal[2],alpha=0.3,
          legend="")+
          stat_cor(data =my_df,aes(x=Nb_reg,y=SD_logAvFITC), label.x = 3, size=5,method = "spearman", label.sep = "\n")+
          xlab(expression("Number of TR"))+
          ylab(expression("SD of"~E[pop]))
p1<-ggpar(p1,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p1


# Noise
p2<-ggerrorplot(my_df,x="Nb_reg",y="Mean_DMv",
          desc_stat = "mean_sd",
          add = "jitter",add.params = list(size = 0.5, jitter = 0.2,alpha=0.5),
          color=mycolpal[2],alpha=0.3,
          legend="")+
          scale_y_continuous(breaks = get_breaks(by=0.04,from = 0,to=0.08),limits = c(-0.02,0.1))+
          stat_cor(data =my_df,aes(x=Nb_reg,y=Mean_DMv), label.x = 1,label.y = 0.08, size=5,method = "spearman", label.sep = "\n")+
          xlab(expression("Number of TR"))+
          ylab(expression("Mean"~DM[V]))
p2<-ggpar(p2,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p2
Sys.time()
```
## 5.14. Correlation between Noise/Plasticity and Nb of Sensory regulators (SRs)
```{r TR,warning=FALSE, message=FALSE,fig.height=3,fig.width=3,dpi=300}
my_tmp<-data_frame(Nb_SR=seq(0,max(dtf[dtf$Essentiality=="nonessential",]$Nb_SR)),Nb_genes=0)
for(i in 1:nrow(my_tmp)){
  my_tmp$Nb_genes[i]<-dtf[(dtf$Essentiality=="nonessential")&(dtf$Nb_SR==my_tmp$Nb_SR[i]),] %>% nrow()
}
my_range<-my_tmp[my_tmp$Nb_genes>0,]$Nb_SR
my_df<-dtf[(dtf$Essentiality=="nonessential")&(dtf$Nb_SR %in% my_range),]

# Plasticity
p1<-ggerrorplot(my_df,x="Nb_SR",y="SD_logAvFITC",
          desc_stat = "mean_sd",
          add = "jitter",add.params = list(size = 0.5, jitter = 0.2,alpha=0.5),
          color=mycolpal[1],alpha=0.3,
          legend="")+
          stat_cor(data =my_df,aes(x=Nb_SR,y=SD_logAvFITC), label.x = 1, size=5,method = "spearman", label.sep = "\n")+
          xlab(expression("Number of SRs"))+
          ylab(expression("SD of"~E[pop]))
p1<-ggpar(p1,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p1

# Noise
p2<-ggerrorplot(my_df,x="Nb_SR",y="Mean_DMv",
          desc_stat = "mean_sd",
          add = "jitter",add.params = list(size = 0.5, jitter = 0.2,alpha=0.5),
          color=mycolpal[1],alpha=0.3,
          legend="")+
          scale_y_continuous(breaks = get_breaks(by=0.04,from = 0,to=0.08),limits = c(-0.02,0.1))+
          stat_cor(data =my_df,aes(x=Nb_SR,y=Mean_DMv), label.x = 1,label.y = 0.08, size=5,method = "spearman", label.sep = "\n")+
          xlab(expression("Number of SRs"))+
          ylab(expression("Mean"~DM[V]))
p2<-ggpar(p2,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p2
Sys.time()
```
## 5.15 Noise-plasticity coupling with controling the number of MSRs
```{r TR,warning=FALSE, message=FALSE,fig.height=3,fig.width=7,dpi=300}
# MSR>2
for (i in 0:3){
  my_nb<-i #2
p1<-ggscatter(dtf[dtf$Nb_MSR>my_nb,],x="SD_logAvFITC",y="Mean_DMv",
          color="Essentiality",palette = mycolpal[c(1,2)],
          cor.coef = TRUE, # Add correlation coefficient. see ?stat_cor
          cor.coeff.args = list(method = "spearman", label.x = 0.25, label.y=0.08, label.sep = "\n",size=6),
          alpha = 0.5, size=2,legend="")+
   scale_y_continuous(breaks = get_breaks(by=0.04,from = 0,to=0.08),limits = c(-0.02,0.1))+
  scale_x_continuous(breaks = get_breaks(by=0.1,from = 0.1,to=0.4),limits = c(0.07,0.43))+
    xlab(expression("SD of"~E[pop]))+
    ylab(expression("Mean DM"[V]))
p1<-ggpar(p1,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)

# MSR<3
p2<-ggscatter(dtf[dtf$Nb_MSR<my_nb+1,],x="SD_logAvFITC",y="Mean_DMv",
          color="Essentiality",palette = mycolpal[c(1,2)],
          cor.coef = TRUE, # Add correlation coefficient. see ?stat_cor
          cor.coeff.args = list(method = "spearman", label.x = 0.25, label.y=0.08, label.sep = "\n",size=6),
          alpha = 0.5, size=2,legend="")+
   scale_y_continuous(breaks = get_breaks(by=0.04,from = 0,to=0.08),limits = c(-0.02,0.1))+
  scale_x_continuous(breaks = get_breaks(by=0.1,from = 0.1,to=0.4),limits = c(0.07,0.43))+
    xlab(expression("SD of"~E[pop]))+
    ylab(expression("Mean DM"[V]))
p2<-ggpar(p2,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)


print(p1+p2)
}



Sys.time()
```
## 5.16 Enrichment analysis for sigma factors
```{r TR}
my_t2g<-dtf %>% select(Sigma_label,Name)
my_df<-dtf[order(dtf$SD_logAvFITC,decreasing = T),]
my_genelist<-my_df$SD_logAvFITC
names(my_genelist)<-my_df$Name
my_res<-GSEA(geneList = my_genelist,TERM2GENE = my_t2g,minGSSize = 3,pvalueCutoff = 1)
my_res@result
```
## 5.17 MSR identities
```{r TR,warning=FALSE, message=FALSE,fig.height=3,fig.width=7,dpi=300}
my_tr<-dtf[!is.na(dtf$MSR),]$MSR %>% paste(., collapse = ";") %>% str_split(.,pattern=";") %>% unlist() %>% unique()
my_msr<-list()
my_gn<-list()
my_esnes<-list()
my_df<-dtf[!is.na(dtf$MSR),]
k<-0
for(i in 1:length(my_tr)){
  my_tg<-my_tr[i]
  my_tmp<-my_df[grepl(x = my_df$MSR,pattern = my_tg),]
  for(j in 1:nrow(my_tmp)){
    k<-k+1
    my_msr[[k]]<-my_tr[i]
    my_gn[[k]]<-my_tmp$Name[j]
    my_esnes[[k]]<-my_tmp$Essentiality[j]
  }
}
my_df<-data.frame(MSR=my_msr %>% unlist(),
                  Name=my_gn %>% unlist(),
                  Essentiality=my_esnes %>% unlist())
my_df$Count<-1
my_df$Essentiality<-factor(my_df$Essentiality,levels=qw(nonessential,essential))
my_df<-my_df[order(my_df$MSR),]

p<-ggbarplot(my_df, x="MSR", y="Count",
          legend="",ylab="Number of genes",
  fill = "Essentiality", color = "Essentiality", palette = mycolpal[c(1,2)])+
  rotate_x_text()
p<-ggpar(p,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p
```

# 6. Mapping KEGG pathways (previous dataset, default)
## 6.1. load the KEGG dataset
```{r Prep_gseKEGG,warning=FALSE, message=FALSE,fig.height=4,fig.width=4,dpi=300}
dkegg_prev<-paste(getwd(),"KEGG_prev","KEGG_prev.xlsx",sep="/") %>% read_xlsx()
dkegg_prev$EntrezID<-NA
i<-1
for(i in 1:nrow(dkegg_prev)){
  my_tmp<-dkegg_prev$Bnb[i] %>% str_split(.,pattern = ",") %>% unlist()
  dkegg_prev$EntrezID[i]<-df_plst_noise$EntrezID %>% paste(.,collapse = ",")
}

for(i in 1:nrow(dkegg_prev)){
  my_tmp<-dkegg_prev$EntrezID[i] %>% str_split(.,pattern = ",") %>% unlist()
  my_df<-data.frame(Pathway_ID=dkegg_prev$Pathway_ID[i],
                    EntrezID=my_tmp)
  if(i==1){
    dkegg.each.gsea_prev<-my_df
  }else{
    dkegg.each.gsea_prev<-bind_rows(dkegg.each.gsea_prev,my_df)
  }
}

dkegg.each_prev<-dkegg.each.gsea_prev
my_df<-df_plst_noise%>% select(EntrezID,Bnb)
my_df$EntrezID<-my_df$EntrezID%>% as.character()
dkegg.each_prev<-left_join(dkegg.each_prev,my_df)

# Update
dkegg<-dkegg_prev
dkegg.each<-dkegg.each_prev
dkegg.each.gsea<-dkegg.each.gsea_prev

my_df<-df_plst_noise
my_df$KEGGpathID<-NA
my_df$KEGGpath<-NA
for(i in 1:nrow(my_df)){
  my_tmp<-dkegg[grepl(x = dkegg$Bnb,pattern = my_df$Bnb[i]),]
  if(nrow(my_tmp)){
    my_df$KEGGpathID[i]<-my_tmp$Pathway_ID %>% paste(.,collapse = ";")
    my_df$KEGGpath[i]<-my_tmp$Pathway_name %>% paste(.,collapse = ";")
  }
}

Sys.time()
```
# 7. Growth characteristics of YFP fusion strains
## 7.1. Medium information
```{r Growth,warning=FALSE, message=FALSE,fig.height=2.5,fig.width=7,dpi=300}
groinfo<-paste(getwd(),"Growth_Curve","fileinfo.txt",sep = "/") %>%
  read_delim(delim = "\t",show_col_types = F) %>%
  data.frame()
groinfo$Growth_h<-NA

# Define a fuction for calc. growth rate
myslope<-function(x,grup,grlw){
  y<-transform(x,ODsbt=x$OD-min(x$OD))
  y<-subset(y,y$ODsbt>c(grlw-min(y$OD))&y$ODsbt<c(grup-min(y$OD)))
  y<-transform(y,logODsbt=log(y$ODsbt))
  z<-lm(logODsbt ~ time_s,data=y)
  z[[1]][2]*3600
}

gro<-paste(getwd(),"Growth_Curve","20181112_kinetic.csv",sep = "/") %>%
  read_csv(show_col_types = F) %>%
  data.frame()
gro<-melt(gro,id.vars =colnames(gro)[1])
colnames(gro)<-qw(time_s,well,OD)

for(i in 1:nrow(groinfo)){
  if(groinfo$YYMMDD[i]==20181112){
    temp<-subset(gro,gro$well==groinfo$MedPos[i])
    groinfo$Growth_h[i]<-myslope(temp,0.4,0.15)
  }
}

gro<-paste(getwd(),"Growth_Curve","20200213_kinetic.csv",sep = "/") %>%
  read_csv(show_col_types = F) %>%
  data.frame()
gro<-melt(gro,id.vars =colnames(gro)[1])
colnames(gro)<-qw(time_s,well,OD)
for(i in 1:nrow(groinfo)){
  if(groinfo$YYMMDD[i]==20200213){
    temp<-subset(gro,gro$well==groinfo$MedPos[i])
    groinfo$Growth_h[i]<-myslope(temp,0.4,0.15)
  }
}

Growth=createEmptyDf(nrow = length(unique(df_med$Medium)),ncol=5,colnames=qw(Medium,Medium_Series,MedID,MeanGrowth_h,SDGrowth_h))
Growth$Medium<-unique(df_med$Medium)
Growth$Medium_Series<-substr(Growth$Medium,1,1)
Growth$MedID<-substr(Growth$Medium,2,3)
for(i in 1:nrow(Growth)){
  my_tmp<-subset(groinfo,groinfo$Medium==Growth$Medium[i])
  if(nrow(my_tmp)>0){
    Growth$MeanGrowth_h[i]<-mean(my_tmp$Growth_h)
    Growth$SDGrowth_h[i]<-sd(my_tmp$Growth_h)
  }
}
Growth$Medium_Series<-factor(Growth$Medium_Series,levels=qw(E,F,G))
Growth$MedID<-factor(Growth$MedID,levels=c("01","02","08","09","10","03","04","05","06"))
# Define Richness
my_tmp<-data.frame(MedID=c("01","02","08","09","10","03","04","05","06"),Richness=0)
my_tmp$Richness<-c(1,2,3,4,5,5,6,7,8) %>% rev()
Growth<-left_join(Growth,my_tmp)

# Growth[Growth$Medium=="E08",]$MeanGrowth_h<-NA # lack of replication
# Growth[Growth$Medium=="E08",]$SDGrowth_h<-NA # lack of replication
# Growth<-Growth[Growth$Medium!="E08",] # lack of replication
my_df<-Growth
my_df$Medium_Series<-factor(my_df$Medium_Series,levels=qw(G,F,E))
my_df$MedID<-factor(my_df$MedID,levels=my_tmp$MedID)
p<-ggplot(my_df, aes(x = MedID, y = Medium_Series, fill = MeanGrowth_h))+
  geom_tile(color="gray")+
  theme_pubr()+
  rotate_x_text()+
  rremove("ticks")+rremove("axis")+
	scale_fill_gradient(low = "white", high = "black",breaks=get_breaks(by = 0.2,from = 0,to = 1),limits=c(0,1))+
  theme(legend.position ="right")+
  labs(x="Suffix",y="Prefix",fill="")+
  coord_equal()
p<-ggpar(p,font.y=my_fontsize,font.x=my_fontsize,font.legend = my_fontsize,font.tickslab =my_fontsize,ticks = FALSE)
p


my_df<-paste(getwd(),"Meta","Medium.xlsx",sep="/") %>% 
  read_xlsx(sheet = "Supplements") %>%
  data.frame()
my_df<-my_df %>% pivot_longer(cols = -MedID,values_to = "PrsAbs",names_to = "Supplements")
my_tmp<-data.frame(Supplements=unique(my_df$Supplements))
my_tmp$Suppl_label<-my_tmp$Supplements
my_tmp$Suppl_label<-str_replace(my_tmp$Suppl_label,pattern = "_20",replacement = "_(20)")
my_tmp$Suppl_label<-str_replace(my_tmp$Suppl_label,pattern = "_12",replacement = "_(12)")
my_tmp$Suppl_label<-str_replace(my_tmp$Suppl_label,pattern = "_6A",replacement = "_(6A)")
my_tmp$Suppl_label<-str_replace(my_tmp$Suppl_label,pattern = "_6B",replacement = "_(6B)")
my_tmp$Suppl_label<-str_replace_all(my_tmp$Suppl_label,pattern = "_",replacement = " ")
my_tmp$Suppl_label<-factor(my_tmp$Suppl_label,levels=my_tmp$Suppl_label)
my_df<-left_join(my_df,my_tmp)
my_df$MedID<-factor(my_df$MedID,levels=c("01","02","08","09","10","03","04","05","06"))
my_df$Text_label<-"-"
my_df[my_df$PrsAbs==1,]$Text_label<-"+"


p<-ggplot(my_df, aes(x = MedID, y = Suppl_label,label=Text_label))+
  geom_tile(fill="white",color="grey20")+
  geom_text()+
  theme_pubr()+
  rotate_x_text()+
  rremove("ticks")+rremove("axis")+
  theme(legend.position ="right")+
  labs(x="Suffix",y="Supplements")+
  coord_equal()
p<-ggpar(p,font.y=my_fontsize,font.x=my_fontsize,ticks = FALSE)
p

my_tmp<-paste(getwd(),"Meta","Medium.xlsx",sep="/") %>% 
  read_xlsx(sheet = "Carbons") %>%
  data.frame()
my_tmp

Sys.time()
```
## 7.2. Correlation between Growth rate and Supplement richness
```{r Growth,warning=FALSE, message=FALSE,fig.height=3,fig.width=3,dpi=300}
my_df<-Growth
p<-ggscatter(my_df, x = "Richness", y = "MeanGrowth_h",
             alpha=0.7,
             cor.coef = TRUE,cor.coeff.args = list(size=5,method = "spearman", label.sep = "\n"),
             legend="",
             shape="Medium_Series",
             xlab="Supplement Richness",ylab="Growth Rate [1/h]")+
  scale_x_continuous(breaks = get_breaks(by=1,from = 1,to = 8),limits=c(1,8))
p<-ggpar(p,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p
#TODO ggsave(file="Fig1c.svg", path=my_figout,dpi = 300, width = 3, height = 3)

Sys.time()
```
## 7.3. Calc. Correlation between Growth rate/Richness and Noise/Expression level
```{r Growth,warning=FALSE, message=FALSE,fig.height=3,fig.width=3,dpi=300}
my_tmp<-Growth %>% select(Medium,MeanGrowth_h,Richness)
df_gr<-left_join(df_noise,my_tmp)
my_df<-df_plst_noise
my_df$Cor_grwth_exprs<-NA
my_df$P_grwth_exprs<-NA
my_df$Cor_grwth_DMv<-NA
my_df$P_grwth_DMv<-NA
my_df$Cor_rich_exprs<-NA
my_df$P_rich_exprs<-NA
my_df$Cor_rich_DMv<-NA
my_df$P_rich_DMv<-NA
i<-1
for(i in 1:nrow(my_df)){
  my_tmp<-df_gr[df_gr$Bnb==my_df$Bnb[i],]
  my_res<-cor_test(data = my_tmp,vars = "log10Av_FITC",vars2 = "MeanGrowth_h",method = "spearman")
  my_df$Cor_grwth_exprs[i]<-my_res$cor
  my_df$P_grwth_exprs[i]<-my_res$p
  my_res<-cor_test(data = my_tmp,vars = "DMv",vars2 = "MeanGrowth_h",method = "spearman")
  my_df$Cor_grwth_DMv[i]<-my_res$cor
  my_df$P_grwth_DMv[i]<-my_res$p
  my_res<-cor_test(data = my_tmp,vars = "log10Av_FITC",vars2 = "Richness",method = "spearman")
  my_df$Cor_rich_exprs[i]<-my_res$cor
  my_df$P_rich_exprs[i]<-my_res$p
  my_res<-cor_test(data = my_tmp,vars = "DMv",vars2 = "Richness",method = "spearman")
  my_df$Cor_rich_DMv[i]<-my_res$cor
  my_df$P_rich_DMv[i]<-my_res$p
}

my_df$Q_grwth_exprs<-qvalue(my_df$P_grwth_exprs)$qvalues
my_df$Q_grwth_DMv<-qvalue(my_df$P_grwth_DMv)$qvalues
my_df$Q_rich_exprs<-qvalue(my_df$P_rich_exprs)$qvalues
my_df$Q_rich_DMv<-qvalue(my_df$P_rich_DMv)$qvalues
df_gr<-my_df

# Correlation with growth rate
p1<-ggscatter(my_df,x="Cor_grwth_exprs",y="Cor_grwth_DMv",
          color = "Essentiality",palette = mycolpal[c(1,2)],
          legend="",
          alpha=0.5)+
  scale_x_continuous(breaks = get_breaks(by=0.4,from=-0.8,to=0.8),limits = c(-0.8,0.8))+
  scale_y_continuous(breaks = get_breaks(by=0.4,from=-0.8,to=0.8),limits = c(-0.8,0.8))+
  xlab(expression(atop("Correlation between",Growth~rate~and~E[pop])))+
  ylab(expression(atop("Correlation between",Growth~rate~and~DM[V])))+
  geom_hline(yintercept = 0)+
  geom_vline(xintercept = 0)
p1

p2<-ggscatter(my_df,x="Cor_grwth_exprs",y="Q_grwth_exprs",
          color = "Essentiality",palette = mycolpal[c(1,2)],
          legend="",
          alpha=0.5)+
  scale_x_continuous(breaks = get_breaks(by=0.4,from=-0.8,to=0.8),limits = c(-0.8,0.8))+
  yscale("log10",.format = TRUE)+
  # scale_y_continuous(breaks = get_breaks(by=0.4,from=-0.8,to=0.8),limits = c(-0.8,0.8))+
  xlab(expression(atop("Correlation between",Growth~rate~and~E[pop])))+
  ylab("Adjusted p-value")+
  geom_vline(xintercept = 0)
p2
p3<-ggscatter(my_df,x="Cor_grwth_DMv",y="Q_grwth_DMv",
          color = "Essentiality",palette = mycolpal[c(1,2)],
          legend="",
          alpha=0.5)+
  scale_x_continuous(breaks = get_breaks(by=0.4,from=-0.8,to=0.8),limits = c(-0.8,0.8))+
  yscale("log10",.format = TRUE)+
  # scale_y_continuous(breaks = get_breaks(by=0.4,from=-0.8,to=0.8),limits = c(-0.8,0.8))+
  xlab(expression(atop("Correlation between",Growth~rate~and~DM[V])))+
  ylab("Adjusted p-value")+
  geom_vline(xintercept = 0)
p3

# Correlation with Richness
p4<-ggscatter(my_df,x="Cor_rich_exprs",y="Cor_rich_DMv",
          color = "Essentiality",palette = mycolpal[c(1,2)],
          legend="",
          alpha=0.5)+
  scale_x_continuous(breaks = get_breaks(by=0.4,from=-0.8,to=0.8),limits = c(-0.8,0.8))+
  scale_y_continuous(breaks = get_breaks(by=0.4,from=-0.8,to=0.8),limits = c(-0.8,0.8))+
  xlab(expression(atop("Correlation between",Richness~and~E[pop])))+
  ylab(expression(atop("Correlation between",Richness~and~DM[V])))+
  geom_hline(yintercept = 0)+
  geom_vline(xintercept = 0)
p4

p5<-ggscatter(my_df,x="Cor_rich_exprs",y="Q_rich_exprs",
          color = "Essentiality",palette = mycolpal[c(1,2)],
          legend="",
          alpha=0.5)+
  scale_x_continuous(breaks = get_breaks(by=0.4,from=-0.8,to=0.8),limits = c(-0.8,0.8))+
  yscale("log10",.format = TRUE)+
  # scale_y_continuous(breaks = get_breaks(by=0.4,from=-0.8,to=0.8),limits = c(-0.8,0.8))+
  xlab(expression(atop("Correlation between",Richness~and~E[pop])))+
  ylab("Adjusted p-value")+
  geom_vline(xintercept = 0)
p5
p6<-ggscatter(my_df,x="Cor_rich_DMv",y="Q_rich_DMv",
          color = "Essentiality",palette = mycolpal[c(1,2)],
          legend="",
          alpha=0.5)+
  scale_x_continuous(breaks = get_breaks(by=0.4,from=-0.8,to=0.8),limits = c(-0.8,0.8))+
  yscale("log10",.format = TRUE)+
  # scale_y_continuous(breaks = get_breaks(by=0.4,from=-0.8,to=0.8),limits = c(-0.8,0.8))+
  xlab(expression(atop("Correlation between",Richness~and~DM[V])))+
  ylab("Adjusted p-value")+
  geom_vline(xintercept = 0)
p6
Sys.time()
```
## 7.4. Relationship between Growth rate/Richness and Noise/Expression level
### 7.4.1. all genes
```{r Growth,warning=FALSE, message=FALSE,fig.height=3,fig.width=3.5,dpi=300}
# Bootstrapping for one sample
my_mean <- function(d, i){
  mean(d[i])
}
my_df<-df_gr
# my_df<-df_gr[df_gr$Essentiality=="nonessential",]

# Growth rate
my_res<-boot(data = my_df$Cor_grwth_exprs,statistic = my_mean,R = 2000,stype = "i")
my_ci<-boot.ci(my_res,conf = 0.95,type = "bca")
p1<-gghistogram(my_df,x = "Cor_grwth_exprs",fill="grey20",size=0.01)+
  xlab(expression(atop("Correlation between",Growth~rate~and~E[pop])))+
  ylab("Count")+
  geom_vline(xintercept = c(my_ci$t0))+
  geom_vline(xintercept = c(my_ci$bca[c(4,5)]),linetype=2)+
  scale_x_continuous(breaks = get_breaks(by=0.4,from=-0.8,to=0.8),limits = c(-0.8,0.8))
p1<-ggpar(p1,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p1

# Richness
my_res<-boot(data = my_df$Cor_rich_exprs,statistic = my_mean,R = 2000,stype = "i")
my_ci<-boot.ci(my_res,conf = 0.95,type = "bca")
p2<-gghistogram(my_df,x = "Cor_rich_exprs",fill="grey20",size=0.01)+
  xlab(expression(atop("Correlation between",Supplement~Richness~and~E[pop])))+
  ylab("Count")+
  geom_vline(xintercept = c(my_ci$t0))+
  geom_vline(xintercept = c(my_ci$bca[c(4,5)]),linetype=2)+
  scale_x_continuous(breaks = get_breaks(by=0.4,from=-0.8,to=0.8),limits = c(-0.8,0.8))
p2<-ggpar(p2,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p2

Sys.time()
```
### 7.4.2. nonessential genes
```{7 Growth,warning=FALSE, message=FALSE,fig.height=3,fig.width=3.5,dpi=300}
# Bootstrapping for one sample
my_mean <- function(d, i){
  mean(d[i])
}
my_df<-df_gr[df_gr$Essentiality=="nonessential",]

# Growth rate
my_res<-boot(data = my_df$Cor_grwth_exprs,statistic = my_mean,R = 2000,stype = "i")
my_ci<-boot.ci(my_res,conf = 0.95,type = "bca")
p1<-gghistogram(my_df,x = "Cor_grwth_exprs",fill=mycolpal[1],size=0.01)+
  xlab(expression(atop("Correlation between",Growth~rate~and~E[pop])))+
  ylab("Count")+
  geom_vline(xintercept = c(my_ci$t0))+
  geom_vline(xintercept = c(my_ci$bca[c(4,5)]),linetype=2)+
  scale_x_continuous(breaks = get_breaks(by=0.4,from=-0.8,to=0.8),limits = c(-0.8,0.8))
p1<-ggpar(p1,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p1

# Richness
my_res<-boot(data = my_df$Cor_rich_exprs,statistic = my_mean,R = 2000,stype = "i")
my_ci<-boot.ci(my_res,conf = 0.95,type = "bca")
p2<-gghistogram(my_df,x = "Cor_rich_exprs",fill=mycolpal[1],size=0.01)+
  xlab(expression(atop("Correlation between",Supplement~Richness~and~E[pop])))+
  ylab("Count")+
  geom_vline(xintercept = c(my_ci$t0))+
  geom_vline(xintercept = c(my_ci$bca[c(4,5)]),linetype=2)+
  scale_x_continuous(breaks = get_breaks(by=0.4,from=-0.8,to=0.8),limits = c(-0.8,0.8))
p2<-ggpar(p2,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p2

Sys.time()
```
### 7.4.3. essential genes
```{r Growth,warning=FALSE, message=FALSE,fig.height=3,fig.width=3.5,dpi=300}
# Bootstrapping for one sample
my_mean <- function(d, i){
  mean(d[i])
}
my_df<-df_gr[df_gr$Essentiality=="essential",]

# Growth rate
my_res<-boot(data = my_df$Cor_grwth_exprs,statistic = my_mean,R = 2000,stype = "i")
my_ci<-boot.ci(my_res,conf = 0.95,type = "bca")
p1<-gghistogram(my_df,x = "Cor_grwth_exprs",fill=mycolpal[2],size=0.01)+
  xlab(expression(atop("Correlation between",Growth~rate~and~E[pop])))+
  ylab("Count")+
  geom_vline(xintercept = c(my_ci$t0))+
  geom_vline(xintercept = c(my_ci$bca[c(4,5)]),linetype=2)+
  scale_x_continuous(breaks = get_breaks(by=0.4,from=-0.8,to=0.8),limits = c(-0.8,0.8))
p1<-ggpar(p1,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p1

# Richness
my_res<-boot(data = my_df$Cor_rich_exprs,statistic = my_mean,R = 2000,stype = "i")
my_ci<-boot.ci(my_res,conf = 0.95,type = "bca")
p2<-gghistogram(my_df,x = "Cor_rich_exprs",fill=mycolpal[2],size=0.01)+
  xlab(expression(atop("Correlation between",Supplement~Richness~and~E[pop])))+
  ylab("Count")+
  geom_vline(xintercept = c(my_ci$t0))+
  geom_vline(xintercept = c(my_ci$bca[c(4,5)]),linetype=2)+
  scale_x_continuous(breaks = get_breaks(by=0.4,from=-0.8,to=0.8),limits = c(-0.8,0.8))
p2<-ggpar(p2,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p2

Sys.time()
```
## 7.5. Relationship between Growth rate/Richness and Noise/Expression level
### 7.5.1. all genes
```{r Growth,warning=FALSE, message=FALSE,fig.height=3,fig.width=3.5,dpi=300}
# Bootstrapping for one sample
my_mean <- function(d, i){
  mean(d[i])
}
my_df<-df_gr
# my_df<-df_gr[df_gr$Essentiality=="nonessential",]

# Growth rate
my_res<-boot(data = my_df$Cor_grwth_DMv,statistic = my_mean,R = 2000,stype = "i")
my_ci<-boot.ci(my_res,conf = 0.95,type = "bca")
p1<-gghistogram(my_df,x = "Cor_grwth_DMv",fill="grey20",size=0.01)+
  xlab(expression(atop("Correlation between",Growth~rate~and~DM[V])))+
  ylab("Count")+
  geom_vline(xintercept = c(my_ci$t0))+
  geom_vline(xintercept = c(my_ci$bca[c(4,5)]),linetype=2)+
  scale_x_continuous(breaks = get_breaks(by=0.4,from=-0.8,to=0.8),limits = c(-0.8,0.8))
p1<-ggpar(p1,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p1

# Richness
my_res<-boot(data = my_df$Cor_rich_DMv,statistic = my_mean,R = 2000,stype = "i")
my_ci<-boot.ci(my_res,conf = 0.95,type = "bca")
p2<-gghistogram(my_df,x = "Cor_rich_DMv",fill="grey20",size=0.01)+
  xlab(expression(atop("Correlation between",Supplement~Richness~and~DM[V])))+
  ylab("Count")+
  geom_vline(xintercept = c(my_ci$t0))+
  geom_vline(xintercept = c(my_ci$bca[c(4,5)]),linetype=2)+
  scale_y_continuous(breaks = get_breaks(by=3,from=-0,to=9),limits = c(0,10))+
  scale_x_continuous(breaks = get_breaks(by=0.4,from=-0.8,to=0.8),limits = c(-0.8,0.8))
p2<-ggpar(p2,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p2
Sys.time()
```
### 7.5.2. nonessential genes
```{r Growth,warning=FALSE, message=FALSE,fig.height=3,fig.width=3.5,dpi=300}
# Bootstrapping for one sample
my_mean <- function(d, i){
  mean(d[i])
}

my_df<-df_gr[df_gr$Essentiality=="nonessential",]

# Growth rate
my_res<-boot(data = my_df$Cor_grwth_DMv,statistic = my_mean,R = 2000,stype = "i")
my_ci<-boot.ci(my_res,conf = 0.95,type = "bca")
p1<-gghistogram(my_df,x = "Cor_grwth_DMv",fill=mycolpal[1],size=0.01)+
  xlab(expression(atop("Correlation between",Growth~rate~and~DM[V])))+
  ylab("Count")+
  geom_vline(xintercept = c(my_ci$t0))+
  geom_vline(xintercept = c(my_ci$bca[c(4,5)]),linetype=2)+
  scale_x_continuous(breaks = get_breaks(by=0.4,from=-0.8,to=0.8),limits = c(-0.8,0.8))
p1<-ggpar(p1,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p1

# Richness
my_res<-boot(data = my_df$Cor_rich_DMv,statistic = my_mean,R = 2000,stype = "i")
my_ci<-boot.ci(my_res,conf = 0.95,type = "bca")
p2<-gghistogram(my_df,x = "Cor_rich_DMv",fill=mycolpal[1],size=0.01)+
  xlab(expression(atop("Correlation between",Supplement~Richness~and~DM[V])))+
  ylab("Count")+
  geom_vline(xintercept = c(my_ci$t0))+
  geom_vline(xintercept = c(my_ci$bca[c(4,5)]),linetype=2)+
  scale_y_continuous(breaks = get_breaks(by=3,from=-0,to=9),limits = c(0,10))+
  scale_x_continuous(breaks = get_breaks(by=0.4,from=-0.8,to=0.8),limits = c(-0.8,0.8))
p2<-ggpar(p2,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p2
Sys.time()
```
### 7.5.3. nonessential genes
```{r Growth,warning=FALSE, message=FALSE,fig.height=3,fig.width=3.5,dpi=300}
# Bootstrapping for one sample
my_mean <- function(d, i){
  mean(d[i])
}

my_df<-df_gr[df_gr$Essentiality=="essential",]

# Growth rate
my_res<-boot(data = my_df$Cor_grwth_DMv,statistic = my_mean,R = 2000,stype = "i")
my_ci<-boot.ci(my_res,conf = 0.95,type = "bca")
p1<-gghistogram(my_df,x = "Cor_grwth_DMv",fill=mycolpal[2],size=0.01)+
  xlab(expression(atop("Correlation between",Growth~rate~and~DM[V])))+
  ylab("Count")+
  geom_vline(xintercept = c(my_ci$t0))+
  geom_vline(xintercept = c(my_ci$bca[c(4,5)]),linetype=2)+
  scale_x_continuous(breaks = get_breaks(by=0.4,from=-0.8,to=0.8),limits = c(-0.8,0.8))
p1<-ggpar(p1,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p1

# Richness
my_res<-boot(data = my_df$Cor_rich_DMv,statistic = my_mean,R = 2000,stype = "i")
my_ci<-boot.ci(my_res,conf = 0.95,type = "bca")
p2<-gghistogram(my_df,x = "Cor_rich_DMv",fill=mycolpal[2],size=0.01)+
  xlab(expression(atop("Correlation between",Supplement~Richness~and~DM[V])))+
  ylab("Count")+
  geom_vline(xintercept = c(my_ci$t0))+
  geom_vline(xintercept = c(my_ci$bca[c(4,5)]),linetype=2)+
  scale_y_continuous(breaks = get_breaks(by=3,from=-0,to=9),limits = c(0,10))+
  scale_x_continuous(breaks = get_breaks(by=0.4,from=-0.8,to=0.8),limits = c(-0.8,0.8))
p2<-ggpar(p2,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p2
Sys.time()
```
# 8. PCA
## 8.1. Expression levels
```{r PCA,warning=FALSE, message=FALSE,fig.height=3,fig.width=3,dpi=300}
mypcs<-paste("PC",seq(1:3),sep="")
my_tmp<-Growth %>% select(Medium,MeanGrowth_h)
my_df<-left_join(df_noise,my_tmp)
my_dat<-my_df %>% select(Bnb,Medium,log10Av_FITC)
my_dat<-my_dat %>% pivot_wider(names_from = Medium,values_from = log10Av_FITC)
my_tmp<-data.frame(Medium=unique(df_noise$Medium),NA_count=0)
for(i in 1:nrow(my_tmp)){
  my_tmp$NA_count[i]<-nrow(my_dat[is.na(my_dat[,colnames(my_dat)==my_tmp$Medium[i]]),colnames(my_dat)==my_tmp$Medium[i]])
}
my_dat<-my_dat %>% select(Bnb,my_tmp[my_tmp$NA_count<5,]$Medium)
my_dat<-na.omit(my_dat)
my_dat<-my_dat[order(my_dat$Bnb),]

my_tmp<-my_dat %>% select(-Bnb) %>% t() %>% data.frame()
colnames(my_tmp)<-my_dat$Bnb
res.pca.exprs <- prcomp(my_tmp, scale. = T)
# The PC scores are stored in the "x" value of the prcomp object
pc_scores_exprs <- res.pca.exprs$x %>% 
  # convert to a tibble retaining the sample names as a new column
  as_tibble(rownames = "Medium")
pc_scores_exprs$label<-rownames(pc_scores_exprs)

pc_eignval_exprs <- res.pca.exprs$sdev^2
pc_eignval_exprs <- tibble(PC = factor(1:length(pc_eignval_exprs)), 
                         variance = pc_eignval_exprs) %>%   
  mutate(pct = variance/sum(variance)*100) %>% # add a new column with the percent variance
  mutate(pct_cum = cumsum(pct)) # add another column with the cumulative variance explained

df_pca_exprs<-pc_scores_exprs %>% select(Medium,PC1,PC2)
df_pca_exprs<-left_join(Growth,df_pca_exprs)

Sys.time()
```
## 8.2. DMv
```{r PCA,warning=FALSE, message=FALSE,fig.height=3,fig.width=3,dpi=300}
mypcs<-paste("PC",seq(1:3),sep="")
my_tmp<-Growth %>% select(Medium,MeanGrowth_h)
my_df<-left_join(df_noise,my_tmp)
my_dat<-my_df %>% select(Bnb,Medium,DMv)
my_dat<-my_dat %>% pivot_wider(names_from = Medium,values_from = DMv)
my_tmp<-data.frame(Medium=unique(df_noise$Medium),NA_count=0)
for(i in 1:nrow(my_tmp)){
  my_tmp$NA_count[i]<-nrow(my_dat[is.na(my_dat[,colnames(my_dat)==my_tmp$Medium[i]]),colnames(my_dat)==my_tmp$Medium[i]])
}
my_dat<-my_dat %>% select(Bnb,my_tmp[my_tmp$NA_count<5,]$Medium)
my_dat<-na.omit(my_dat)
my_dat<-my_dat[order(my_dat$Bnb),]

my_tmp<-my_dat %>% select(-Bnb) %>% t() %>% data.frame()
colnames(my_tmp)<-my_dat$Bnb
res.pca.dmv <- prcomp(my_tmp, scale. = T)
# The PC scores are stored in the "x" value of the prcomp object
pc_scores_dmv <- res.pca.dmv$x %>% 
  # convert to a tibble retaining the sample names as a new column
  as_tibble(rownames = "Medium")
pc_scores_dmv$label<-rownames(pc_scores_dmv)

pc_eignval_dmv <- res.pca.dmv$sdev^2
pc_eignval_dmv <- tibble(PC = factor(1:length(pc_eignval_dmv)), 
                         variance = pc_eignval_dmv) %>%   
  mutate(pct = variance/sum(variance)*100) %>% # add a new column with the percent variance
  mutate(pct_cum = cumsum(pct)) # add another column with the cumulative variance explained

df_pca_dmv<-pc_scores_dmv %>% select(Medium,PC1,PC2)
df_pca_dmv<-left_join(Growth,df_pca_dmv)
Sys.time()
```
## 8.3. PC1 vs. PC2 in Expression level
```{r PCA,warning=FALSE, message=FALSE,fig.height=3,fig.width=3,dpi=300}
my_df<-df_pca_exprs
my_df$Medium_Series<-factor(my_df$Medium_Series,levels=qw(E,F,G))
my_df$Richness<-factor(my_df$Richness,levels=rev(seq(1,max(my_df$Richness))))
my_count<-my_df$Richness %>% unique() %>% length()

p1<-ggscatter(data=my_df,x="PC1",y="PC2",alpha=1,size=3,
             color = "Richness",palette = viridis(n = my_count),
             # label="Medium", repel=T,font.label=5,
             shape = "Medium_Series",
             legend="",legend.title="")+
  xlab(paste("PC1 (", round(pc_eignval_exprs$pct[1],digits = 0),"%)",sep=""))+
  ylab(paste("PC2 (", round(pc_eignval_exprs$pct[2],digits = 0),"%)",sep=""))+
  scale_y_continuous(expand = expansion(mult = c(0.2, 0.1)))
p1<-ggpar(p1,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p1
#TODO ggsave(file="Fig2a.svg", path=my_figout,dpi = 300, width = 3, height = 3)

p2<-ggscatter(data=my_df,x="MeanGrowth_h",y="PC1",alpha=1,size=3,
             color = "Richness",palette = viridis(n = my_count),
             cor.coef = TRUE,cor.coeff.args = list(size=5,method="spearman", label.sep = "\n",label.x=0.6,label.y=-5),
             xlab="Growth rate [1/h]",ylab="PC1",
             shape = "Medium_Series",
             legend="",legend.title="")+
  scale_y_continuous(expand = expansion(mult = c(0.2, 0.1)))
p2<-ggpar(p2,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p2

my_df2<-my_df
my_df2$Richness_num<-as.numeric(my_df2$Richness)

p3<-ggscatter(data=my_df2,x="Richness_num",y="PC1",alpha=1,size=3,
             color = "Richness",palette = viridis(n = my_count),
             xlab="Supplement Richness",ylab="PC1",
             shape = "Medium_Series",
             legend="",legend.title="")+
  stat_cor(data =my_df2,aes(x=Richness_num,y=PC1), label.x = 4,label.y = 10, size=5,method = "spearman", label.sep = "\n")
p3<-ggpar(p3,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p3

p4<-ggboxplot(my_df2,x="Richness_num",y="PC1",add="jitter",xlab="Supplement Richness")+
  scale_y_continuous(breaks = get_breaks(by=10,from=-10,to=10),limits = c(-11,20))+
  stat_compare_means(label.x = 2,label.y = 18,size=5)
p4

# # one-way ANOVA
# my_df2 %>% anova_test(PC1 ~ Richness)

Sys.time()
```
## 8.4. PC1 vs. PC2 in Noise
```{r PCA,warning=FALSE, message=FALSE,fig.height=3,fig.width=3,dpi=300}
my_df<-df_pca_dmv
my_df$Medium_Series<-factor(my_df$Medium_Series,levels=qw(E,F,G))
my_df$Richness<-factor(my_df$Richness,levels=rev(seq(1,max(my_df$Richness))))
my_count<-my_df$Richness %>% unique() %>% length()

p<-ggscatter(data=my_df,x="PC1",y="PC2",alpha=1,size=3,
             color = "Richness",palette = viridis(n = my_count),
             # label="Medium", repel=T,font.label=5,
             shape = "Medium_Series",
             legend="",legend.title="")+
  xlab(paste("PC1 (", round(pc_eignval_dmv$pct[1],digits = 0),"%)",sep=""))+
  ylab(paste("PC2 (", round(pc_eignval_dmv$pct[2],digits = 0),"%)",sep=""))+
  scale_y_continuous(expand = expansion(mult = c(0.2, 0.1)))
p<-ggpar(p,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p


p2<-ggscatter(data=my_df,x="MeanGrowth_h",y="PC1",alpha=1,size=3,
             color = "Richness",palette = viridis(n = my_count),
             cor.coef = TRUE,cor.coeff.args = list(size=5,method="spearman", label.sep = "\n",label.x=0.6,label.y=-5),
             xlab="Growth rate [1/h]",ylab="PC1",
             shape = "Medium_Series",
             legend="",legend.title="")+
  scale_y_continuous(expand = expansion(mult = c(0.2, 0.1)))
p2<-ggpar(p2,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p2

my_df2<-my_df
my_df2$Richness_num<-as.numeric(my_df2$Richness)

p3<-ggscatter(data=my_df2,x="Richness_num",y="PC1",alpha=1,size=3,
             color = "Richness",palette = viridis(n = my_count),
             xlab="Supplement Richness",ylab="PC1",
             shape = "Medium_Series",
             legend="",legend.title="")+
  stat_cor(data =my_df2,aes(x=Richness_num,y=PC1), label.x = 4,label.y = 10, size=5,method = "spearman", label.sep = "\n")
p3<-ggpar(p3,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p3

p4<-ggboxplot(my_df2,x="Richness_num",y="PC1",add="jitter",xlab="Supplement Richness")+
  scale_y_continuous(breaks = get_breaks(by=10,from=-10,to=10),limits = c(-13,20))+
  stat_compare_means(label.x = 2,label.y = 18,size=5)
p4

# # one-way ANOVA
# my_df2 %>% anova_test(PC1 ~ Richness)
Sys.time()
```
# 9. Schematics
```{r Schematics,warning=FALSE, message=FALSE,fig.height=3,fig.width=4,dpi=300}
my_count<-100000
my_df = data.frame(
   med = factor(rep(c(3,1,5,7), each=my_count)),
   yfp = c(rnorm(n = my_count,mean = 1,sd = 0.3),
           rnorm(n = my_count,mean = 1.66,sd = 0.23),
           rnorm(n = my_count,mean = 2.34,sd = 0.18),
           rnorm(n = my_count,mean = 3,sd = 0.15)))
my_mean<-mean(my_df$yfp)
# c("#440154FF","#46337EFF","#365C8DFF","#277F8EFF","#277F8EFF","#1FA187FF","#4AC16DFF","#9FDA3AFF","#FDE725FF")
my_df$med<-factor(my_df$med,levels=c(7,5,3,1))
p<-ggdensity(my_df, x = "yfp", fill = "med",
             palette = c("#46337EFF","#277F8EFF","#4AC16DFF","#FDE725FF"),
             size=0.2,
          add="mean",legend.title="",legend="right")+
  geom_vline(xintercept = my_mean,size=1)+
  xlab(expression(log[10]~"YFP FI"))+
  ylab("Relative frequency")
p<-ggpar(p,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = c(size=0),font.ytickslab = c(size=0),ticks = FALSE,font.legend = my_fontsize)
p
#TODO ggsave(file="Fig2b.svg", path=my_figout,dpi = 300, width = 4, height = 3)

Sys.time()
```
# 10. Growth characteristis of KO strains
## 10.1. Growth test under selected environments
```{r Growth_KO,warning=FALSE, message=FALSE,fig.height=2.5,fig.width=7,dpi=300}
df_kogr_fileinfo<-paste(getwd(),"Growth","fileinfo.xlsx",sep="/") %>%
  read_xlsx()

df_kogr_fileinfo[df_kogr_fileinfo$Strain_ID=="IntS",]$Bnb<-"b2349"

my_xlfiles<-c("20250228.xlsx","20250302.xlsx","20250303.xlsx","20250304.xlsx")
my_sheets<-paste("Sheet",seq(2,10),sep="")
my_xlrange<-"B25:Y40"

i<-1
for(j in 1:length(my_xlfiles)){
  for(i in 1:length(my_sheets)){
    my_dat<-paste(getwd(),"Growth",my_xlfiles[j],sep="/") %>%
      read_xlsx(sheet = my_sheets[i],range = my_xlrange,col_names = paste("Col",seq(1,24),sep=""))
    my_dat<-my_dat %>% pivot_longer(cols =everything(),names_to = "Col",values_to = "RawOD")
    my_dat$Row<-paste(rep(LETTERS[1:16],each=24))
    my_dat$Col<-my_dat$Col %>% str_remove_all(pattern = "Col") %>% as.numeric()
    my_dat$RowCol<-paste(my_dat$Row,my_dat$Col,sep="")
    my_dat$Plate<-i
    my_dat$PlateRowCol<-paste(paste("P",my_dat$Plate,sep=""),my_dat$RowCol,sep="_")
    my_dat$Xlfile<-my_xlfiles[j]
    my_dat<-my_dat %>% select(Xlfile,Plate,Row,Col,RowCol,PlateRowCol,RawOD)
    if((j==1)&(i==1)){
      my_df<-my_dat
    }else{
      my_df<-bind_rows(my_df,my_dat)
    }
  }
}


df_kogr<-df_kogr_fileinfo
my_days<-qw(Day1,Day3,Day4,Day5)
for(i in 1:length(my_days)){
  my_df2<-my_df[my_df$Xlfile==my_xlfiles[i],]
  my_df2<-my_df2 %>% select(PlateRowCol,RawOD)
  colnames(my_df2)[2]<-paste("ODraw",my_days[i],sep="_")
  df_kogr<-left_join(df_kogr,my_df2)
}

# Day3
df_kogr$ODsbtrct_Day3<-NA
for(p in 1:max(df_kogr$Plate)){
  my_pl<-df_kogr[df_kogr$Plate==p,]
  my_df<-my_pl[(my_pl$Strain_ID=="Blank")&(my_pl$Outer_Inner=="Inner"),]
  my_bkgrnd<-mean(my_df$ODraw_Day3)+5*sd(my_df$ODraw_Day3)
  df_kogr[df_kogr$Plate==p,]$ODsbtrct_Day3<-df_kogr[df_kogr$Plate==p,]$ODraw_Day3-my_bkgrnd
}

# Day4
df_kogr$ODsbtrct_Day4<-NA
for(p in 1:max(df_kogr$Plate)){
  my_pl<-df_kogr[df_kogr$Plate==p,]
  my_df<-my_pl[(my_pl$Strain_ID=="Blank")&(my_pl$Outer_Inner=="Inner"),]
  my_bkgrnd<-mean(my_df$ODraw_Day4)+5*sd(my_df$ODraw_Day4) # Difinition of significant growth
  df_kogr[df_kogr$Plate==p,]$ODsbtrct_Day4<-df_kogr[df_kogr$Plate==p,]$ODraw_Day4-my_bkgrnd
}

# Day5
df_kogr$ODsbtrct_Day5<-NA
for(p in 1:max(df_kogr$Plate)){
  my_pl<-df_kogr[df_kogr$Plate==p,]
  my_df<-my_pl[(my_pl$Strain_ID=="Blank")&(my_pl$Outer_Inner=="Inner"),]
  my_bkgrnd<-mean(my_df$ODraw_Day5)+5*sd(my_df$ODraw_Day5) # Difinition of significant growth
  df_kogr[df_kogr$Plate==p,]$ODsbtrct_Day5<-df_kogr[df_kogr$Plate==p,]$ODraw_Day5-my_bkgrnd
}



my_df<-df_kogr_fileinfo[(df_kogr_fileinfo$Plate==1)&(df_kogr_fileinfo$Replicate==1),]
my_df<-my_df[!is.na(my_df$Bnb),]
my_df<-my_df %>% select(Strain_ID,Bnb)

# Use Day4 
my_env<-df_kogr_fileinfo$Medium %>% unique
i<-1
j<-1
for(i in 1:length(my_env)){
  my_tmp<-df_kogr[(df_kogr$Medium==my_env[i])&
                    (df_kogr$Outer_Inner=="Inner")&
                    (!is.na(df_kogr$Bnb)),]
  my_df1<-my_df
  my_df1$Medium<-my_env[i]
  my_df1$Mean_ODsbstrct<-NA
  my_df1$SD_ODsbstrct<-NA
  my_df1$BiolRepl_Total<-NA
  my_df1$BiolRepl_SignifGrowth<-NA
  my_df1$SignifGrowth<-"No Growth"
  for(j in 1:nrow(my_df1)){
    my_tmp2<-my_tmp[my_tmp$Bnb==my_df1$Bnb[j],]
    my_df1$Mean_ODsbstrct[j]<-my_tmp2$ODsbtrct_Day4 %>% mean()
    my_df1$SD_ODsbstrct[j]<-my_tmp2$ODsbtrct_Day4 %>% sd()
    my_df1$BiolRepl_Total[j]<-nrow(my_tmp2)
    my_df1$BiolRepl_SignifGrowth[j]<-nrow(my_tmp2[my_tmp2$ODsbtrct_Day4>0,])
    if(c(my_df1$BiolRepl_SignifGrowth[j]/my_df1$BiolRepl_Total[j])>c(1/2)){
      my_df1$SignifGrowth[j]<-"Growth"
    }
  }
  if(i==1){
    df_kogr_summary<-my_df1
  }else{
    df_kogr_summary<-bind_rows(df_kogr_summary,my_df1)
  }
}

my_df<-df_kogr_fileinfo %>% select(Medium,Medium_Info,Environment_ID,Carbon,Use)
my_df<-my_df %>% distinct(Medium,.keep_all = TRUE)
my_df<-my_df[!is.na(my_df$Use)|my_df$Medium=="LB",]
my_df$EnvLabel<-paste(my_df$Carbon,my_df$Environment_ID,sep="_")
my_df[my_df$Medium=="LB",]$EnvLabel<-"LB"
my_df<-my_df %>% select(Medium,EnvLabel)

df_kogr_summary<-df_kogr_summary[df_kogr_summary$Medium %in% my_df$Medium,]
df_kogr_summary<-left_join(df_kogr_summary,my_df)

df_kogr_summary[df_kogr_summary$SignifGrowth=="No Growth",]$Bnb %>% unique()

# write_csv(df_kogr_summary,file = paste(getwd(),"Growth","Output","Growth_KOstrains.csv",sep="/"))

```
## 10.2. 384-well Plate overview (Day3)
```{r Growth_KO,warning=FALSE, message=FALSE}
# p: plate id
# i: row
# j: col
textcol<-"black"
ODsbtrct_thr<-0
p<-1
for(p in 1:max(df_kogr$Plate)){
  my_pl<-df_kogr[df_kogr$Plate==p,]
  my_thr<-ODsbtrct_thr
  my_pl$ODaboveThr<-0
  my_pl[my_pl$ODsbtrct_Day3>my_thr,]$ODaboveThr<-1
  my_pl$ODaboveThr<-factor(my_pl$ODaboveThr,levels=c(1,0))
  my_pl$Col<-factor(my_pl$Col,levels=seq(1,24))
  my_pl$Row<-factor(my_pl$Row,levels=rev(LETTERS[1:16]))
  f <- ggplot(my_pl, aes(x=Col, y=Row, fill=ODaboveThr))+
  geom_tile(colour="white", size=0.2)+
  guides(fill="none")+
  labs(x="", y="", title=paste("Plate ID:",p))+
  scale_y_discrete(expand=c(0, 0))+
  scale_x_discrete(expand=c(0, 0), breaks=seq(1,24),position = "top")+
  scale_fill_manual(values=c("#d53e4f","gray90"))+
  geom_text(aes(label=RowCol),size=2.5)+
  theme_classic(base_size=10)+
  theme(legend.position="right", legend.direction="vertical",
        legend.title=element_text(colour=textcol),
        legend.margin=margin(grid::unit(0, "cm")),
        legend.text=element_text(colour=textcol, size=7, face="bold"),
        legend.key.height=grid::unit(0.8, "cm"),
        legend.key.width=grid::unit(0.2, "cm"),
        axis.text.x=element_text(size=10),
        axis.text.y=element_text(size=10),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.ticks=element_line(size=0.4),
        # plot.background=element_blank(),
        # panel.border=element_blank(),
        panel.border = element_rect(fill = NA, linewidth =1.5),
        plot.margin=margin(0.7, 0.4, 0.1, 0.2, "cm"),
        plot.title=element_text(colour=textcol, hjust=0, size=14, face="bold"),
        panel.background = element_rect(fill = "white", colour = "black", linewidth = 1.2),
        aspect.ratio=85.48/127.76
      )
  print(f)
}
```
## 10.3. 384-well Plate overview (Day4)
```{r Growth_KO,warning=FALSE, message=FALSE}
# p: plate id
# i: row
# j: col
textcol<-"black"
ODsbtrct_thr<-0
p<-1
for(p in 1:max(df_kogr$Plate)){
  my_pl<-df_kogr[df_kogr$Plate==p,]
  my_thr<-ODsbtrct_thr
  my_pl$ODaboveThr<-0
  my_pl[my_pl$ODsbtrct_Day4>my_thr,]$ODaboveThr<-1
  my_pl$ODaboveThr<-factor(my_pl$ODaboveThr,levels=c(1,0))
  my_pl$Col<-factor(my_pl$Col,levels=seq(1,24))
  my_pl$Row<-factor(my_pl$Row,levels=rev(LETTERS[1:16]))
  f <- ggplot(my_pl, aes(x=Col, y=Row, fill=ODaboveThr))+
  geom_tile(colour="white", size=0.2)+
  guides(fill="none")+
  labs(x="", y="", title=paste("Plate ID:",p))+
  scale_y_discrete(expand=c(0, 0))+
  scale_x_discrete(expand=c(0, 0), breaks=seq(1,24),position = "top")+
  scale_fill_manual(values=c("#d53e4f","gray90"))+
  geom_text(aes(label=RowCol),size=2.5)+
  theme_classic(base_size=10)+
  theme(legend.position="right", legend.direction="vertical",
        legend.title=element_text(colour=textcol),
        legend.margin=margin(grid::unit(0, "cm")),
        legend.text=element_text(colour=textcol, size=7, face="bold"),
        legend.key.height=grid::unit(0.8, "cm"),
        legend.key.width=grid::unit(0.2, "cm"),
        axis.text.x=element_text(size=10),
        axis.text.y=element_text(size=10),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.ticks=element_line(size=0.4),
        # plot.background=element_blank(),
        # panel.border=element_blank(),
        panel.border = element_rect(fill = NA, linewidth =1.5),
        plot.margin=margin(0.7, 0.4, 0.1, 0.2, "cm"),
        plot.title=element_text(colour=textcol, hjust=0, size=14, face="bold"),
        panel.background = element_rect(fill = "white", colour = "black", linewidth = 1.2),
        aspect.ratio=85.48/127.76
      )
  print(f)
}
```
## 10.4. 384-well Plate overview (Day5)
```{r Growth_KO,warning=FALSE, message=FALSE}
# p: plate id
# i: row
# j: col
textcol<-"black"
ODsbtrct_thr<-0
p<-1
for(p in 1:max(df_kogr$Plate)){
  my_pl<-df_kogr[df_kogr$Plate==p,]
  my_thr<-ODsbtrct_thr
  my_pl$ODaboveThr<-0
  my_pl[my_pl$ODsbtrct_Day5>my_thr,]$ODaboveThr<-1
  my_pl$ODaboveThr<-factor(my_pl$ODaboveThr,levels=c(1,0))
  my_pl$Col<-factor(my_pl$Col,levels=seq(1,24))
  my_pl$Row<-factor(my_pl$Row,levels=rev(LETTERS[1:16]))
  f <- ggplot(my_pl, aes(x=Col, y=Row, fill=ODaboveThr))+
  geom_tile(colour="white", size=0.2)+
  guides(fill="none")+
  labs(x="", y="", title=paste("Plate ID:",p))+
  scale_y_discrete(expand=c(0, 0))+
  scale_x_discrete(expand=c(0, 0), breaks=seq(1,24),position = "top")+
  scale_fill_manual(values=c("#d53e4f","gray90"))+
  geom_text(aes(label=RowCol),size=2.5)+
  theme_classic(base_size=10)+
  theme(legend.position="right", legend.direction="vertical",
        legend.title=element_text(colour=textcol),
        legend.margin=margin(grid::unit(0, "cm")),
        legend.text=element_text(colour=textcol, size=7, face="bold"),
        legend.key.height=grid::unit(0.8, "cm"),
        legend.key.width=grid::unit(0.2, "cm"),
        axis.text.x=element_text(size=10),
        axis.text.y=element_text(size=10),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.ticks=element_line(size=0.4),
        # plot.background=element_blank(),
        # panel.border=element_blank(),
        panel.border = element_rect(fill = NA, linewidth =1.5),
        plot.margin=margin(0.7, 0.4, 0.1, 0.2, "cm"),
        plot.title=element_text(colour=textcol, hjust=0, size=14, face="bold"),
        panel.background = element_rect(fill = "white", colour = "black", linewidth = 1.2),
        aspect.ratio=85.48/127.76
      )
  print(f)
}
```
## 10.5. Growth at Day4
```{r Growth_KO,warning=FALSE, message=FALSE,fig.height=3,fig.width=12,dpi=300}
my_df<-df_kogr[(df_kogr$Strain_ID %in% df_kogr_summary$Strain_ID)&(df_kogr$Outer_Inner=="Inner"),]
my_tmp<-df_plst_noise %>% select(Bnb,Name,Essentiality,Mean_logAvFITC,SD_logAvFITC,Mean_DMv,EntrezID)
my_df<-left_join(my_df,my_tmp)
my_df[my_df$Bnb=="b2349",]$Name<-"intS"
my_df$Name<-factor(my_df$Name,levels=c(my_tmp[order(my_tmp$SD_logAvFITC,decreasing = T),]$Name,"intS"))
my_df$Label<-paste("Δ",my_df$Name,sep="")
my_df$Label<-factor(my_df$Label,levels=paste("Δ",levels(my_df$Name),sep=""))
levels(my_df$Label)
my_df$Class<-"Sample"
my_df[my_df$Name=="intS",]$Class<-"Control"
my_df$Class<-factor(my_df$Class,levels=qw(Sample,Control))
my_envs<-c("LB","E6","F6","G6","E1","F1","G1")

for(i in 1:length(my_envs)){
  my_df1<-my_df[my_df$Medium==my_envs[i],] %>%
    as.data.frame() %>%
    select(Medium,Bnb,Name,Label,Class,ODsbtrct_Day4)
  my_df1<-my_df1[order(my_df1$Label),]
  my_df1$Label<-factor(my_df1$Label,levels =my_df1$Label %>% unique())
  stat.test<-my_df1 %>%
    t_test(ODsbtrct_Day4~Label,ref.group = "ΔintS",p.adjust.method = "BH")
  stat.test$p.adj.signif2<-stat.test$p.adj.signif
  stat.test[stat.test$p.adj.signif!="ns",]$p.adj.signif2<-"*"
    # wilcox_test(ODsbtrct_Day4~Label,ref.group = "ΔintS",p.adjust.method = "BH")
  p<-ggerrorplot(my_df1,x="Label",y="ODsbtrct_Day4", alpha=0.5,
                 desc_stat = "mean_sd",
                 ylim=c(-0.1,2.3),
            color="Class",palette = c(mycolpal[1],"black"),legend="",
            xlab="Keio strains",ylab="Cell density (OD)",
            add="jitter",add.params = list(size=1,alpha=0.5))+
    stat_pvalue_manual(stat.test,  label = "p.adj.signif2", 
                       x="group2",y=max(my_df1$ODsbtrct_Day4,na.rm = T)+0.03, hide.ns = TRUE)+
  geom_hline(yintercept = my_df1[my_df1$Name=="intS",]$ODsbtrct_Day4 %>% mean())+
    # annotate("text",x=-Inf,y=Inf,label=my_envs[i],hjust = -0.1,vjust = 1.5,size=3)+
    font("x.text",face="italic")+
    rotate_x_text()
  print(p)
}


```
## 10.6. Growth at Day5
```{r Growth_KO,warning=FALSE, message=FALSE,fig.height=3,fig.width=12,dpi=300}
my_df<-df_kogr[(df_kogr$Strain_ID %in% df_kogr_summary$Strain_ID)&(df_kogr$Outer_Inner=="Inner"),]
my_tmp<-df_plst_noise %>% select(Bnb,Name,Essentiality,Mean_logAvFITC,SD_logAvFITC,Mean_DMv,EntrezID)
my_df<-left_join(my_df,my_tmp)
my_df[my_df$Bnb=="b2349",]$Name<-"intS"
my_df$Name<-factor(my_df$Name,levels=c(my_tmp[order(my_tmp$SD_logAvFITC,decreasing = T),]$Name,"intS"))
my_df$Label<-paste("Δ",my_df$Name,sep="")
my_df$Label<-factor(my_df$Label,levels=paste("Δ",levels(my_df$Name),sep=""))
levels(my_df$Label)
my_df$Class<-"Sample"
my_df[my_df$Name=="intS",]$Class<-"Control"
my_df$Class<-factor(my_df$Class,levels=qw(Sample,Control))
my_envs<-c("LB","E6","F6","G6","E1","F1","G1")

for(i in 1:length(my_envs)){
  my_df1<-my_df[my_df$Medium==my_envs[i],] %>%
    as.data.frame() %>%
    select(Medium,Bnb,Name,Label,Class,ODsbtrct_Day5)
  my_df1<-my_df1[order(my_df1$Label),]
  my_df1$Label<-factor(my_df1$Label,levels =my_df1$Label %>% unique())
  stat.test<-my_df1 %>%
    t_test(ODsbtrct_Day5~Label,ref.group = "ΔintS",p.adjust.method = "BH")
  stat.test$p.adj.signif2<-stat.test$p.adj.signif
  stat.test[stat.test$p.adj.signif!="ns",]$p.adj.signif2<-"*"
    # wilcox_test(ODsbtrct_Day5~Label,ref.group = "ΔintS",p.adjust.method = "BH")
  p<-ggerrorplot(my_df1,x="Label",y="ODsbtrct_Day5", alpha=0.5,
                 desc_stat = "mean_sd",
                 ylim=c(-0.1,2.3),
            color="Class",palette = c(mycolpal[1],"black"),legend="",
            xlab="Keio strains",ylab="Cell density (OD)",
            add="jitter",add.params = list(size=1,alpha=0.5))+
    stat_pvalue_manual(stat.test,  label = "p.adj.signif2", 
                       x="group2",y=max(my_df1$ODsbtrct_Day5,na.rm = T)+0.03, hide.ns = TRUE)+
  geom_hline(yintercept = my_df1[my_df1$Name=="intS",]$ODsbtrct_Day5 %>% mean())+
    annotate("text",x=-Inf,y=Inf,label=my_envs[i],hjust = -0.1,vjust = 1.5,size=3)+
    font("x.text",face="italic")+
    rotate_x_text()
  print(p)
}


```
## 10.6.Comparison of growth yild between day 4 and day 5
```{r Growth_KO,warning=FALSE, message=FALSE,fig.height=3,fig.width=3,dpi=300}
my_df<-df_kogr_fileinfo[(df_kogr_fileinfo$Plate==1)&(df_kogr_fileinfo$Replicate==1),]
my_df<-my_df[!is.na(my_df$Bnb),]
my_df<-my_df %>% select(Strain_ID,Bnb)

# Use Day4 
my_env<-df_kogr_fileinfo$Medium %>% unique
i<-1
j<-1
for(i in 1:length(my_env)){
  my_tmp<-df_kogr[(df_kogr$Medium==my_env[i])&
                    (df_kogr$Outer_Inner=="Inner")&
                    (!is.na(df_kogr$Bnb)),]
  my_df1<-my_df
  my_df1$Medium<-my_env[i]
  my_df1$Mean_ODsbstrct_Day4<-NA
  my_df1$SD_ODsbstrct_Day4<-NA
  my_df1$BiolRepl_Total<-NA
  my_df1$BiolRepl_SignifGrowth_Day4<-NA
  my_df1$SignifGrowth_Day4<-"No Growth"
  my_df1$Mean_ODsbstrct_Day5<-NA
  my_df1$SD_ODsbstrct_Day5<-NA
  my_df1$BiolRepl_SignifGrowth_Day5<-NA
  my_df1$SignifGrowth_Day5<-"No Growth"
  for(j in 1:nrow(my_df1)){
    my_tmp2<-my_tmp[my_tmp$Bnb==my_df1$Bnb[j],]
    my_df1$Mean_ODsbstrct_Day4[j]<-my_tmp2$ODsbtrct_Day4 %>% mean()
    my_df1$SD_ODsbstrct_Day4[j]<-my_tmp2$ODsbtrct_Day4 %>% sd()
    my_df1$BiolRepl_Total[j]<-nrow(my_tmp2)
    my_df1$BiolRepl_SignifGrowth_Day4[j]<-nrow(my_tmp2[my_tmp2$ODsbtrct_Day4>0,])
    if(c(my_df1$BiolRepl_SignifGrowth_Day4[j]/my_df1$BiolRepl_Total[j])>c(1/2)){
      my_df1$SignifGrowth_Day4[j]<-"Growth"
    }
    my_df1$Mean_ODsbstrct_Day5[j]<-my_tmp2$ODsbtrct_Day5 %>% mean()
    my_df1$SD_ODsbstrct_Day5[j]<-my_tmp2$ODsbtrct_Day5 %>% sd()
    my_df1$BiolRepl_Total[j]<-nrow(my_tmp2)
    my_df1$BiolRepl_SignifGrowth_Day5[j]<-nrow(my_tmp2[my_tmp2$ODsbtrct_Day5>0,])
    if(c(my_df1$BiolRepl_SignifGrowth_Day5[j]/my_df1$BiolRepl_Total[j])>c(1/2)){
      my_df1$SignifGrowth_Day5[j]<-"Growth"
    }
  }
  if(i==1){
    df_kogr_day45<-my_df1
  }else{
    df_kogr_day45<-bind_rows(df_kogr_day45,my_df1)
  }
}

my_df<-df_kogr_fileinfo %>% select(Medium,Medium_Info,Environment_ID,Carbon,Use)
my_df<-my_df %>% distinct(Medium,.keep_all = TRUE)
my_df<-my_df[!is.na(my_df$Use)|my_df$Medium=="LB",]
my_df$EnvLabel<-paste(my_df$Carbon,my_df$Environment_ID,sep="_")
my_df[my_df$Medium=="LB",]$EnvLabel<-"LB"
my_df<-my_df %>% select(Medium,EnvLabel)

df_kogr_day45<-df_kogr_day45[df_kogr_day45$Medium %in% my_df$Medium,]
df_kogr_day45<-left_join(df_kogr_day45,my_df)

df_kogr_day45[df_kogr_day45$SignifGrowth_Day4=="No Growth",]$Bnb %>% unique()
df_kogr_day45[df_kogr_day45$SignifGrowth_Day5=="No Growth",]$Bnb %>% unique()


formula <- y ~ 0+x
ggscatter(df_kogr_day45,x="Mean_ODsbstrct_Day4",y="Mean_ODsbstrct_Day5",size=0.3,alpha=0.3,
          xlab="Cell density after 60 h",ylab="Cell density after 84 h")+
  stat_smooth(method = "lm", formula = formula) +
  stat_poly_eq(parse=T, aes(label = paste(stat(eq.label),stat(rr.label),sep="*\", \"*")), formula=formula)
```
## 10.7.
```{r Growth_KO,warning=FALSE, message=FALSE,fig.height=3,fig.width=12,dpi=300}
my_df<-df_kogr_summary
my_tmp<-df_plst_noise %>% select(Bnb,Name,Essentiality,Mean_logAvFITC,SD_logAvFITC,Mean_DMv,EntrezID)
my_df<-left_join(my_df,my_tmp)
my_df[my_df$Bnb=="b2349",]$Name<-"IntS"
my_df$Name<-factor(my_df$Name,levels=c(my_tmp[order(my_tmp$SD_logAvFITC,decreasing = T),]$Name,"IntS"))
my_df$Rel_OD<-NA
my_df<-my_df[my_df$Medium!="LB",]
my_df[my_df$SignifGrowth=="No Growth",]$Mean_ODsbstrct<-0
my_envs<-c("E6","F6","G6","E1","F1","G1")
for(i in 1:length(my_envs)){
  my_df[my_df$Medium==my_envs[i],]$Rel_OD<-my_df[my_df$Medium==my_envs[i],]$Mean_ODsbstrct/my_df[(my_df$Strain_ID=="IntS")&(my_df$Medium==my_envs[i]),]$Mean_ODsbstrct
}
ggboxplot(my_df,x="Name",y="Rel_OD",add="jitter",add.params = list(size=1,alpha=0.8))+rotate_x_text()+
  geom_hline(yintercept = 1,color="gray")

ggscatter(my_df[my_df$Medium=="F6",],x="Rel_OD",y="SD_logAvFITC",cor.coef = TRUE)


my_df1<-my_tmp
my_df1$Mean_Rel_OD<-NA
my_df1$Med_Rel_OD<-NA
for(i in 1:nrow(my_df1)){
  my_df1$Mean_Rel_OD[i]<-my_df[my_df$Bnb==my_df1$Bnb[i],]$Rel_OD %>% mean(na.rm=T)
  my_df1$Med_Rel_OD[i]<-my_df[my_df$Bnb==my_df1$Bnb[i],]$Rel_OD %>% median()
}

ggscatter(my_df1,x="Mean_Rel_OD",y="SD_logAvFITC",cor.coef = TRUE)
```
# 11. ENV Dataset
## 11.1. correlation analysis
```{r ENV,warning=FALSE, message=FALSE,fig.height=3,fig.width=3.5,dpi=300}
df_env<-paste(getwd(),"ENV_Dataset/df_env.csv",sep="/") %>%
  read_csv()
my_tmp<-df_env %>% select(Bnb,DMenv)
my_df<-left_join(df_plst_noise,my_tmp)

p1<-ggscatter(my_df[my_df$Essentiality=="nonessential",],y="SD_logAvFITC",x="DMenv",
          color="Essentiality",palette = mycolpal[1],
          label="Name",repel = T, label.select = list(criteria = "`x` > 0.8 | `y` > 0.25"),font.label = c("italic"),
          cor.coef = TRUE, # Add correlation coefficient. see ?stat_cor
          cor.coeff.args = list(method = "spearman", label.y = 0.45, label.x=0.2, label.sep = "\n",size=5),
          alpha = 0.5, size=2,legend="")+
  scale_x_continuous(breaks = get_breaks(by=1,from = 0,to=2),limits = c(-0.6,2.3))+
  scale_y_continuous(breaks = get_breaks(by=0.1,from = 0.1,to=0.5),limits = c(0.07,0.5))+
  geom_hline(yintercept = median(my_df[my_df$Essentiality=="nonessential",]$SD_logAvFITC),linetype="dashed",color=mycolpal[1])+
  geom_vline(xintercept = median(my_df[my_df$Essentiality=="nonessential",]$DMenv),linetype="dashed",color=mycolpal[1])+
    ylab(expression("SD of"~E[pop]))+
    xlab(expression("DM"[env]))
p1<-ggpar(p1,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p1
#TODO ggsave(file="Fig2e_nes.svg", path=my_figout,dpi = 300, width = 3.5, height = 3)

p2<-ggscatter(my_df[my_df$Essentiality=="essential",],y="SD_logAvFITC",x="DMenv",
          color="Essentiality",palette = mycolpal[2],
          label="Name",repel = T, label.select = list(criteria = "`x` > 0.1 | `y` > 0.2"),font.label = c("italic"),
          cor.coef = TRUE, # Add correlation coefficient. see ?stat_cor
          cor.coeff.args = list(method = "spearman", label.y = 0.4, label.x=0.07, label.sep = "\n",size=5),
          alpha = 0.5, size=2,legend="")+
  scale_x_continuous(breaks = get_breaks(by=1,from = 0,to=2),limits = c(-0.6,2.3))+
  scale_y_continuous(breaks = get_breaks(by=0.1,from = 0.1,to=0.5),limits = c(0.07,0.5))+
  geom_hline(yintercept = median(my_df[my_df$Essentiality=="essential",]$SD_logAvFITC),linetype="dashed",color=mycolpal[2])+
  geom_vline(xintercept = median(my_df[my_df$Essentiality=="essential",]$DMenv),linetype="dashed",color=mycolpal[2])+
    ylab(expression("SD of"~E[pop]))+
    xlab(expression("DM"[env]))
p2<-ggpar(p2,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p2
#TODO ggsave(file="Fig2e_ess.svg", path=my_figout,dpi = 300, width = 3.5, height = 3)

p3<-ggscatter(my_df[my_df$Essentiality=="nonessential",],y="Mean_DMv",x="DMenv",
          color="Essentiality",palette = mycolpal[1],
          label="Name",repel = T, label.select = list(criteria = "(`x` > 0.8 & `y` > 0)|`y` > 0.04"),font.label = c("italic"),
          cor.coef = TRUE, # Add correlation coefficient. see ?stat_cor
          cor.coeff.args = list(method = "spearman", label.y = 0.09, label.x=0.8, label.sep = "\n",size=5),
          alpha = 0.5, size=2,legend="")+
  scale_x_continuous(breaks = get_breaks(by=1,from = 0,to=2),limits = c(-0.6,2.3))+
  scale_y_continuous(breaks = get_breaks(by=0.04,from = 0,to=0.08),limits = c(-0.02,0.1))+
    ylab(expression("Mean"~DM[V]))+
    xlab(expression("DM"[env]))
p3<-ggpar(p3,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p3
#TODO ggsave(file="Fig4b_nes.svg", path=my_figout,dpi = 300, width = 3.5, height = 3)

p4<-ggscatter(my_df[my_df$Essentiality=="essential",],y="Mean_DMv",x="DMenv",
          color="Essentiality",palette = mycolpal[2],
          label="Name",repel = T, label.select = list(criteria = "`x` > 0.1 | `y` > 0.01"),font.label = c("italic"),
          cor.coef = TRUE, # Add correlation coefficient. see ?stat_cor
          cor.coeff.args = list(method = "spearman", label.y = 0.09, label.x=0.8, label.sep = "\n",size=5),
          alpha = 0.5, size=2,legend="")+
  scale_x_continuous(breaks = get_breaks(by=1,from = 0,to=2),limits = c(-0.6,2.3))+
  scale_y_continuous(breaks = get_breaks(by=0.04,from = 0,to=0.08),limits = c(-0.02,0.1))+
    ylab(expression("Mean"~DM[V]))+
    xlab(expression("DM"[env]))
p4<-ggpar(p4,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p4
#TODO ggsave(file="Fig4b_ess.svg", path=my_figout,dpi = 300, width = 3.5, height = 3)

p5<-ggscatter(my_df,y="Mean_DMv",x="DMenv",
          color="Essentiality",palette = mycolpal,
          # label="Name",repel = T, label.select = list(criteria = "`x` > 0.1 | `y` > 0.01"),
          cor.coef = TRUE, # Add correlation coefficient. see ?stat_cor
          cor.coeff.args = list(method = "spearman", label.y = 0.09, label.x=0.8, label.sep = "\n",size=5),
          alpha = 0.5, size=2,legend="")+
  scale_x_continuous(breaks = get_breaks(by=1,from = 0,to=2),limits = c(-0.6,2.3))+
  scale_y_continuous(breaks = get_breaks(by=0.04,from = 0,to=0.08),limits = c(-0.02,0.1))+
    ylab(expression("Mean"~DM[V]))+
    xlab(expression("DM"[env]))
p5<-ggpar(p5,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p5
#TODO ggsave(file="Fig4b_pool.svg", path=my_figout,dpi = 300, width = 3.5, height = 3)

Sys.time()
```
## 11.2. Statistical test
```{r ENV,warning=FALSE, message=FALSE,fig.height=3,fig.width=3,dpi=300}
my_tmp<-df_env %>% select(Bnb,DMenv)
my_df<-left_join(df_plst_noise,my_tmp)
my_df %>% wilcox_test(DMenv ~ Essentiality)

Sys.time()
```
## 11.3.
```{r ENV,warning=FALSE, message=FALSE,fig.height=6,fig.width=12,dpi=300}
my_df<-df_env
my_df$Nb_reg<-0
my_df$TR<-NA
my_df$Sigma<-NA
i<-2
for(i in 1:nrow(my_df)){
  my_tmp<-TRN[TRN$gene_id == my_df$Bnb[i],]
  if(nrow(my_tmp)>0){
    my_df$Nb_reg[i]<-my_tmp$regulator %>% unique() %>% length()
    my_df$TR[i]<-my_tmp$regulator %>% unique() %>% paste(.,collapse = ";")
    my_sig<-my_tmp[my_tmp$category=="sigma",]
    if(nrow(my_sig)>0){
      my_sig$regulator<-factor(my_sig$regulator,levels=my_sigmas)
      my_sig<-my_sig[order(my_sig$regulator),]
      my_df$Sigma[i]<-my_sig$regulator %>% unique() %>% paste(.,collapse = ";")
    }
  }
}
my_df[is.na(my_df$Sigma),]$Sigma<-"Null"
my_df$Sigma %>% unique()

my_level<-c("Null","RpoD","RpoE","RpoH","RpoN","RpoS","FecI","FliA","RpoD;RpoE","RpoD;RpoH","RpoD;RpoN","RpoD;RpoS","RpoD;FliA","RpoN;RpoH","RpoH;RpoS","RpoE;RpoH","RpoN;RpoS","RpoD;RpoE;RpoH","RpoD;RpoH;RpoS","RpoD;RpoN;RpoS","RpoD;RpoE;RpoN;RpoS")
my_df$Sigma<-factor(my_df$Sigma,levels=my_level)



ggboxplot(my_df[(my_df$Nb_reg<7)&(my_df$Nb_reg>0),],x="Sigma",y="DMenv",color="Sigma",
          facet.by = "Nb_reg",legend="",
          add = "jitter",add.params = list(size=0.6,alpha=0.3,position = position_jitter(w = 0.01, h = 0)))+
  rotate_x_text()

ggboxplot(my_df[(my_df$Nb_reg<7)&(my_df$Nb_reg>0),],x="Sigma",y="DMenv",color="Essentiality",palette = mycolpal[c(2,1)],
          facet.by = "Nb_reg",legend="",
          add = "jitter",add.params = list(size=0.6,alpha=0.3,position = position_jitter(w = 0.01, h = 0)))+
  rotate_x_text()

ggboxplot(my_df[(my_df$Nb_reg>0),],x="Sigma",y="DMenv",color="Essentiality",palette = mycolpal[c(2,1)],
          facet.by = "Nb_reg",legend="",
          add = "jitter",add.params = list(size=0.6,alpha=0.3,position = position_jitter(w = 0.01, h = 0)))+
  rotate_x_text()

```
## 11.4.
```{r ENV,warning=FALSE, message=FALSE,fig.height=6,fig.width=12,dpi=300}
my_df<-TRN
my_df$Essentiality<-"nonessential"
my_df[my_df$gene_id %in% dBnb[dBnb$ECKnb %in% dess$ECKnb,]$Bnb,]$Essentiality<-"essential"


my_regs<-qw(ArgP,MraZ,NagC)
my_reg<-my_regs[3]
my_df[my_df$regulator==my_reg,] %>% nrow()
my_df[(my_df$regulator==my_reg)&(my_df$Essentiality=="essential"),] %>% nrow()

```
# 12. Promoter-mediated Noise
## 12.1. Define PromDM
```{r Prom_med_Noise,warning=FALSE, message=FALSE,fig.height=3,fig.width=3,dpi=300}
df_prom_noise<-paste(getwd(),"Promoter_Noise","Output","Promoter_Noise_Essentiality.csv",sep="/") %>%
  read_csv()
df_prom_noise$PromoterEssentiality<-factor(df_prom_noise$PromoterEssentiality,levels = qw(nonessential,essential))
df_prom_noise<-df_prom_noise[!is.na(df_prom_noise$Mean_gfp),]

df_prom_noise<-df_prom_noise[order(df_prom_noise$Mean_log_gfp),]
df_prom_noise<-transform(df_prom_noise,PromRunMed=NA,PromSmoothSp=NA,PromDM=NA)
df_prom_noise$PromRunMed<-runmed(df_prom_noise$SD_log_gfp,41)
PromSSvislist<-createEmptyDf(nrow=1000,ncol=2, colnames = qw(logx,SS))
PromSSvislist$logx=seq(min(df_prom_noise$Mean_log_gfp),max(df_prom_noise$Mean_log_gfp),length=nrow(PromSSvislist))
misplist<-list()
misplist[[1]]<-smooth.spline(data.frame(x=df_prom_noise$Mean_log_gfp,y=df_prom_noise$PromRunMed),df=12)
PromSSvislist$SS<-predict(misplist[[1]],PromSSvislist$logx)[[2]]
df_prom_noise$PromSmoothSp<-predict(misplist[[1]],df_prom_noise$Mean_log_gfp)[[2]]
df_prom_noise$PromDM<-df_prom_noise$SD_log_gfp-df_prom_noise$PromSmoothSp

my_limit<-PromSSvislist[PromSSvislist$SS==max(PromSSvislist$SS),]$logx
df_prom_noise$DetectLimit<-"Above"
df_prom_noise[df_prom_noise$Mean_log_gfp<my_limit,]$DetectLimit<-"Under"

my_df<-df_env %>% select(Bnb,MEANenv,DMenv)
df_prom_noise<-left_join(df_prom_noise,my_df)
df_prom_noise_sbst<-df_prom_noise[df_prom_noise$DetectLimit=="Above",]


# Relationship between mean and promoter-mediated noise
p1<-ggscatter(df_prom_noise,x="Mean_log_gfp",y="SD_log_gfp",
              color="PromoterEssentiality",palette = mycolpal[c(1,2)],
              # cor.coef = TRUE,
              # cor.coeff.args = list(method = "spearman", label.x = 1.5, label.y=0.8, label.sep = "\n",size=5),
              alpha=0.5,size=0.3,legend="")+
  xlab(expression("E"[pop]~"in promoter"))+
  ylab(expression("V"[pop]~"in promoter"))+
  # scale_x_continuous(breaks = get_breaks(by = 2, from = -2),limits =  c(-2, 4))+
  scale_y_continuous(breaks = get_breaks(by = 0.1, from = 0.1),limits =  c(0.08, 0.31))+
  geom_vline(xintercept = my_limit,linetype=2)+
  geom_line(data=df_prom_noise,aes(x=Mean_log_gfp,y=PromRunMed),colour="magenta", size=1.75)+
  geom_line(data=PromSSvislist,aes(x=logx,y=SS),colour="deepskyblue", size=0.75)
p1<-ggpar(p1,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p1

Sys.time()
```
## 12.2. Relationship between DMprom and DMenv
```{r Prom_med_Noise,warning=FALSE, message=FALSE,fig.height=3,fig.width=3,dpi=300}
p1<-ggscatter(df_prom_noise_sbst,x="PromDM",y="DMenv",
              color="PromoterEssentiality",palette = mycolpal[c(1,2)],
              cor.coef = TRUE,
              cor.coeff.args = list(method = "spearman", label.x = 0.06, label.y=2.2, label.sep = "\n",size=5),
              alpha=0.5,size=0.3,legend="")+
  xlab(expression("DM"[prom]))+
  ylab(expression("DM"[env]))+
  scale_x_continuous(breaks = get_breaks(by = 0.05, from = 0),limits =  c(-0.05, 0.14))+
  scale_y_continuous(breaks = get_breaks(by = 1, from = 0),limits =  c(-0.6, 2.7))
p1<-ggpar(p1,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p1

p2<-ggscatter(df_prom_noise_sbst[df_prom_noise_sbst$PromoterEssentiality=="nonessential",],x="PromDM",y="DMenv",
              color="PromoterEssentiality",palette = mycolpal[c(1)],
              cor.coef = TRUE,
              cor.coeff.args = list(method = "spearman", label.x = 0.06, label.y=2.2, label.sep = "\n",size=5),
              alpha=0.5,size=0.3,legend="")+
  xlab(expression("DM"[prom]))+
  ylab(expression("DM"[env]))+
  scale_x_continuous(breaks = get_breaks(by = 0.05, from = 0),limits =  c(-0.05, 0.14))+
  scale_y_continuous(breaks = get_breaks(by = 1, from = 0),limits =  c(-0.6, 2.7))
p2<-ggpar(p2,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p2

p3<-ggscatter(df_prom_noise_sbst[df_prom_noise_sbst$PromoterEssentiality=="essential",],x="PromDM",y="DMenv",
              color="PromoterEssentiality",palette = mycolpal[c(2)],
              cor.coef = TRUE,
              cor.coeff.args = list(method = "spearman", label.x = 0.06, label.y=2.2, label.sep = "\n",size=5),
              alpha=0.5,size=0.3,legend="")+
  xlab(expression("DM"[prom]))+
  ylab(expression("DM"[env]))+
  scale_x_continuous(breaks = get_breaks(by = 0.05, from = 0),limits =  c(-0.05, 0.14))+
  scale_y_continuous(breaks = get_breaks(by = 1, from = 0),limits =  c(-0.6, 2.7))
p3<-ggpar(p3,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p3

Sys.time()
```
## 12.3. Relationship between DMprom and DMv
```{r Prom_med_Noise,warning=FALSE, message=FALSE,fig.height=3,fig.width=3,dpi=300}
my_df<-left_join(df_plst_noise,df_prom_noise_sbst)
p1<-ggscatter(my_df,x="PromDM",y="Mean_DMv",
              color="Essentiality",palette = mycolpal[c(1,2)],
              cor.coef = TRUE,
              cor.coeff.args = list(method = "spearman", label.x = 0.01, label.y=0.04, label.sep = "\n",size=5),
              alpha=0.5,size=0.3,legend="")+
  xlab(expression("DM"[prom]))+
  ylab(expression("DM"[v]))+
  scale_x_continuous(breaks = get_breaks(by = 0.04, from = -0.02),limits =  c(-0.025, 0.07))+
  scale_y_continuous(breaks = get_breaks(by = 0.04, from = -0.02),limits =  c(-0.025, 0.07))
p1<-ggpar(p1,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p1

Sys.time()
```
# 13. Promoter Analysis
## 13.1 load sigma 70 promoters
```{r Promoter,warning=FALSE, message=FALSE,fig.height=3,fig.width=3,dpi=300}
df_sigma70<-paste(getwd(),"Sigmulon/Output/Sigma70_Promoters.csv",sep = "/") %>%
  read_csv()
df_sigma70<-df_sigma70[!is.na(df_sigma70$Dwnstrm_Bnb),]
# df_sigma70<-df_sigma70[!is.na(df_sigma70$Lv_dist_from_cons),]
my_df<-df_plst_noise
my_df$Sigma70_pro<-NA
my_df$Min_Lv_dist<-NA
my_df$Ave_Lv_dist<-NA
for(i in 1:nrow(my_df)){
  my_tmp<-df_sigma70[grepl(pattern = my_df$Bnb[i],x = df_sigma70$Dwnstrm_Bnb),]
  if(nrow(my_tmp)>0){
    my_df$Sigma70_pro[i]<-paste(my_tmp$`Promoter Name`,collapse = ";")
    my_tmp<-my_tmp[!is.na(my_tmp$Lv_dist_from_cons),]
    if(nrow(my_tmp)>0){
      my_df$Min_Lv_dist[i]<-min(my_tmp$Lv_dist_from_cons,na.rm=TRUE)
      my_df$Ave_Lv_dist[i]<-mean(my_tmp$Lv_dist_from_cons,na.rm=TRUE)
    }
  }
}

df_all_prom<-paste(getwd(),"Sigmulon/Output/All_Promoters.csv",sep = "/") %>%
  read_csv()
my_df$All_pro<-NA
my_df$Nb_of_pro<-0
for(i in 1:nrow(my_df)){
  my_tmp<-df_all_prom[grepl(pattern = my_df$Bnb[i],x = df_all_prom$Dwnstrm_Bnb),]
  if(nrow(my_tmp)>0){
    my_df$All_pro[i]<-paste(my_tmp$`Promoter Name`,collapse = ";")
    my_df$Nb_of_pro[i]<-nrow(my_tmp)
  }
}

df_sigm_summary<-my_df

ggscatter(df_sigm_summary[df_sigm_summary$Essentiality=="nonessential",],x="Ave_Lv_dist",y="Mean_DMv",
          cor.coef = TRUE,cor.coeff.args = list(method = "spearman", label.x = 4, label.y=0.07, label.sep = "\n",size=5),
          alpha=0.5)
ggscatter(df_sigm_summary[df_sigm_summary$Essentiality=="nonessential",],x="Ave_Lv_dist",y="SD_logAvFITC",
          cor.coef = TRUE,cor.coeff.args = list(method = "spearman", label.x = 4, label.y=0.35, label.sep = "\n",size=5),
          alpha=0.5)


my_bn<-list()
my_sigma70<-list()
k<-0
for(i in 1:nrow(df_sigm_summary)){
  if(!is.na(df_sigm_summary$Sigma70_pro[i])){
    my_tmp<-df_sigm_summary$Sigma70_pro[i] %>%
      str_split(pattern = ";") %>% 
      unlist()
    for(j in 1:length(my_tmp)){
      k<-k+1
      my_bn[[k]]<-df_sigm_summary$Bnb[i]
      my_sigma70[[k]]<-my_tmp[j]
    }
  }
}
my_df<-data.frame(Bnb=my_bn %>% unlist(),
                  Sigma70_pro=my_sigma70 %>% unlist())
my_tmp<-df_plst_noise %>% select(Bnb,Name,Essentiality)
my_df<-left_join(my_df,my_tmp)
my_tmp<-df_sigma70 %>% select(`Promoter Name`,Minus_10_box,Minus_35_box,Concat_35_10_box)
colnames(my_tmp)[1]<-"Sigma70_pro"
my_df<-left_join(my_df,my_tmp)
df_sigma70_summary<-my_df


Sys.time()
```
## 13.2. Phylogenetic tree in conatenate seqs of -35 and -10 elements
```{r Seq_Anal,warning=FALSE, message=FALSE,fig.height=10,fig.width=6,dpi=300}
my_df<-df_sigma70_summary[!is.na(df_sigma70_summary$Concat_35_10_box),]
my_df$label<-paste(my_df$Name,my_df$Sigma70_pro,sep="_")
Boxseqs<-my_df$Concat_35_10 %>% DNAStringSet()
names(Boxseqs)<-my_df$label

seqalign<-msa(Boxseqs,method = "ClustalOmega",order = "input")
alignment_seqinr<-msaConvert(seqalign,type="seqinr::alignment")
distances<-seqinr::dist.alignment(alignment_seqinr,"identity") # compute the distance matrix from the alignment
tree<-ape::nj(distances) # compute the neighbor-joining tree

cls <- list(Nes=my_df[my_df$Essentiality=="nonessential",]$label,
            Ess=my_df[my_df$Essentiality=="essential",]$label)

tree <- groupOTU(tree, cls)
mycolpal<-get_palette("lancet",9)

p<-ggtree(tree)+
    geom_tippoint(aes(color=group))+
  scale_color_manual(values=c(mycolpal[2],mycolpal[1],"gray60"))+ 
  theme(legend.position="")+
  geom_tiplab(offset = 0.01,size=3)+
  # geom_tiplab(aes(subset=(group=="Synthetic")),offset=0.01, size=3)+
  geom_treescale(offset=-2.5,width=0.1)+ xlim_tree(0.65)
p

my_df1<-data.frame(name=names(Boxseqs),seq=seq(1,length(names(Boxseqs))))
my_df1$name<-factor(my_df1$name,levels = get_taxa_name(p))
my_order<-my_df1[order(my_df1$name),]$seq
Boxseqs2<-Boxseqs[my_order]
my_aln<-seqalign<-msa(Boxseqs2,method = "ClustalOmega",order = "input")
class(my_aln)<-"DNAMultipleAlignment"
ggmsa(my_aln, color = "Chemistry_NT", font = "DroidSansMono", char_width = 0.5, seq_name = TRUE ,)

Sys.time()
```
## 13.3. Phylogenetic tree in Binding sites of Transcriptional Regulators
```{r Seq_Anal,warning=FALSE, message=FALSE,fig.height=6,fig.width=6,dpi=600}
df_TF_RISet<-paste(getwd(),"RegulonDB","2025_ver_12","TF_RISet.tsv",sep="/") %>%
  read_delim()
df_TUSet<-paste(getwd(),"RegulonDB","2025_ver_12","TUSet.tsv",sep="/") %>%
  read_delim(skip = 28)
df_GeneProductSet<-paste(getwd(),"RegulonDB","2025_ver_12","GeneProductSet.tsv",sep="/") %>%
  read_delim(skip=29)
df_TuPromOperonTFSet<-paste(getwd(),"RegulonDB","2025_ver_12","TuPromOperonTFSet.tsv",sep="/") %>%
  read_delim()

## TU
my_df<-df_TuPromOperonTFSet %>% select(`1)tuId`,`2)tuName`,`7)promoterId`,`8)promoterName`,`14)tuGenesBnumber`)
my_tu<-list()
my_bn<-list()
k<-0
for(i in 1:nrow(df_plst_noise)){
  my_bni<-df_plst_noise$Bnb[i]
  my_tmp<-my_df[grepl(x = my_df$`14)tuGenesBnumber`,pattern = my_bni),]
  if(nrow(my_tmp)>0){
    for(j in 1:nrow(my_tmp)){
      k<-k+1
      my_tu[[k]]<-my_tmp$`1)tuId`[j]
      my_bn[[k]]<-my_bni
    }
  }
}
my_df2<-data.frame(Bnb=my_bn %>% unlist(),
                   tuID=my_tu %>% unlist())
colnames(my_df)[1]<-"tuID"
my_df2<-left_join(my_df2,my_df)

## Gene
my_df<-df_GeneProductSet %>% select(`1)geneId`,`2)geneName`,`3)bnumber`)
colnames(my_df)<-qw(geneID,geneName,Bnb)
my_df<-my_df[my_df$Bnb %in% df_plst_noise$Bnb,]
my_df<-my_df %>% select(Bnb,geneID,geneName)


## TFBS
my_df2$riID<-NA
for(i in 1:nrow(my_df2)){
  my_tu<-my_df2$tuID[i]
  my_tmp<-df_TF_RISet[grepl(x=df_TF_RISet$`19)targetTuOrGene`,pattern = my_tu),]
  if(nrow(my_tmp)>0){
    my_df2$riID[i]<-my_tmp$`1)riId` %>% paste(.,collapse=";")
  }
  if(!is.na(my_df2$`7)promoterId`[i])){
    my_pro<-my_df2$`7)promoterId`[i]
    my_tmp<-df_TF_RISet[grepl(x=df_TF_RISet$`12)promoterID`,pattern = my_pro),]
    if(nrow(my_tmp)>0){
      if(!is.na(my_df2$riID[i])){
        my_chr1<-my_df2$riID[i]
        my_chr2<-my_tmp$`1)riId` %>% paste(.,collapse=";")
        my_chr<-paste(my_chr1,my_chr2,sep=";")
        my_chr<-my_chr %>% str_split(.,pattern=";") %>% unlist() %>% unique() %>% paste(.,collapse=";")
        my_df2$riID[i]<-my_chr
      }else{
        my_df2$riID[i]<-my_tmp$`1)riId` %>% paste(.,collapse=";")
      }
    }
  }
}
my_df$riID<-NA
for(i in 1:nrow(my_df)){
  my_gn<-my_df$geneID[i]
  my_tmp<-df_TF_RISet[grepl(x=df_TF_RISet$`19)targetTuOrGene`,pattern = my_gn),]
  if(nrow(my_tmp)>0){
    my_df$riID[i]<-my_tmp$`1)riId` %>% paste(.,collapse=";")
  }
}

df_ri<-my_df
df_ri$tuID<-NA
# df_ri$promoterID<-NA
# df_ri$tuGenesBnb<-NA
i<-2
for(i in 1:nrow(df_ri)){
  my_bn<-df_ri$Bnb[i]
  my_tmp<-my_df2[my_df2$Bnb==my_bn,]
  if(nrow(my_tmp)>0){
    my_tmp<-my_tmp[!is.na(my_tmp$riID),]
    if(nrow(my_tmp)>0){
          df_ri$tuID[i]<-my_tmp$tuID %>% paste(.,collapse=";")
      if(!is.na(df_ri$riID[i])){
        my_chr1<-paste(my_tmp$riID,collapse=";")
        my_chr2<-paste(df_ri$riID[i],collapse = ";")
        my_chr<-paste(my_chr1,my_chr2,sep = ";")
        df_ri$riID[i]<- my_chr
      }else{
        df_ri$riID[i]<-paste(my_tmp$riID,collapse=";")
      }
    }
  }
}

my_ri<-df_ri[!is.na(df_ri$riID),]$riID %>%
  paste(.,collapse=";") %>%
  str_split(.,pattern = ";") %>%
  unlist() %>%
  unique()

df_TF_RISet_sbst<-df_TF_RISet[df_TF_RISet$`1)riId` %in% my_ri,]
df_TF_RISet_sbst<-df_TF_RISet_sbst %>% select(`1)riId`,`4)regulatorName`,`19)targetTuOrGene`,`10)tfrsSeq`)
colnames(df_TF_RISet_sbst)<-qw(riID,Regulator,Target,tfrsSeq)
df_TF_RISet_sbst$BindingSite<-NA
df_TF_RISet_sbst$BindingSite<-df_TF_RISet_sbst$tfrsSeq %>% str_remove_all(.,pattern = "[[a-z]]")

my_ri<-list()
my_bn<-list()
k<-0
for(i in 1:nrow(df_ri)){
  if(!is.na(df_ri$riID[i])){
    my_tmp<-df_ri$riID[i] %>% str_split(.,pattern=";") %>% unlist()
    for(j in 1:length(my_tmp)){
      k<-k+1
      my_ri[k]<-my_tmp[j]
      my_bn[k]<-df_ri$Bnb[i]
    }
  }
}
my_df<-data.frame(riID=my_ri %>% unlist(),
                  Bnb=my_bn %>% unlist())
my_df<-left_join(my_df,df_TF_RISet_sbst)
my_df<-left_join(my_df,df_plst_noise)
df_TF_RI_plst_noise<-my_df %>% select(riID,Bnb,Name,Essentiality,everything())


my_reg<-qw(CRP,Fis,Nac,Lrp)
tree_list<-list()
msa_list<-list()
for(i in 1:length(my_reg)){
  my_df<-df_TF_RI_plst_noise[df_TF_RI_plst_noise$Regulator==my_reg[i],]
  my_df<-my_df %>% distinct(Bnb,Regulator,tfrsSeq,.keep_all = TRUE)
  my_df<-my_df[!is.na(my_df$BindingSite),]
  my_df$label<-paste(my_df$Name,my_df$Regulator,my_df$riID,sep="_")
  Boxseqs<-my_df$BindingSite %>% DNAStringSet()
  names(Boxseqs)<-my_df$label
  
  seqalign<-msa(Boxseqs,method = "ClustalOmega")
  alignment_seqinr<-msaConvert(seqalign,type="seqinr::alignment")
  distances<-seqinr::dist.alignment(alignment_seqinr,"identity") # compute the distance matrix from the alignment
  tree<-ape::nj(distances) # compute the neighbor-joining tree
  cls <- list(Nes=my_df[my_df$Essentiality=="nonessential",]$label,
              Ess=my_df[my_df$Essentiality=="essential",]$label)
  tree <- groupOTU(tree, cls)
  
  if(length(cls$Nes)>0&length(cls$Ess)>0){
      p<-ggtree(tree)+
      geom_tippoint(aes(color=group))+
      scale_color_manual(values=c(mycolpal[2],mycolpal[1],"gray60"))+ 
      theme(legend.position="")+
      geom_tiplab(offset = 0.01,size=3)+
      # geom_tiplab(aes(subset=(group=="Synthetic")),offset=0.01, size=3)+
      geom_treescale(offset=-2.5,width=0.1)+ xlim_tree(0.8)
  }
  if(length(cls$Nes)>0&length(cls$Ess)==0){
      p<-ggtree(tree)+
      geom_tippoint(aes(color=group))+
      scale_color_manual(values=c(mycolpal[1],mycolpal[1],"gray60"))+ 
      theme(legend.position="")+
      geom_tiplab(offset = 0.01,size=3)+
      # geom_tiplab(aes(subset=(group=="Synthetic")),offset=0.01, size=3)+
      geom_treescale(offset=-2.5,width=0.1)+ xlim_tree(0.8)
  }
  if(length(cls$Nes)==0&length(cls$Ess)>0){
      p<-ggtree(tree)+
      geom_tippoint(aes(color=group))+
      scale_color_manual(values=c(mycolpal[2],mycolpal[2],"gray60"))+ 
      theme(legend.position="")+
      geom_tiplab(offset = 0.01,size=3)+
      # geom_tiplab(aes(subset=(group=="Synthetic")),offset=0.01, size=3)+
      geom_treescale(offset=-2.5,width=0.1)+ xlim_tree(0.8)
  }
  
  my_df1<-data.frame(name=names(Boxseqs),seq=seq(1,length(names(Boxseqs))))
  my_df1$name<-factor(my_df1$name,levels = get_taxa_name(p))
  my_order<-my_df1[order(my_df1$name),]$seq
  Boxseqs2<-Boxseqs[my_order]
  my_aln<-seqalign<-msa(Boxseqs2,method = "ClustalOmega",order = "input")
  class(my_aln)<-"DNAMultipleAlignment"
  q<-ggmsa(my_aln, color = "Chemistry_NT", font = "DroidSansMono", char_width = 0.5, seq_name = TRUE ,)
  
  tree_list[[i]]<-p
  msa_list[[i]]<-q

  print(p)
  print(q)
}

Sys.time()
```
## 13.4.
```{r Seq_Anal,warning=FALSE, message=FALSE,fig.height=3.5,fig.width=6,dpi=600}
tree_list[1]
msa_list[1]
```
## 13.5.
```{r Seq_Anal,warning=FALSE, message=FALSE,fig.height=6,fig.width=6,dpi=600}
tree_list[2]
msa_list[2]
```
## 13.6.
```{r Seq_Anal,warning=FALSE, message=FALSE,fig.height=3,fig.width=6,dpi=600}
tree_list[3]
msa_list[3]
```
# 14. Noise_ch dataset
https://doi.org/10.1126/science.1188308
## 14.1. Calc. DM_noise_ch protein burst size
```{r Noise_ch,warning=FALSE, message=FALSE,fig.height=3,fig.width=3,dpi=300}
df_tani<-paste(getwd(),"NOISE_CH_DataSet","TableS6.xlsx",sep = "/") %>%
  read_xlsx() %>%
  data.frame()
df_tani<-df_tani %>% select(B.Number,Mean_Protein,Noise_Protein,Mean_RNAseq,Life.time_RNAseq,A..mRNA.per.cell.cycle._RNAseq,B..proteins.mRNA._RNAseq)
colnames(df_tani)<-qw(Bnb,TNMean,TNNoise,RNAcopy,RNAlifetime,RNAperCellCycle,PROperRNA)

# Calc. DM_noise_ch
df_tani$TNMean_log<-ifelse(is.na(df_tani$TNMean),NA,log10(df_tani$TNMean))
df_tani$TNNoise_log<-ifelse(is.na(df_tani$TNNoise),NA,log10(df_tani$TNNoise))
df_tani<-df_tani[!is.na(df_tani$TNMean),]
df_tani<-df_tani[order(df_tani$TNMean_log),]
df_tani<-transform(df_tani,TNRunMed=NA,TNSmoothSp=NA,TNDM=NA)
df_tani$TNRunMed<-runmed(df_tani$TNNoise_log,41)
TNSSvislist<-createEmptyDf(nrow=1000,ncol=2, colnames = qw(logx,SS))
TNSSvislist$logx=seq(min(df_tani$TNMean_log),max(df_tani$TNMean_log),length=nrow(TNSSvislist))
misplist<-list()
misplist[[1]]<-smooth.spline(data.frame(x=df_tani$TNMean_log,y=df_tani$TNRunMed),df=12)
TNSSvislist$SS<-predict(misplist[[1]],TNSSvislist$logx)[[2]]
df_tani$TNSmoothSp<-predict(misplist[[1]],df_tani$TNMean_log)[[2]]
df_tani$TNDM<-df_tani$TNNoise_log-df_tani$TNSmoothSp

# Relationship between mean and protein noise in Taniguchi et al.
p1<-ggscatter(df_tani,x="TNMean_log",y="TNNoise_log",
              cor.coef = TRUE,
              cor.coeff.args = list(method = "spearman", label.x = 1.5, label.y=0.8, label.sep = "\n",size=5),
              alpha=0.5,size=0.3,legend="")+
  xlab(expression(log[10]~"protein expression level [a.u.]"))+
  ylab(expression(log[10]~"protein noise [a.u.]"))+
  scale_x_continuous(breaks = get_breaks(by = 2, from = -2),limits =  c(-2, 4))+
  scale_y_continuous(breaks = get_breaks(by = 1, from = -2),limits =  c(-2, 2))+
  geom_line(data=df_tani,aes(x=TNMean_log,y=TNRunMed),colour="darkorange", size=0.7)+
  geom_line(data=TNSSvislist,aes(x=logx,y=SS),colour="deepskyblue", size=1)
p1<-ggpar(p1,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p1

# Calc. protein burst size
df_tani_sbst<-df_tani[df_tani$Bnb %in% df_plst_noise$Bnb,]
df_tani_sbst$Gamma_RNA<-log(2)/df_tani_sbst$RNAlifetime
df_tani_sbst$CellCycle<-df_tani_sbst$RNAperCellCycle/df_tani_sbst$RNAcopy*df_tani_sbst$RNAlifetime
df_tani_sbst$Gamma_PRO<-log(2)/df_tani_sbst$CellCycle
df_tani_sbst$Syn_RNA<-(df_tani_sbst$RNAcopy)*df_tani_sbst$Gamma_RNA
df_tani_sbst$Syn_PRO<-(df_tani_sbst$TNMean/df_tani_sbst$RNAcopy)*df_tani_sbst$Gamma_PRO
df_tani_sbst$Syn_PROperGamma_RNA<-df_tani_sbst$Syn_PRO/df_tani_sbst$Gamma_RNA # protein burst size b
df_tani_sbst$log_burst<-log10(df_tani_sbst$Syn_PROperGamma_RNA)
df_tani_sbst<-left_join(df_tani_sbst,df_plst_noise)

p2<-ggscatter(df_tani_sbst,x="Mean_DMv",y="TNDM",
              color="Essentiality",palette = mycolpal[c(1,2)],
              cor.coef = TRUE,
              cor.coeff.args = list(method = "spearman", label.x = 0.03, label.y=1.5, label.sep = "\n",size=5),
              alpha=0.5,legend="")+
  scale_x_continuous(breaks = get_breaks(by=0.04,from = 0,to=0.08),limits = c(-0.02,0.085))+
  xlab(expression("Mean"~DM[V]))+
  ylab(expression("DM"[noise_ch]))
p2<-ggpar(p2,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p2

Sys.time()
```
## 14.2. Relationship between protein burst size and Noise/Plasticity
```{r Noise_ch,warning=FALSE, message=FALSE,fig.height=3,fig.width=3,dpi=300}
my_mean<-exp(mean(log(df_tani_sbst$Syn_PROperGamma_RNA),na.rm = T)) 
p1<-ggscatter(df_tani_sbst,y = "SD_logAvFITC",x="Syn_PROperGamma_RNA",
             label="Name",repel=T,label.select = list(criteria = "`y` > 0.22"),
          # cor.coef = TRUE,cor.coeff.args = list(method="spearman"),
          color="Essentiality",palette = mycolpal[c(1,2)],legend="",alpha=0.5)+
    # stat_cor(aes(color = Essentiality), label.x = 0.1, size=4,method = "spearman")+
  ylab(expression("SD of"~E[pop]))+
  xlab("Burst size")+
  geom_vline(xintercept = my_mean)+
  scale_x_log10(breaks = 10^(0:3),
                labels = trans_format("log10", math_format(10^.x)))
p1<-ggpar(p1,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p1


p2<-ggscatter(df_tani_sbst,y = "Mean_DMv",x="Syn_PROperGamma_RNA",
              label="Name",repel=T,label.select = list(criteria = "`y` > 0.02"),
          # cor.coef = TRUE,cor.coeff.args = list(method="spearman"),
          color="Essentiality",palette = mycolpal[c(1,2)],legend="",alpha=0.5)+
    # stat_cor(aes(color = Essentiality), label.x = 0.1, size=4,method = "spearman")+
  ylab(expression("Mean"~DM[V]))+
  xlab("Burst size")+
  geom_vline(xintercept = my_mean)+
  scale_y_continuous(breaks = get_breaks(by=0.04,from = 0,to=0.08),limits = c(-0.02,0.1))+
  scale_x_log10(breaks = 10^(0:3),
                labels = trans_format("log10", math_format(10^.x)))
p2<-ggpar(p2,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p2

my_mean<-exp(mean(log(df_tani_sbst[df_tani_sbst$Essentiality=="nonessential",]$Syn_PROperGamma_RNA),na.rm = T)) 
p3<-ggscatter(df_tani_sbst[df_tani_sbst$Essentiality=="nonessential",],y = "SD_logAvFITC",x="Syn_PROperGamma_RNA",
             label="Name",repel=T,label.select = list(criteria = "`y` > 0.22"),
          # cor.coef = TRUE,cor.coeff.args = list(method="spearman"),
          color="Essentiality",palette = mycolpal[1],legend="",alpha=0.5)+
    # stat_cor(aes(color = Essentiality), label.x = 0.1, size=4,method = "spearman")+
  ylab(expression("SD of"~E[pop]))+
  xlab("Burst size")+
  geom_vline(xintercept = my_mean)+
  scale_x_log10(breaks = 10^(0:3),
                labels = trans_format("log10", math_format(10^.x)))
p3<-ggpar(p3,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p3

p4<-ggscatter(df_tani_sbst[df_tani_sbst$Essentiality=="nonessential",],y = "Mean_DMv",x="Syn_PROperGamma_RNA",
              label="Name",repel=T,label.select = list(criteria = "`y` > 0.02"),
          # cor.coef = TRUE,cor.coeff.args = list(method="spearman"),
          color="Essentiality",palette = mycolpal[1],legend="",alpha=0.5)+
    # stat_cor(aes(color = Essentiality), label.x = 0.1, size=4,method = "spearman")+
  ylab(expression("Mean"~DM[V]))+
  xlab("Burst size")+
  geom_vline(xintercept = my_mean)+
  scale_y_continuous(breaks = get_breaks(by=0.04,from = 0,to=0.08),limits = c(-0.02,0.1))+
  scale_x_log10(breaks = 10^(0:3),
                labels = trans_format("log10", math_format(10^.x)))
p4<-ggpar(p4,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p4



Sys.time()
```
## 14.3.
```{r Noise_Plasticity,warning=FALSE, message=FALSE, fig.width=4.5,fig.height=3}
my_tmp<-dtf %>% select(Bnb,Nb_MSR)
my_df<-left_join(df_tani_sbst,my_tmp)

my_med1<-median(my_df$Syn_PROperGamma_RNA,na.rm=T)
my_med2<-median(my_df$Nb_MSR,na.rm=T)
p1<-ggscatter(my_df,x="Syn_PROperGamma_RNA",y="Nb_MSR",
              # label="Name",repel = T,label.select = list(criteria = "`y` > 2"),
              size="SD_logAvFITC",alpha=0.5,
              color="Essentiality",palette = mycolpal[c(1,2)],
              legend="right",legend.title="")+
  geom_hline(yintercept =my_med2 )+
  geom_vline(xintercept =my_med1 )+
  scale_x_log10(breaks = 10^(0:3),labels = trans_format("log10", math_format(10^.x)))+
  scale_y_continuous(breaks=get_breaks(by=3,from=0,to=6),limits = c(0,6))+
  scale_size(range = c(0.5, 5))+
  ylab("Number of MSR")+
  xlab("Burst size")
p1<-ggpar(p1,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p1

p2<-ggscatter(my_df,x="Syn_PROperGamma_RNA",y="Nb_MSR",
              # label="Name",repel = T,label.select = list(criteria = "`y` > 2"),
              size="Mean_DMv",alpha=0.5,
              color="Essentiality",palette = mycolpal[c(1,2)],
              legend="right",legend.title="")+
  geom_hline(yintercept =my_med2 )+
  geom_vline(xintercept =my_med1 )+
  scale_x_log10(breaks = 10^(0:3),labels = trans_format("log10", math_format(10^.x)))+
  scale_y_continuous(breaks=get_breaks(by=3,from=0,to=6),limits = c(0,6))+
  scale_size(range = c(0.5, 5))+
  ylab("Number of MSR")+
  xlab("Burst size")
p2<-ggpar(p2,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
p2


Sys.time()
```
## 14.4.
```{r Noise_Plasticity,warning=FALSE, message=FALSE, fig.width=3.5,fig.height=3}
df_tani_rna<-paste(getwd(),"NOISE_CH_DataSet","TableS6.xlsx",sep = "/") %>%
  read_xlsx() %>%
  data.frame()
df_tani_rna<-df_tani_rna %>% select(B.Number,Mean_Protein,Noise_Protein,Mean_RNAseq,Life.time_RNAseq,A..mRNA.per.cell.cycle._RNAseq,B..proteins.mRNA._RNAseq, Mean_RNA.FISH,Noise_RNA.FISH)
colnames(df_tani_rna)<-qw(Bnb,TNMean,TNNoise,RNAcopy,RNAlifetime,RNAperCellCycle,PROperRNA,TNMean_RNA,TNNoise_RNA)
df_tani_rna$Essentiality<-"nonessential"
df_tani_rna[df_tani_rna$Bnb %in% dBnb[dBnb$ECKnb %in% dess$ECKnb,]$Bnb,]$Essentiality<-"essential"
df_tani_rna$Essentiality<-factor(df_tani_rna$Essentiality,levels=qw(nonessential,essential))
df_tani_rna$Mean_RNA_log<-df_tani_rna$TNMean_RNA %>% log10()
df_tani_rna$Noise_RNA_log<-df_tani_rna$TNNoise_RNA %>% log10()
my_res<-lm(data = df_tani_rna,formula = Noise_RNA_log~Mean_RNA_log)
df_tani_rna$DMv_RNA<-df_tani_rna$Noise_RNA_log-df_tani_rna$Mean_RNA_log*my_res$coefficients[2]+my_res$coefficients[1]
df_tani_rna<-df_tani_rna[!is.na(df_tani_rna$Mean_RNA_log),]
my_df<-df_env %>% select(Bnb,MEANenv,DMenv)
df_tani_rna<-left_join(df_tani_rna,my_df)
ggscatter(df_tani_rna,x="Mean_RNA_log",y="Noise_RNA_log",
          size=1,alpha=0.5,
          color="Essentiality",palette = mycolpal[c(1,2)],
          legend="",
          )+
  xlab(expression(log[10]~mean~mRNA~copy))+
  ylab(expression(log[10]~CV^2))+
  geom_smooth(method="lm")+
  stat_regline_equation(label.x = -1, label.y = 0.1)
ggscatter(df_tani_rna,y="DMv_RNA",x="DMenv",
          size=1,alpha=0.5,
          color="Essentiality",palette = mycolpal[c(1,2)],
          cor.coef = TRUE,
          legend="",
          )+
  xlab(expression(DM[env]))+
  ylab(expression(DM[RNA]))
ggscatter(df_tani_rna[df_tani_rna$Essentiality=="nonessential",],y="DMv_RNA",x="DMenv",
          size=1,alpha=0.5,
          color="Essentiality",palette = mycolpal[c(1)],
          cor.coef = TRUE,
          legend="",
          )+
  xlab(expression(DM[env]))+
  ylab(expression(DM[RNA]))

```
# 15. Noise_pl dataset
https://doi.org/10.1371/journal.pbio.3001491
## 15.1. Load the Noise_pl dataset
```{r Noise_pl,warning=FALSE, message=FALSE,fig.height=5,fig.width=10,dpi=300}
durdat<-paste(getwd(),"NOISE_PL_DataSet","processed_datasets","dataset_with_noise_estimates.csv",sep="/") %>% # all data
  read_csv(skip = 1)
myurcond<-c("Synthetic Rich","Ciprofloxacin 1.5 ng/ml","M9 + 0.2% glucose","M9 + 0.2% lactose","M9 + 0.2% glycerol","M9 + 0.4M NaCl","Stationary phase 16h","Stationary phase 30h")
names(myurcond)<-paste("cond_",seq(1,length(myurcond)),sep="")
print(myurcond)
durdat$condition<-factor(durdat$condition,levels=myurcond)
durdat$mycond<-NA
for(i in 1:nrow(durdat)){
  durdat$mycond[i]<-names(myurcond)[myurcond==durdat$condition[i]]
}
df_urch<-durdat %>% select(blattner,fl_mean_log,fl_var_log,noise,mycond)
colnames(df_urch)[colnames(df_urch)=="blattner"]<-"Bnb"

ggviolin(durdat,x="condition",y="noise",ylim=c(0,0.4),draw_quantiles = 0.5,palette="lancet",fill="condition",legend="")+ rotate_x_text(90)
Sys.time()
```
## 15.2. Correlation between DMnoise_ch and DMnoise_pl
```{r Noise_pl,warning=FALSE, message=FALSE,fig.height=3,fig.width=3,dpi=300}
my_df<-left_join(df_urch,df_tani)
my_df<-my_df %>% select(Bnb,TNDM,noise,mycond)
my_df<-na.omit(my_df)
my_df<-my_df[order(my_df$mycond),]
my_df<-my_df %>% pivot_wider(names_from = mycond,values_from = noise)
my_df %>% 
  cor_test(vars = "TNDM",vars2 = names(myurcond),method = "spearman") %>%
  adjust_pvalue(method = "BH")


for (i in 1:length(myurcond)){
  figtemp<-df_urch[df_urch$mycond==names(myurcond)[i],]
  figtemp<-left_join(df_tani,figtemp)
  figtemp<-figtemp[!is.na(figtemp$noise),]
  
  # DMenv vs. DMnoise
  p1<-ggscatter(figtemp,x="TNDM",y="noise",
            size=2,alpha=0.5,
            color="gray20",
            subtitle=myurcond[i],
            cor.coef = T,
            cor.coeff.args = list(method = "spearman",label.sep = "\n",size=5,label.x=0.7,label.y=0.5))+
    scale_x_continuous(breaks = get_breaks(by = 1, from = 0),limits =  c(-0.5, 1.6))+
    scale_y_continuous(breaks = get_breaks(by = 0.2, from = 0),limits =  c(-0.01, 0.6))+
    xlab(expression(DM[noise_ch]~"[a.u.]"))+
    ylab(expression(DM[noise_pl]~"[a.u.]"))
  p1<-ggpar(p1,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
  print(p1)

}
Sys.time()
```
## 15.3. Correlation between DMv and DMnoise_pl
```{r Noise_pl,warning=FALSE, message=FALSE,fig.height=3,fig.width=3,dpi=300}
my_df<-left_join(df_urch,df_plst_noise)
my_df<-my_df %>% select(Bnb,Mean_DMv,noise,mycond)
my_df<-na.omit(my_df)
my_df<-my_df[order(my_df$mycond),]
my_df<-my_df %>% pivot_wider(names_from = mycond,values_from = noise)
my_df %>% 
  cor_test(vars = "Mean_DMv",vars2 = names(myurcond),method = "spearman") %>%
  adjust_pvalue(method = "BH")

for (i in 1:length(myurcond)){
  figtemp<-df_urch[df_urch$mycond==names(myurcond)[i],]
  figtemp<-left_join(df_plst_noise,figtemp)
  figtemp<-figtemp[!is.na(figtemp$noise),]
  
  # DMenv vs. DMnoise
  p1<-ggscatter(figtemp,x="Mean_DMv",y="noise",
            size=2,alpha=0.5,
            color="gray20",
            subtitle=myurcond[i],
            cor.coef = T,
            cor.coeff.args = list(method = "spearman",label.sep = "\n",size=5,label.x=0.04,label.y=0.5))+
    scale_x_continuous(breaks = get_breaks(by=0.04,from = 0,to=0.08),limits = c(-0.02,0.085))+
    scale_y_continuous(breaks = get_breaks(by = 0.2, from = 0),limits =  c(-0.01, 0.6))+
    xlab(expression("Mean"~DM[V]))+
    ylab(expression(DM[noise_pl]~"[a.u.]"))
  p1<-ggpar(p1,font.y=my_fontsize,font.x=my_fontsize,font.xtickslab = my_fontsize,font.ytickslab = my_fontsize)
  print(p1)

}
Sys.time()
```
# 16. Output
```{r Output,warning=FALSE, message=FALSE,fig.height=3,fig.width=3,dpi=300}
my_df<-df_plst_noise %>% select(Name,Bnb,Essentiality,Mean_logAvFITC,SD_logAvFITC,Mean_DMv)
my_tmp<-dtf %>% select(Bnb,Regulator)
my_tmp$MSR<-NA
i<-1
for(i in 1:nrow(my_tmp)){
  if(!is.na(my_tmp$Regulator[i])){
    my_TR<-str_split(string = my_tmp$Regulator[i],pattern = ";")[[1]]
    my_MSR<-df_msr[(!is.na(df_msr$Nb_of_Metabolite))&(df_msr$regulator %in% my_TR),]
    if(nrow(my_MSR)>0){
      my_tmp$MSR[i]<-paste(my_MSR$regulator,collapse = ";")
    }
  }
}
my_df<-left_join(my_df,my_tmp)

# TODO
# write_csv(x = my_df,file = paste(getwd(),"Output/df_plst_noise_reg.csv",sep="/"))

# TODO
my_df<-df_msr %>% select(regulator,Nb_of_Metabolite,List_of_Metabolites)
# write_csv(x = my_df,file = paste(getwd(),"Output/df_msr.csv",sep="/"))

Sys.time()
```
```{r}

```

