---
title: "Noise_Plasticity_Coupling_in_E.coli"
author: "Tsuru"
date: "2024/8/15"
output: html_document
---
# 0. Set the codes public or private 
```{r Set,warning=FALSE, message=FALSE}
# TODO
my_public<-FALSE # TRUE: public, FALSE: private 
```
# 1. General settings
## 1.1. Load workspace
```{r General,warning=FALSE, message=FALSE}
# load("./Main.RData")
```
## 1.2. Save workspace
```{r General,warning=FALSE, message=FALSE}
# save.image("./Main.RData")
```
## 1.3. Library loading
```{r General,warning=FALSE, message=FALSE}
library(dplyr)# dataframe
library(tidyverse)# dataframe
library(magrittr)# pipe
library(Hmisc) # use %nin%
library(readxl) # read xlsx
library(flowCore) # flow cytometry
# library(flowViz) # flow cytometry

library(stringr)# regular expression

library(KernSmooth)
library(ggplot2)# visualization
library(gridExtra)# visualization
library(grid)# visualization
library(scales)# visualization
library(ggrepel)# visualization
library(ggfortify)
library(reshape2) # dataframe
library(cowplot)
library(ggpubr)# visualization
library(rstatix)# statistical test
library(boot)
library(qvalue)# statistical test
library(ppcor)# calc. partial correlation coeff. 
library(GGally)# visualization
library(gtable)# visualization

library(matrixStats) # rowMeans etc.
library(preprocessCore)
library(RColorBrewer)# visualization

library(boot) # bootstrap

library(fitdistrplus)

library(clusterProfiler) # statistical test
library(KEGGREST) # enrichment analysis

library(FactoMineR) # PCA
library(factoextra) # PCA
library(viridis) # visualization

Sys.time()
```
## 1.4. versatile user functions
The [qw](https://ja.coder.work/so/r/240447) function in Perl.  
The [createEmptyDf](https://htsuda.net/archives/2560) function.
The [g_legend](https://github.com/hadley/ggplot2/wiki/Share-a-legend-between-two-ggplot2-graphs) function to extract legend.
```{r General}
qw <- function(...) {
  sapply(match.call()[-1], deparse)
}

createEmptyDf = function( nrow, ncol, colnames = c() ){
  data.frame( matrix( vector(), nrow, ncol, dimnames = list( c(), colnames ) ) )
}

g_legend<-function(a.gplot){
  tmp <- ggplot_gtable(ggplot_build(a.gplot))
  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
  legend <- tmp$grobs[[leg]]
  return(legend)}

pValue_sp_text=function(dtf){
  pcor_sp<-cor.test(x=dtf[,1],y=dtf[,2],method="spearman")
  rho_sp<-round(pcor_sp$estimate,digits = 2)
  pv_sp<-ifelse(pcor_sp$p.value<0.05," P<0.05",paste(" P==",round(pcor_sp$p.value,digits = 1),sep = ""))
  rhopvtxt_sp<-paste("list(italic(rho)==", rho_sp,", ",pv_sp,")")
  return(rhopvtxt_sp)
}

pValue_pr_text=function(dtf){
  pcor_pr<-cor.test(x=dtf[,1],y=dtf[,2],method="pearson")
  r_pr<-round(pcor_pr$estimate,digits = 2)
  pv_pr<-ifelse(pcor_pr$p.value<0.05," P<0.05",paste(" P==",round(pcor_pr$p.value,digits = 1),sep = ""))
  rpvtxt_pr<-paste("list(italic(r)==", r_pr,", ",pv_pr,")")
  return(rpvtxt_pr)
}
Sys.time()
```
## 1.5 Font size
```{r General}
my_fontsize<-16
Sys.time()
```
## 1.6. External ssd/hdd
```{r General}
my_volume<-"/Volumes/DailyUse"
my_playgrnd<-paste(my_volume,"Noise_Plasticity",sep="/")

if (my_public){
  my_playgrnd<-getwd()
}

Sys.time()
```
## 1.7. Versatile color palletes
```{r General}
mycolpal<-get_palette("lancet",9)
print(c("#00468BFF","#ED0000FF","#42B540FF","#0099B4FF","#925E9FFF","#FDAF91FF","#AD002AFF","#ADB6B6FF","#1B1919FF"))
mycolpal.BuRd<-c(get_palette(palette = "Blues", 4)[2:4],get_palette(palette = "Reds", 4)[2:4])
print(c("#FEE5D9","#FCAE91","#FB6A4A","#CB181D"))
print(c("#EFF3FF","#BDD7E7","#6BAED6","#2171B5"))
Sys.time()
```
## 1.8. Legends
```{r General,fig.height=2.5,fig.width=1,dpi=300}
my_richness<-c("#440154FF","#46337EFF","#365C8DFF","#277F8EFF","#277F8EFF","#1FA187FF","#4AC16DFF","#9FDA3AFF","#FDE725FF") # based on viridis(n=8)
my_tmp<-data.frame(x=seq(1,9),y=seq(1,9),z=seq(1,9),zz=c("01","02","08","09","10","03","04","05","06"))
my_tmp$z<-factor(my_tmp$z,levels = seq(1,9))
my_tmp$zz<-factor(my_tmp$zz,levels = my_tmp$zz)
p<-ggscatter(my_tmp,x="x",y="y",color="zz",palette = my_richness,legend="right",legend.title="")
q<-get_legend(p)
as_ggplot(q)

p<-ggbarplot(my_tmp,x="x",y="y",color="zz",fill="zz",palette = my_richness,legend="right",legend.title="")
q<-get_legend(p)
as_ggplot(q)


my_richness2<-c("#440154FF","#46337EFF","#365C8DFF","#277F8EFF","#1FA187FF","#4AC16DFF","#9FDA3AFF","#FDE725FF") # based on viridis(n=8)
my_tmp<-data.frame(x=seq(1,8),y=seq(1,8),z=seq(1,8))
my_tmp$z<-factor(my_tmp$z,levels = rev(seq(1,8)))
p<-ggscatter(my_tmp,x="x",y="y",color="z",palette = my_richness2,legend="right",legend.title="")
p<-ggpar(p,font.legend = my_fontsize)
q<-get_legend(p)
as_ggplot(q)

p<-ggbarplot(my_tmp,x="x",y="y",color="z",fill="z",palette = my_richness2,legend="right",legend.title="")
p<-ggpar(p,font.legend = my_fontsize)
q<-get_legend(p)
as_ggplot(q)

my_tmp<-data.frame(x=seq(1,3),y=seq(1,3),z=qw(E,F,G))
my_tmp$z<-factor(my_tmp$z,levels = qw(E,F,G))
p<-ggscatter(my_tmp,x="x",y="y",shape="z",legend="right",legend.title="")
q<-get_legend(p)
as_ggplot(q)


Sys.time()
```

# 2. Name Space
## 2.1. Define namse space of genes
```{r Global_Bnb,warning=FALSE, message=FALSE,fig.height=3,fig.width=3,dpi=300}
# gene name of W3110
genename.w3110<-paste(getwd(),"W3110_genes","w3110_gnftr.csv",sep="/") %>%
  read_csv() %>%
  data.frame()
# gene name of MG1655 including CDS, ncRNA, tRNA, rRNA
genename.mg1655<-paste(getwd(),"MG1655_genes","MG1655_gnftr.csv",sep="/") %>%
  read_csv() %>%
  data.frame()
genename.mg1655<-genename.mg1655[,c(2:ncol(genename.mg1655))]
colnames(genename.mg1655)[colnames(genename.mg1655)=="locus_tag"]<-"Bnb"
colnames(genename.mg1655)[colnames(genename.mg1655)=="GeneID"]<-"EntrezID"
# Essentiality (Goodal 2018 mBio)
dess<-paste(getwd(),"W3110_genes","ESSCDSList_Goodall.txt",sep="/") %>%
  read_delim(col_names =qw(Name,ECKnb) ) %>%
  data.frame()
dess$Essentiality<-"essential"
dess<-dess %>% select(ECKnb,Essentiality)

dBnb<-genename.mg1655
dBnb<-dBnb[!is.na(dBnb$Bnb),]
Sys.time()
```
# 3. Transcription Unit
## 3.1. Promoter-Mediated Phenotypic Noise
https://doi.org/10.1371/journal.pgen.1002443
Dataset S1
```{r FlowData,warning=FALSE, message=FALSE}
df_pn<-paste(getwd(),"Promoter_Noise","pgen.1002443.s010.xls",sep="/") %>%
  read_xls(range = "A1:F1833")
colnames(df_pn)<-qw(Bnb,Mean_log_gfp,SD_log_gfp,Mean_gfp,SD_gfp,Noise)
Sys.time()
```

## 3.1. ECOCYC ver. 28.5 (March,2025) 
```{r FlowData,warning=FALSE, message=FALSE}
df_gn<-paste(getwd(),"Promoter_Noise","TUSmartTable_EcoCyc_ver28_5","All_genes.txt",sep="/") %>%
  read_delim()
df_gn<-df_gn %>% select(`Gene Name`,`Accession-1...2`,`Accession-2`,`Transcription Units`)
colnames(df_gn)<-qw(Gene,Bnb,ECKnb,TUs)
df_gn$TUs<-df_gn$TUs %>% str_replace_all(pattern = " // ",";")
df_gn$Gene_Essentiality<-"nonessential"
df_gn[df_gn$ECKnb %in% dess$ECKnb,]$Gene_Essentiality<-"essential"
df_gn[df_gn$Gene_Essentiality=="essential",] %>% nrow()

df_tu<-paste(getwd(),"Promoter_Noise","TUSmartTable_EcoCyc_ver28_5","All_transcription_unit.txt",sep="/") %>%
  read_delim()
colnames(df_tu)<-qw(TU,Prom_TU,Genes_TU,Bnb_TU,ECKnb_TU)
df_tu$Genes_TU<-df_tu$Genes_TU %>% str_replace_all(pattern = " // ",";")
df_tu$Bnb_TU<-df_tu$Bnb_TU %>% str_replace_all(pattern = " // ",";")
df_tu$ECKnb_TU<-df_tu$ECKnb_TU %>% str_replace_all(pattern = " // ",";")
df_tu<-df_tu[!is.na(df_tu$ECKnb_TU),]
df_tu<-df_tu[grepl(x = df_tu$ECKnb_TU,pattern = "^ECK"),]
df_tu$Ess_ECKnb_TU<-NA
df_tu$Ess_Gene_TU<-NA
i<-1
for (i in 1:nrow(df_tu)){
  my_ecks<-df_tu$ECKnb_TU[i] %>% str_split(pattern = ";") %>% unlist()
  my_ecks<-my_ecks[my_ecks %in% df_gn[df_gn$Gene_Essentiality=="essential",]$ECKnb]
  if(length(my_ecks)>0){
    my_gns<-df_gn[df_gn$ECKnb %in% my_ecks,]$Gene
    df_tu$Ess_ECKnb_TU[i]<-my_ecks %>% paste(.,collapse=";")
    df_tu$Ess_Gene_TU[i]<-my_gns %>% paste(.,collapse=";")
  }
}

df_tu$Bnb_Promlib<-NA # Bnb in promoter library
df_tu$Gene_Promlib<-NA
i<-1
for(i in 1:nrow(df_tu)){
  my_bs<-df_tu$Bnb_TU[i] %>% str_split(pattern = ";") %>% unlist()
  my_bs<-my_bs[my_bs %in% df_pn[!is.na(df_pn$Noise),]$Bnb]
  if(length(my_bs)>0){
    df_tu$Bnb_Promlib[i]<-my_bs %>% paste(.,collapse = ";")
    df_tu$Gene_Promlib[i]<-df_gn[df_gn$Bnb %in% my_bs,]$Gene %>% paste(.,collapse = ";")
    
  }
}

my_df<-df_tu[(!is.na(df_tu$Ess_Gene_TU))&(!is.na(df_tu$Bnb_Promlib)),]

# TODO
# write_csv(my_df,paste(getwd(),"Promoter_Noise","Output","All_TU_containing_Ess_pre.csv",sep="/"))

Sys.time()
```


## 3.1.Load the reviewed TU 
```{r FlowData,warning=FALSE, message=FALSE}
df_tu_reviwed<-paste(getwd(),"Promoter_Noise","Output","All_TU_containing_Ess_reviewed.xlsx",sep="/") %>%
  read_xlsx()
  # if a TU driven by a focal promoter has a essential gene positioned downstream of the promoter, then the promoter is defined as an essential promoter
  # gene essentiality is based on the common essential genes between three datasets (TRADIS,KO,PEC)
my_gns<-df_tu_reviwed[!is.na(df_tu_reviwed$Corresponding_Promlib),]$Corresponding_Promlib %>% 
  paste(.,collapse=";") %>%
  str_split(.,pattern =";") %>%
  unlist() %>%
  unique()
my_df<-df_pn
my_df$PromoterEssentiality<-"nonessential"
my_df[my_df$Bnb %in% df_gn[df_gn$Gene %in% my_gns,]$Bnb,]$PromoterEssentiality<-"essential"
my_df$TU_containing_EssentialGenes<-NA
for(i in 1:nrow(my_df)){
  if(my_df$PromoterEssentiality[i]=="essential"){
    my_df$TU_containing_EssentialGenes[i]<-df_tu_reviwed[grepl(x=df_tu_reviwed$Bnb_Promlib,pattern = my_df$Bnb[i]),]$TU %>%
      unique() %>%
      paste(.,collapse = ";")
  }
}

# TODO
# write_csv(my_df,paste(getwd(),"Promoter_Noise","Output","Promoter_Noise_Essentiality.csv",sep="/"))

Sys.time()
```


